%% filename: amsbook-template.tex
%% version: 1.1
%% date: 2014/07/24
%%
%% American Mathematical Society
%% Technical Support
%% Publications Technical Group
%% 201 Charles Street
%% Providence, RI 02904
%% USA
%% tel: (401) 455-4080
%%      (800) 321-4267 (USA and Canada only)
%% fax: (401) 331-3842
%% email: tech-support@ams.org
%% 
%% Copyright 2006, 2008-2010, 2014 American Mathematical Society.
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3c
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%   http://www.latex-project.org/lppl.txt
%% and version 1.3c or later is part of all distributions of LaTeX
%% version 2005/12/01 or later.
%% 
%% This work has the LPPL maintenance status `maintained'.
%% 
%% The Current Maintainer of this work is the American Mathematical
%% Society.
%%
%% ====================================================================

%    AMS-LaTeX v.2 driver file template for use with amsbook
%
%    Remove any commented or uncommented macros you do not use.

\documentclass{book}

%    For use when working on individual chapters
%\includeonly{}

\input{"../Book Preamble/Book Preamble.tex"}


% Glossary - Notation
\glsxtrnewsymbol[description={finite measures on $(X, \MA)$}]{n000001}{$\MM_+(X, \MA)$}
\glsxtrnewsymbol[description={velocity}]{v}{\ensuremath{v}}


\makeindex

\begin{document}
	
	\frontmatter
	
	\title{Introduction to Category Theory}
	
	%    Remove any unused author tags.
	
	%    author one information
	\author{Carson James}
	\thanks{}
	
	\date{}
	
	\maketitle
	
	%    Dedication.  If the dedication is longer than a line or two,
	%    remove the centering instructions and the line break.
	%\cleardoublepage
	%\thispagestyle{empty}
	%\vspace*{13.5pc}
	%\begin{center}
	%  Dedication text (use \\[2pt] for line break if necessary)
	%\end{center}
	%\cleardoublepage
	
	%    Change page number to 6 if a dedication is present.
	\setcounter{page}{4}
	
	\tableofcontents
	\printunsrtglossary[type=symbols,style=long,title={Notation}]
	
	%    Include unnumbered chapters (preface, acknowledgments, etc.) here.
	%\include{}
	
	\mainmatter
	%    Include main chapters here.
	%\include{}
	
	\chapter*{Preface}
	\addcontentsline{toc}{chapter}{Preface}
	
	\begin{flushleft}
		\href{https://creativecommons.org/licenses/by-nc-sa/4.0/legalcode.txt}{cc-by-nc-sa}
	\end{flushleft}

	\newpage
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\chapter{Preliminary Material}
	
	\section{First Order Logic}
	
	\tcr{maybe reorganize and move to logic notes?}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\section{von Neumann–Bernays–Gödel (NBG) Set Theory}
	
	\tcr{maybe just use iterated extensions to not worry about if stuff is well defined or small, etc}, see \href{https://mathoverflow.net/questions/51257/can-zfc-%E2%86%92-nbg-be-iterated}{iterated NBG math overflow}
	
	\begin{defn} \ld{11001} 
		Let $x$ be a class. Then $x$ is said to be a set iff there exists a class $A$ such that $x \in A$. 
	\end{defn}

	\begin{defn}
		Let $x$ and $y$ be classes. Then $x$ is said to be a \tbf{subclass} of $y$, denoted $x \subset y$, if for each set $a$, $a \in x$ implies that $a \in y$. 
	\end{defn}

	\begin{defn}
		Let $x$ and $y$ be classes. Then $x$ is said to be \tbf{equal} to $y$ if $x \subset y$ and $y \subset x$. 
	\end{defn}

	\begin{ax} \lax{11001.1a} \textbf{Axiom of Extensionality:}  \\
		Let $x$ and $y$ be classes. If for each set $a$, $a \in x$ iff $a \in y$, then $x = y$.
	\end{ax}
	
	\begin{ax} \lax{11001.1b} \textbf{Axiom of Pairing:}  \\
		Let $a$, $b$ be sets. Then there exists a set $p$ such that for each for each set $x$, $x \in p$ iff $x = a$ or $x = b$. 
	\end{ax}

	\begin{defn}
		product of two classes
	\end{defn}
	
	\begin{defn}
		Let $A$, $B$ be classes and $R \subset A \times B$. elation from $A$ to $B$.
	\end{defn}
	
	\begin{note}
		We can define cartesion products, relations, and functions for classes just like for sets. 
	\end{note}

	\begin{ex}
		Let $a$, $b$ be sets. Then there exists a unique set $p$ such that for each for each set $x$, $x \in p$ iff $x = a$ or $x = b$. 
	\end{ex}
	
	\begin{proof}
		By \rax{11001.1b} implies that there exists a set $p$ such that for each for each set $x$, $x \in p$ iff $x = a$ or $x = b$. Let $q$ be a set. Suppose that for each for each set $x$, $x \in q$ iff $x = a$ or $x = b$. Then  
	\end{proof}

	\begin{defn}
		Let $x$ and $y$ be sets. We define $(x,y) = \{\}$, denoted 
	\end{defn}
	
	\begin{ax} \lax{11001.1} \textbf{Axiom of Replacement:}  \\
		Let $A$, $B$ be classes and $f:A \rightarrow B$. If $A$ is a set, then $f(A)$ is a set. 
	\end{ax}

	\begin{ax} \lax{11002} \textbf{Schema of Specification:}  \lax{11002}\\
		Let $\phi$ a propositional function on sets. Then there exists a class $A$ such that for each set $x$, $x \in A$ iff $\phi(x)$. 
	\end{ax}
	
	\begin{ex} \lex{11003}
		There exists a class $A$ such that for each class $x$, $x \in A$ iff $x$ is a set.
	\end{ex}
	
	\begin{proof}
		Define $\phi$ by $$\phi(x) : x = x$$ 
		\rax{11002} implies that there exists a class $A$ such that for each set $x$, $x \in A$ iff $x = x$. Let $x$ be a class. If $x \in A$, then by definition, $x$ is a set. \\
		Conversely, if $x$ is a set, then by construction, $x \in A$.
	\end{proof}
	
	\begin{ex} \lex{11004}
		There exists a class $A$ such that for each class $G$ and $*: G \times G \rightarrow G$, $(G, *) \in A$ iff $(G, *)$ is a group.
	\end{ex}
	
	\begin{proof}
		Define $\phi_1$, $\phi_2$ and $\phi_3$ by 
		\begin{itemize}
			\item $\phi_1(G, *): *:G \times G \rightarrow G$ is associative
			\item $\phi_2(G, *):$ there exists $e \in G$ such that for each $g \in G$, $e * g = g * e = g$
			\item $\phi_3(G, *):$ for each $g \in G$ there exists $h \in G$ such that $g * h = h * g = e$
		\end{itemize}
		Define $\phi$ by 
		$$\phi(G, *) : \phi_1(G, *) \text{ and } \phi_2(G, *) \text{ and } \phi_3(G, *)$$
		Then there exists a class $A$ such that for each set $G$ and  $*: G \times G \rightarrow G$, $(G, *) \in A$ iff $\phi(G, *)$ $(G, *) \text{ ``is a group"}$. Therefore, for each group $(G, *)$, $(G, *) \in A$.
		\textbf{FINISH!!!}
	\end{proof}
	
	
	\subsection{TO DO}
	\begin{enumerate} 
		\item \tcb{ cover existence of subclasses, products of classes to be able to define class relations and subsequently class functions}
		\item need to merge this with set theory notes and into to math notes, can first have naive set theory and then the NBG set theory or something
	\end{enumerate}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Relations}
	
	\tcr{can I define relations on classes instead of just sets? do i need to move this stuff before to prelim material since we need class functions which I guess are class relations?} \\
	\tcr{apparently yes } \href{https://arxiv.org/abs/2006.01613}{class,set theory notes (link, but already downloaded)}
	
	\begin{defn}
		Let $A, B$ be classes and $R \subset A \times B$. Then $R$ is said to be a \tbf{relation between $A$ and $B$}. 
		\tcr{write out 1st order logic definition like in notes} \href{https://arxiv.org/abs/2006.01613}{class,set theory notes (link, but already downloaded)}
	\end{defn}
	
	\begin{defn}
		Let $A,B,C$ be classes, $R$ a relation between $A$ and $B$, $S$ a relation between $B$ and $C$. We define the \tbf{composition relation of $R$ with $S$ between $A$ and $C$}, denoted $R \circ S$, by $R \circ S \defeq \{(a,c) \in A \times C: \text{there exists $b \in B$ such that $(a,b) \in R$ and $(b,c) \in S$}\}$.
	\end{defn}
	
	\begin{ex}
		\tcr{show composition of class relations exists}
	\end{ex}
	
	\begin{ex}
		Let $A,B, C, D$ be classes, $R$ a relation between $A$ and $B$, $S$ relation between $B$ and $C$ and $T$ relation between $C$ and $D$. Then $(T \circ S) \circ R = T \circ (S \circ R)$.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item Let $(a,d) \in (T \circ S) \circ R$. Then there exists $b \in B$ such that $(a,b) \in R$ and $(b,d) \in T \circ S$. Since $(b,d) \in T \circ S$, there exists $c \in C$ such that $(b,c) \in S$ and $(c,d) \in T$. Since $(a,b) \in R$ and $(b,c) \in S$, $(a,c) \in S \circ R$. Since $(a,c) \in S \circ R$ and $(c,d) \in T$, we have that $(a,d) \in T \circ (S \circ R)$. Since $(a,d) \in (T \circ S) \circ R$ is arbitrary, we have that for each $(a,d) \in (T \circ S) \circ R$, $(a,d) \in T \circ (S \circ R)$. Hence $(T \circ S) \circ R \subset T \circ (S \circ R)$.
			\item Similarly, $T \circ (S \circ R) \subset (T \circ S) \circ R$. 
		\end{itemize}
		Since $(T \circ S) \circ R \subset T \circ (S \circ R)$ and $T \circ (S \circ R) \subset (T \circ S) \circ R$, we have that $(T \circ S) \circ R = T \circ (S \circ R)$.
		
		\tcr{review, input any necessary axioms for classes}
	\end{proof}
	
	
	
	\begin{defn}
		Let $A$ be a class. We define the \tbf{diagonal relation on $A$}, denoted $\Del_A$, by $\Del_A \defeq \{(a,a): a \in A\}$. \tcr{make and show exists in a previous ex}
	\end{defn}
	
	\begin{ex}
		Let $A, B$ be classes and $R$ a relation between $A$ and $B$. Then 
		\begin{enumerate}
			\item $R \circ \Del_A = R$
			\item $\Del_B \circ R = R$
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{itemize}
				\item Let $(a,b) \in R \circ \Del_A$. Then there exists $a' \in A$ such that $(a, a') \in \Del_A$ and $(a',b) \in R$. By definition of $\Del_A$, $a = a'$. Therefore $(a,b) \in R$. Since $(a,b) \in R \circ \Del_A$ is arbitrary, we have that for each $(a,b) \in R \circ \Del_A$, $(a,b) \in R$. Hence $ R \circ \Del_A \subset R$. 
				\item Let $(a,b) \in R$. Then $a \in A$. Therefore $(a,a) \in \Del_A$. Since $(a,a) \in \Del_A$ and $(a,b) \in R$, we have that $(a, b) \in R \circ \Del_A$. Since $(a,b) \in R$ is arbitrary, we have that for each $(a,b) \in R$, $(a,b) \in R \circ \Del_A$. Hence $R \circ \Del_A \subset R$.  
			\end{itemize}
			Since $R \circ \Del_A \subset R$ and $R \circ \Del_A \subset R$, we have that $R \circ \Del_A = R$.
			\item Similar to $(1)$.
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Functions}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Digraphs}
	
	\begin{defn}
		\tcr{talk about what it means for two diagrams to commute, talk about parallel morphisms being the only exception}
	\end{defn}
	
	\begin{defn}
		\begin{itemize}
			\item We say a digraph $(G, E)$ \tbf{commutes} if for each $x, y \in G$ and paths $p, q$, if $p,q$ start at $x$ and end at $y$, then $p = q$ \tcr{need to fix this definition}
		\end{itemize}
	\end{defn}
	
	\begin{note}
		We make the following exception about parallel arrows. if two ore more edges are equal, we draw them as curved arrows, not parallel.  
		
		We define parallel arrows \tcr{FINISH!!!}
	\end{note}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\chapter{Basic Concepts}
	
	\section{Categories}
	
	\subsection{Introduction}
	
	\begin{defn} \ld{12001}
		Let $\MC_0$, $\MC_1$ be classes and $\dom, \cod : \MC_1 \rightarrow \MC_0$. Define $\MC_1^{(2)}\subset \MC_1 \times \MC_1$ by $\MC_1^{(2)} \defeq \{(g,f) \in \MC_1 \times \MC_1 : \dom(g) = \cod(f) \}$. Let $\circ: \MC_1^{(2)} \rightarrow \MC_1$. Then $(\MC_0, \MC_1, \dom, \cod, \circ)$ is said to be a \textbf{category} if 
		\begin{enumerate}
			\item \tbf{(Composition):} \\ 
			for each $(g,f) \in \MC_1^{(2)}$, $\dom(g \circ f) = \dom(f)$ and $\cod(g \circ f) = \cod(g)$
			\item \tbf{(Associativity):} \\ 
			for each $f,g,h \in \MC_1$, if $(g,f), (h,g) \in \MC_1^{(2)}$, then 
			$$(h \circ g) \circ f = h \circ (g \circ f)$$  
			\item \tbf{(Identity):} \\ 
			for each $X \in \MC_0$, there exists $e \in \MC_1$ such that $\dom(e) = X$, $\cod(e) = X$ and for each $f, g \in \MC_1$, if $\dom(f) = X$ and $\cod(g) = X$, then 
			$$f \circ e = f \text{ and } e \circ g = g$$ 
		\end{enumerate}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category. Write $\MC = (\MC_0, \MC_1, \dom, \cod, \circ)$.
		\begin{itemize}
			\item We define the
			\begin{itemize}
				\item \textbf{objects of $\MC$}, denoted $\Obj(\MC)$, by $\Obj(\MC) \defeq \MC_0$
				\item \textbf{morphisms of $\MC$}, denoted $\Hom$, by $\Hom_{\MC} \defeq \MC_1$ 
				\item \textbf{domain function of $\MC$}, denoted $\dom_{\MC}$, by $\dom_{\MC} \defeq \dom$
				\item \textbf{codomain function of $\MC$}, denoted $\cod_{\MC}$, by $\cod_{\MC} \defeq \cod$
				\item \textbf{composition operator of $\MC$}, denoted $\circ_{\MC}$, by $\circ_{\MC} \defeq \circ$
			\end{itemize}
			\item For $X, Y \in \Obj(\MC)$, we define the \textbf{Morphisms of $\MC$ from $X$ to $Y$}, denoted $\Hom_{\MC}(X, Y)$, by $\Hom_{\MC}(X, Y) \defeq \{f \in \Hom(\MC): \dom_{\MC}(f) = X \text{ and } \cod_{\MC}(f) = Y\}$.
		\end{itemize}
	\end{defn}

	\begin{note}
		When the context is clear, we write $\dom$, $\cod$ and $g \circ f$ in place of $\dom_{\MC}$, $\cod_{\MC}$ and $g \circ_{\MC} f$ respectively.
	\end{note}

	\begin{note} 
		We typically define a category $\MC$ by specifying 
		\begin{itemize}
			\item $\Obj(\MC)$
			\item for $X,Y \in \Obj(\MC)$, the class $\Hom_{\MC}(X, Y)$
			\item for $X,Y,Z \in \Obj(\MC)$, $f \in \Hom_{\MC}(X, Y)$ and $g \in \Hom_{\MC}(Y, Z)$, the composite morphism $g \circ f \in \Hom_{\MC}(X,Z)$.
		\end{itemize}
		and then show 
		\begin{itemize}
			\item well-definedness of composition
			\item associativity of composition 
			\item existence of identities 
		\end{itemize}
	\end{note}
	
	\begin{ex} \lex{15001} \textbf{Uniqueness of Identities:} \\
		Let $\MC$ be a category. Then for each $A \in \Obj(\MC)$, there exists a unique $e \in \Endo_{\MC}(A)$ such that for each $B \in \Obj(\MC)$, $f \in \Hom_{\MC}(A, B)$ and $g \in \Hom_{\MC}(B, A)$, $f \circ e = f$ and $e \circ g = g$.
	\end{ex}
	
	\begin{proof}
		Let $A \in \Obj(\MC)$. 
		\begin{itemize}
			\item \tbf{Existence:} \\
			Since $\MC$ is a category, by definition there exists $e \in \Hom_{\MC}(A, A)$ such that for each $B \in \Obj(\MC)$, $f \in \Hom_{\MC}(A, B)$ and $g \in \Hom_{\MC}(B, A)$, $f \circ e = f$ and $e \circ g = g$. 
			\item \tbf{Uniqueness: } \\
			Let $e_1, e_2 \in \Hom_{\MC}(A, A)$. Suppose that for each $B \in \Obj(\MC)$, $f \in \Hom_{\MC}(A, B)$ and $g \in \Hom_{\MC}(B, A)$, $f \circ e_1 = f$, $f \circ e_2 = f$, $e_1 \circ g = g$ and $e_2 \circ g = g$. Then 
			\begin{align*}
				e_1
				& = e_2 \circ e_1 \\
				& = e_2.
			\end{align*}
		\end{itemize}
	\end{proof}
	
	\begin{defn}
		Let $\MC$ be a category and $A \in \Obj(\MC)$. We define the \tbf{identity morphism on $A$}, denoted $\id_A^{\MC} \in \Hom_{\MC}(A, A)$, to be the unique $e \in \Hom_{\MC}(A, A)$ such that for each $B \in \Obj(\MC)$, $f \in \Hom_{\MC}(A, B)$ and $g \in \Hom_{\MC}(B, A)$, $f \circ e = f$ and $e \circ g = g$.
	\end{defn}
	
	\begin{note}
		When the context is clear, we write $\id_A$ in place of $\id_A^{\MC}$.
	\end{note}
	
	\begin{defn} \ld{12002}
		Let $\MC$ be a category. Then $\MC$ is said to be 
		\begin{itemize}
			\item \textbf{small} if $\Obj(\MC)$ and $\Hom_{\MC}$ are sets
			\item \textbf{locally small} if for each $A,B \in \Obj(\MC)$, $\Hom_{\MC}(A,B)$ is a set 
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{12003}
		Let $\MC$ be a category. If $\MC$ is small, then $\MC$ is a set. 
	\end{ex}
	
	\begin{proof}
		Suppose that $\MC$ is small. Then $\Obj(\MC)$ and $\Hom_{\MC}$ are sets. Then $\MP(\Obj(\MC))$, $\MP(\Hom_{\MC})$ and $\Obj(\MC)^{\Hom_{\MC}}$ are sets. Hence $\Obj(\MC) \times \Hom_{\MC} \times \Obj(\MC)^{\Hom_{\MC}} \times \Obj(\MC)^{\Hom_{\MC}}$ is a set. By definition, $\MC = (\Obj(\MC), \Hom_{\MC}, \dom, \cod) \in \Obj(\MC) \times \Hom_{\MC} \times \Obj(\MC)^{\Hom_{\MC}} \times \Obj(\MC)^{\Hom_{\MC}}$. By definition, $\MC$ is a set. 
	\end{proof}
	
	\begin{ex} \lex{12004}
		There exists a class $A$ such that $\MC \in A$ iff $\MC$ is a small category. 
	\end{ex}
	
	\begin{proof}
		\rex{12003} implies that for each category $\MC$, $\MC$ is small implies that $\MC$ is a set. Define $\phi$ by $$\phi(\MC): \MC \text{ is a small category} $$ 
		Then \rax{11002} implies that there exists a class $A$ such that $\MC \in A$ iff $\MC$ is a small category.  
	\end{proof}
	
	\tcr{prosets}
	\begin{defn}
		Let $\MP$ be a category. Then $\MP$ is said to be a 
		\begin{enumerate}
			\item \tbf{proset category} if for each $a, b \in \Obj(\MP)$, $\# \Hom_{\MP}(a,b) \leq 1$
			\item \tbf{poset category} if $\MP$ is a proset category and for each $a,b \in \Obj(\MP)$, $\# \Hom_{\MP}(a,b) = 1$ and $\# \Hom_{\MP}(b,a) = 1$ implies that $a = b$.  
		\end{enumerate}
	\end{defn}
	
	\begin{defn}
		Let $\MP$ be a proset. Set $P \defeq \Obj(\MP)$. We define the \tbf{less-than-or-equal-to relation} on $P$, denoted ${\leq} \subset P \times P$, by 
		$${\leq} \defeq \{(a,b) \in P \times P: \Hom_{\MP}(a,b) \neq \varnothing\}.$$
	\end{defn}
	
	\begin{defn}  
		Let $\MC$ be a category. Then $\MC$ is said to be \tbf{discrete} if $\Hom_{\MC} = \{\id_X: X \in \Obj(\MC)\}$. 
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Fundamental Examples}

	\begin{defn} \ld{12001.1}
		We define the \textbf{empty category}, denoted $\0$, by 
		\begin{itemize}
			\item $\Obj(\0) = \varnothing$
			\item $\Hom_{\0} = \varnothing$
		\end{itemize}
	\end{defn}

	\begin{ex} \lex{12001.2}
		We have that $\0$ is a category.
	\end{ex}
	
	\begin{proof}
		Vacuously true.
	\end{proof}

	\begin{defn} \ld{12001.}
		We define the \textbf{trivial category}, denoted $\1$, by 
		\begin{itemize}
			\item $\Obj(\1) = \{*\}$
			\item $\Hom_{\1} = \{\id_*\}$
		\end{itemize}
	\end{defn}

	\begin{ex} \lex{12001.}
		We have that $\1$ is a category.
	\end{ex}

	\begin{proof}
		Clear.
	\end{proof}
	
	\begin{defn} \ld{12001.}
		We define $\bSet$ by  
		\begin{itemize}
			\item $\Obj(\bSet) = \{A: A \text{ is a set}\}$ 
			\item for each $A,B \in \Obj(\bSet)$, $\Hom_{\bSet}(A,B) = \{f: f:A \rightarrow B\}$
			\item for $A, B, C \in \bSet$, $f \in \Hom_{\bSet}(A, B)$ and $g \in \Hom_{\bSet}(B, C)$, $g \circ_{\bSet} f = g \circ f$. 
		\end{itemize}
	\end{defn}

	\begin{ex} \lex{12001.}
		We have that $\bSet$ is a category.
	\end{ex}

	\begin{proof}\
		\begin{itemize}
			\item \tbf{well-definedness of composition:}
			\item \tbf{associativity of composition:} 
			\item \tbf{existence of identities:} 
		\end{itemize}
		\tcr{FINISH!!!}
	\end{proof}
	
	\begin{ex}
		\tcr{Let $A,B \in \Obj(\bSet)$, show $\MR(A, B)$ is a category, (category of relations)}
	\end{ex}
	
	\begin{ex}
		\tcr{preordered set is a category}
	\end{ex}
	
	
	

	
	\tcr{FIX!!!! need to decide what to do about relations, on the one hand, we can define relations as classes like in the previous section, on another hand, we can define the category of relations based on $\bSet$, on the third hand, looking at `Elementary categories, elementary toposes` by mcLarty who shows you cand define relations in terms of subobjects, i.e. morphisms, does this more general idea also form a category, of which the category of relations based on set can be considered a subobject(i.e. a subcategory)?}
	\begin{defn}
		We define the \tbf{category of relations}, denoted $\bRel$, by 
		\begin{itemize}
			\item $\Obj(\bRel) \defeq \Obj(\bSet)$
			\item for each $A,B \in \Obj(\bRel)$, $\Hom_{\bRel}(A, B) \defeq \MP(A \times B)$
			\item for each $A,B, C \in \Obj(\bRel)$, $R \in \Hom_{\bRel}(A, B)$ and $\Hom_{\bRel}(B, C)$, we define $S \circ_{\bRel} R \defeq \{(a,c) \in A \times C: \text{there exists $b \in B$ such that $(a,b) \in R$ and $(b,c) \in S$}\}$.
		\end{itemize}
	\end{defn}
	
	\begin{proof}\
		\begin{itemize}
			\item \tbf{well-definedness of composition:} \\
			By definition, for each $A,B, C \in \Obj(\bRel)$, $R \in \Hom_{\bRel}(A, B)$ and $S \in \Hom_{\bRel}(B, C)$, we have that 
			\begin{align*}
				S \circ_{\bRel} R 
				& \in \MP (A \times C) \\
				& = \Hom_{\bRel}(A, C).
			\end{align*}
			So $\circ_{\bRel}$ is well-defined.
			\item \tbf{associativity of composition:} \\
			\tcr{ref ex in basic concepts chapter}
			\item \tbf{existence of identities:} \\
			\tcr{ref ex in basic concepts chapter}
		\end{itemize}
		\tcr{FINISH!!!}
	\end{proof}
	
	
	

	
	
	\tcr{maybe discuss a quiver as a category whos objects are vertices and morphisms are  and composition is given by concatenation (i.e. I guess a quiver equipped with the path algebra), maybe this is not appropriate}
	\href{https://en.wikipedia.org/wiki/Quiver_(mathematics)#Path_algebra}{quiver wikipedia} 
	
	\begin{defn}
		We define the \tbf{category of quivers}, denoted $\bQuiv$, by 
		\begin{itemize}
			\item $\Obj(\bQuiv) \def \{\MQ: \text{$\MQ$ is a quiver}\}$
			\item for $\MQ$, $\ML \in \Obj(\bQuiv)$, 
			$$\Hom_{\bQuiv}(\MQ, \ML) \defeq \{\phi: \text{$\phi$ is a quiver} \}$$
		\end{itemize}
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	


















	













































	
	
	\subsection{Opposite Categories}

	\begin{defn}  \ld{12004}
		Let $\MC$ be a category, we define the \text{dual of $\MC$} or the \textbf{opposite of $\MC$}, denoted $\op{\MC}$, by 
		\begin{itemize}
			\item $\Obj(\op{\MC}) \defeq \Obj(\MC)$
			\item for $X,Y \in \Obj(\op{\MC})$, $\Hom_{\op{\MC}}(X,Y) \defeq \Hom_{\MC}(Y,X)$
			\item for $X, Y, Z \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(X, Y), g \in \Hom_{\op{\MC}}(Y,Z)$, $g \circ_{\op{\MC}} f \defeq f \circ_{\MC} g$
		\end{itemize}
	\end{defn}

	\begin{ex}  \lex{12005}
		Let $\MC$ be a category. Then $\op{\MC}$ is a category.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item for $W,X,Y,Z \in \Obj(\MC)$, $f \in \Hom_{\op{\MC}}(W, X)$ and $g \in \Hom_{\op{\MC}}(X, Y)$ and $h \in \Hom_{\op{\MC}}(Y, Z)$. Then 
			\begin{align*}
				(h \circ_{\op{\MC}} g) \circ_{\op{\MC}} f 
				&= f \circ_{\MC}( h \circ_{\op{\MC}} g) \\
				&= f \circ_{\MC} (g \circ_{\MC} h) \\
				&= (f \circ_{\MC} g) \circ_{\MC} h \\
				&= h \circ_{\op{\MC}} (f \circ_{\MC} g) \\
				&= h \circ_{\op{\MC}} (g \circ_{\op{\MC}} f)
			\end{align*}
			So composition is associative.
			\item Let $X \in \Obj(\MC)$ and $f,g \in \Hom_{\op{\MC}}$. Suppose that $\dom(f) = X$ and $\cod(g) = X$ 
			Then 
			\begin{align*}
				f  \circ_{\op{\MC}} \id_X
				&= \id_X  \circ_{\MC} f \\
				&= f
			\end{align*}
			and 
			\begin{align*}
				\id_X  \circ_{\op{\MC}} g 
				&= g \circ_{\MC} \id_X \\
				&= g
			\end{align*}
		So $(\id_X)_{\op{\MC}} =  (\id_X)_{\MC}$.
		\end{itemize}
	\end{proof}
	
	\begin{ex} \lex{12005.1}
		Let $\MC$ be a category. Then $\op{(\op{\MC})}  = \MC$. 
	\end{ex}
	
	\begin{proof}
		Set $\MD \defeq \op{\MC}$.
		\begin{itemize}
			\item We have that
			\begin{align*}
				\Obj(\op{(\op{\MC})} )
				& = \Obj(\op{\MD}) \\
				& = \Obj(\MD), \quad \text{(by definition)} \\
				& = \Obj(\op{\MC}) \\
				& = \Obj(\MC), \quad \text{(by definition)}. 
			\end{align*}
			\item Let $X,Y \in \Obj(\op{(\op{\MC})} )$. Then
			\begin{align*}
				\Hom_{\op{(\op{\MC})} }(X, Y) 
				& = \Hom_{\op{\MD}}(X, Y) \\
				& = \Hom_{\MD}(Y, X), \quad \text{(by definition)} \\
				& = \Hom_{\op{\MC}}(Y, X) \\
				& = \Hom_{\MC}(X, Y), \quad \text{(by definition)}.
			\end{align*}
		\end{itemize}
	\end{proof}

	\begin{ex}
		Let $\MP$ be a category. Then 
		\begin{enumerate}
			\item $\MP$ is a proset iff $\op{\MP}$ is a proset
			\item $\MP$ is a poset iff $\op{\MP}$ is a poset
		\end{enumerate} 
	\end{ex}

	\begin{proof}
		\tcr{FINISH!!!}
	\end{proof}

	\begin{defn}
		Let $\MP$ be a proset. Set $P \defeq \Obj(\MP)$. We define the \tbf{less-than-or-equal-to relation} on $P$, denoted ${\leq} \subset P \times P$, by 
		$${\leq} \defeq \{(a,b) \in P \times P: \Hom_{\op{\MP}}(a,b) \neq \varnothing\}.$$
	\end{defn}





































	
	
	
	























































	
	
	

	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Functors}
	
	
	\subsection{Introduction}
	
	\begin{defn} \ld{def:basics:functors:intro:0001}
		Let $\MC$ and $\MD$ be categories and $F_0 : \Obj(\MC) \rightarrow \Obj(\MD)$, $F_1: \Hom_{\MC} \rightarrow \Hom_{\MD}$ class functions. Set $F = (F_0, F_1)$. Then $F$ is said to be a \text{$(\MC, \MD)$-functor}, denoted  $F:\MC \rightarrow \MD$, if 
		\begin{enumerate}
			\item for each $A,B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$, $F_1(f) \in \Hom_{\MD}(F_0(A), F_0(B))$
			\item for each $A,B, C \in \Obj(\MC)$, $f \in \Hom_{\MC}(A,B)$ and $g \in \Hom_{\MC}(B, C)$, $F_1(g \circ f) = F_1(g) \circ F_1(f)$
			\item for each $A \in \Obj(\MC)$,  $F_1(\id_A) = \id_{F_0(A)}$
		\end{enumerate}
	\end{defn}
	
	\begin{note}
		When the context is clear, we may say ``functor" instead of ``$(\MC, \MD)$-functor".
	\end{note}

	\begin{note}
		For $A \in \Obj(C)$ and $f \in \Hom_{\MC}$, we typically write $F(A)$ and $F(f)$ instead of $F_0(A)$ and $F_1(f)$ respectively.
		\tcr{maybe discuss how this is just a quiver homomorphism}
	\end{note}

	\begin{defn} \ld{def:basics:functors:intro:0002}
		Let $\MC$ be a category. We define the \textbf{empty functor} from $\0$ to $\MC$, denoted $E_{\MC}: \0 \rightarrow \MC$ by $(E_{\MC})_0 \defeq \varnothing$ and = $(E_{\MC})_1 \defeq \varnothing$. 
	\end{defn}

	\begin{ex} \lex{ex:basics:functors:intro:0003}
		Let $\MC$ be a category. Then $E_{\MC}: \0 \rightarrow \MC$ is a functor.
	\end{ex}

	\begin{proof}
		Since $\Obj(\0) = \varnothing$ and $\Hom_{\0} = \varnothing$, this is vacuously true. 
	\end{proof}

	\begin{defn} \ld{def:basics:functors:intro:0004}
		Let $\MC, \MD$ be categories and $X \in \Obj(\MD)$. We define the \textbf{constant functor} from $\MC$ onto $X$, denoted $\Del^{\MC}_X: \MC \rightarrow \MD$ by 
		\begin{itemize}
			\item $\Del^{\MC}_X (A) = X$
			\item $\Del^{\MC}_X (f) = \id_X$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:functors:intro:0005}
		Let $\MC, \MD$ be categories and $X \in \Obj(\MD)$. Then $\Del^{\MC}_X : \MC \rightarrow \MD$ is a functor.
	\end{ex}

	\begin{proof}\
		\begin{enumerate}
			\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$. Then 
			\begin{align*}
				\Del^{\MC}_X (f)
				& = \id_X \\
				& \in \Hom_{\MD}(X, X) \\
				& = \Hom_{\MD}(\Del^{\MC}_X (A), \Del^{\MC}_X (B))
			\end{align*}  
			\item Let $A,B,C \in \Obj(\MC)$, $f \in \Hom_{\MC}(A, B)$ and $g \in \Hom_{\MC}(B, C)$. Then 
			\begin{align*}
				\Del^{\MC}_X (g \circ f) 
				& = \id_X \\
				& = \id_X \circ \id_X \\
				& = \Del^{\MC}_X (g) \circ \Del^{\MC}_X (f)
			\end{align*} 
			\item Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				\Del^{\MC}_X (\id_A)
				& = \id_X \\
				& = \id_{\Del^{\MC}_X (A)}
			\end{align*}
		\end{enumerate}
		So $\Del^{\MC}_X : \MC \rightarrow \MD$ is a functor.
	\end{proof}

	
	
	
	
	
	















































\subsection{Fundamental Examples}

\tcr{discuss a quiver as a functor from the free quiver (a category) to $\bSet$ or other category}
\href{https://en.wikipedia.org/wiki/Quiver_(mathematics)#Path_algebra}{quiver wikipedia} 


\begin{note}
	We recall for $X,Y \in \Obj(\bSet)$, $f \in \Hom_{\bSet}(X,Y)$, the image and preimage maps induced by $f$, denoted $f_* \in \Hom_{\bSet}(\MP(X), \MP(Y))$ and $f^* \in \Hom_{\bSet}(\MP(Y), \MP(X))$ are defined by $f_*(A) \defeq f(A)$ and $f^*(B) \defeq f^{-1}(B)$. \tcr{make exercise in set theory notes showing $(g \circ f)_* = g+* \circ f_*$ and similar for contravariant version}
\end{note}

\begin{defn}
	We define the 
	\begin{itemize}
		\item \tbf{image power set functor on $\bSet$}, denoted $\MP_*: \bSet \rightarrow \bSet$ by 
		\begin{itemize}
			\item $\MP_*(X) \defeq \MP(X), \quad X \in \Obj(\bSet)$
			\item $\MP_*(f) \defeq f_*, \quad f \in \Hom_{\bSet}$
		\end{itemize}
		\item 
		\tbf{preimage power set functor on $\bSet$}, denoted $\MP^*: \op{\bSet} \rightarrow \bSet$ by 
		\begin{itemize}
			\item $\MP^*(X) \defeq \MP(X), \quad X \in \Obj(\bSet)$
			\item $\MP^*(f) \defeq f^*, \quad f \in \Hom_{\bSet}$
		\end{itemize}
	\end{itemize}
\end{defn}

\begin{ex}
	We have that 
	\begin{enumerate}
		\item $\MP_*: \bSet \rightarrow \bSet$ is a functor.
		\item $\MP^*: \op{\bSet} \rightarrow \bSet$ is a functor.
	\end{enumerate}
\end{ex}

\begin{proof}\
	\begin{enumerate}
		\item 
		\begin{enumerate}
			\item For each $X,Y \in \Obj(\bSet)$ and $f \in \Hom_{\bSet}(X,Y)$, 
			\begin{align*}
				\MP_*(f)
				& = f_* \\
				& \in \Hom_{\bSet}(\MP(X), \MP(Y)) \quad \tcr{(ref ex in set theory section intro to math notes)}\\
				& = \Hom_{\bSet}(\MP_*(X), \MP_*(Y)).
			\end{align*}
			\item 
			For each $X,Y,Z \in \Obj(\bSet)$, $f \in \Hom_{\bSet}(X,Y)$ and $g \in \Hom_{\bSet}(Y,Z)$,
			\begin{align*}
				\MP_*(g \circ_{\bSet} f)
				& = (g \circ_{\bSet} f)_* \\
				& = g_* \circ_{\bSet} f_* \quad \text{(ref ex in set theory section intro to math notes)} \\
				& = \MP_*(g) \circ_{\bSet} \MP_*(f).
			\end{align*}
			\item 
			For each $X \in \Obj(\bSet)$, 
			\begin{align*}
				\MP_*(\id_X^{\bSet})
				& = \id_{\MP(X)}^{\bSet} \quad \text{(ref ex in set theory section intro to math notes)} \\
				& = \id_{\MP_*(X)}^{\bSet}.
			\end{align*}
		\end{enumerate}
		Thus $\MP_*: \bSet \rightarrow \bSet$ is a functor.
		\item 
		\begin{enumerate}
			\item Let $X,Y \in \Obj(\op{\bSet})$ and $f \in \Hom_{\op{\bSet}}(X,Y)$. Then $X \in \Obj(\bSet)$ and $f \in \Hom_{\bSet}(Y, X)$. Therefore
			\begin{align*}
				\MP^*(f)
				& = f^* \\
				& \in \Hom_{\bSet}(\MP(X), \MP(Y)) \quad \tcr{(ref ex in set theory section intro to math notes)} \\
				& = \Hom_{\bSet}(\MP^*(X), \MP^*(Y)).
			\end{align*}
			Since $X,Y \in \Obj(\op{\bSet})$ and $f \in \Hom_{\op{\bSet}}(X,Y)$ are arbitrary, we have that for each $X,Y \in \Obj(\op{\bSet})$ and $f \in \Hom_{\op{\bSet}}(X,Y)$, $\MP^*(f) \in \Hom_{\op{\bSet}}(\MP^*(X), \MP^*(Y))$.
			\item 
			Let $X,Y,Z \in \Obj(\op{\bSet})$, $f \in \Hom_{\op{\bSet}}(X,Y)$ and $g \in \Hom_{\op{\bSet}}(Y,Z)$. Then $X,Y,Z \in \Obj(\bSet)$, $f \in \Hom_{\bSet}(Y,X)$ and $g \in \Hom_{\bSet}(Z,Y)$. Therefore
			\begin{align*}
				\MP^*(g \circ_{\op{\bSet}} f)
				& = (g \circ_{\op{\bSet}} f)^* \\
				& = (f \circ_{\bSet} g)^* \\
				& = g^* \circ_{\bSet} f^* \quad \text{(ref ex in set theory section intro to math notes)} \\
				& = \MP^*(g) \circ_{\bSet} \MP^*(f).
			\end{align*}
			\item 
			For each $X \in \Obj(\op{\bSet})$, 
			\begin{align*}
				\MP^*(\id_X^{\op{\bSet}})
				& = (\id_X^{\op{\bSet}})^* \\
				& = (\id_X^{\bSet}) \\
				& = \id_{\MP(X)}^{\op{\bSet}} \quad \text{(ref ex in set theory section intro to math notes)} \\
				& = \id_{\MP^*(X)}^{\op{\bSet}}.
			\end{align*}
		\end{enumerate}
		Thus $\MP^*: \op{\bSet} \rightarrow \bSet$ is a functor.
	\end{enumerate}
\end{proof}

%\begin{defn}
%	We define the \tbf{Boolean exponential functor on $\bSet$}, denoted $\Exp((-, \{0,1\})): \op{\bSet} \rightarrow \bSet$ by 
%	\begin{itemize}
%		\item $\Exp((-, \{0,1\}))(X) \defeq \{0,1\}^X, \quad X \in \Obj(\bSet)$
%		\item $\Exp((-, \{0,1\}))(f) \defeq (-) \circ_{\bSet} f, \quad f \in \Hom_{\bSet}$
%	\end{itemize}
%\end{defn}
%
%\begin{ex}
%	We have that $\Exp_{\bSet}(-, \{0,1\}) \op{\bSet} \rightarrow \bSet$ is a functor. 
%\end{ex}
%	






























































	\subsection{Category of Small Categories}

	\begin{defn} \ld{def:basics:functors:small_cat:0001}
		Let $\MC$, $\MD$ and $\ME$ be categories and $F:\MC \rightarrow \MD$, $G: \MD \rightarrow \ME$ functors. We define the \textbf{composition of $G$ with $F$}, denoted $G \circ F: \MC \rightarrow \ME$, by 
		\begin{itemize}
			\item $G \circ F (A) \defeq G(F(A))$
			\item $G \circ F (f) \defeq G(F(f))$
		\end{itemize} 
	\end{defn}
	
	\begin{note}
		Writing $G \circ F = (H_0, H_1)$, we have that $H_0 = G_0 \circ F_0$ and $H_1 = G_1 \circ F_1$. 
	\end{note}
	
	\begin{ex} \lex{ex:basics:functors:small_cat:0002}
		Let $\MC$, $\MD$ and $\ME$ be categories and $F:\MC \rightarrow \MD$, $G: \MD \rightarrow \ME$ functors. Then  $G \circ F: \MC \rightarrow \ME$ is a functor.
	\end{ex}

	\begin{proof}\
		\begin{enumerate}
				\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Since $F(f) \in \Hom_{\MD}(F(A), F(B))$, we have that $G(F(f)) \in \Hom_{\ME}(G(F(A)), G(F(B)))$. Then 
			\begin{align*}
				G \circ F (f) 
				& = G(F(f)) \\
				& \in \Hom_{\ME}(G(F(A)), G(F(B))) \\
				& =  \Hom_{\ME}(G \circ F(A), G \circ F (B)) \\
			\end{align*}
			\item Let $A,B, C \in \Obj(\MC)$, $f \in \Hom_{\MC}(A,B)$ and $g \in \Hom_{\MC}(B, C)$. Then 
			\begin{align*}
				G \circ F(g \circ f) 
				& = G (F (g \circ f)) \\
				& = G(F(g) \circ F(f)) \\
				& = G(F(g)) \circ G(F(f)) \\
				& = G \circ F (g) \circ G \circ F (f) \\
			\end{align*}
			\item Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				G \circ F(\id_{A})
				& = G(F(\id_A) )\\
				& = G(\id_{F(A)}) \\
				& = \id_{G(F(A))} \\
				& = \id_{G \circ F(A)} 
			\end{align*}
		\end{enumerate}
		So $G \circ F: \MC \rightarrow \ME$ is a functor. 
	\end{proof}

	\begin{ex} \lex{ex:basics:functors:small_cat:0003}
		Let $\MC$, $\MD$, $\ME$, $\MF$ be categories and $F:\MC \rightarrow \MD$, $G : \MD \rightarrow \ME$, $H: \ME \rightarrow \MF$ functors. Then $(H \circ G) \circ F = H \circ (G \circ F)$.
	\end{ex}

	\begin{proof}
		Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Then 
		\begin{itemize}
				\item 
				\begin{align*}
					(H \circ G) \circ F(A) 
					& = H \circ G (F(A)) \\
					& = H (G(F(A))) \\
					& = H( G \circ F (A)) \\
					& = H \circ (G \circ F) (A)
				\end{align*}
				\item  
				\begin{align*}
					(H \circ G) \circ F(f) 
					& = H \circ G (F(f)) \\
					& = H (G(F(f))) \\
					& = H( G \circ F (f)) \\
					& = H \circ (G \circ F) (f)
				\end{align*}
		\end{itemize}
		Hence $(H \circ G) \circ F = H \circ (G \circ F)$.
	\end{proof}

	\begin{defn} \ld{def:basics:functors:small_cat:0004}
		Let $\MC$ be a category. We define the \textbf{identity functor from $\MC$ to $\MC$}, denoted $\id_{\MC}: \MC \rightarrow \MC$, by 
		\begin{itemize}
			\item $\id_{\MC}(A) \defeq A, \quad (A \in \Obj(\MC))$
			\item $\id_{\MC}(f) \defeq f, \quad (f \in \Hom_{\MC})$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:functors:small_cat:0005}
		Let $\MC$ be a category. Then $\id_{\MC}: \MC \rightarrow \MC$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Then 
			\begin{align*}
				\id_{\MC}(f) 
				& = f \\
				& \in \Hom_{\MC}(A, B) \\
				& = \Hom_{\MC}(\id_{\MC}(A), \id_{\MC}(B)) \\
			\end{align*}
			\item Let $A,B, C \in \Obj(\MC)$, $f \in \Hom_{\MC}(A,B)$ and $g \in \Hom_{\MC}(B, C)$. Then 
			\begin{align*}
				\id_{\MC}(g \circ f) 
				& = g \circ f \\
				& = \id_{\MC}(g) \circ \id_{\MC} (f)
			\end{align*}
			\item Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				\id_{\MC}(\id_{A})
				& = \id_A \\
				& = \id_{\id_{\MC}(A)}
			\end{align*}
		\end{enumerate}
	\end{proof}

	\begin{ex} \lex{ex:basics:functors:small_cat:0006}
		Let $\MC$ and $\MD$ be categories and $F:\MC \rightarrow \MD$. Then 
		\begin{enumerate}
			\item $\id_{\MD} \circ F = F$
			\item $F \circ \id_{\MC} = F$
		\end{enumerate}
	\end{ex}

	\begin{proof}\
		\begin{enumerate}
			\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$. Then 
			\begin{align*}
				\id_{\MD} \circ F(A) 
				& = \id_{\MD}(F(A)) \\
				& = F(A)
			\end{align*}
			and 
			\begin{align*}
				\id_{\MD} \circ F(f) 
				& = \id_{\MD}(F(f)) \\
				& = F(f)
			\end{align*} 
			Since $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$ are arbitrary, $\id_{\MD} \circ F = F$.
			\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$. Then
			\begin{align*}
				F \circ \id_{\MC}(A) 
				& = F(\id_{\MC}(A)) \\
				& = F(A) 
			\end{align*}
			and 
			\begin{align*}
				F \circ \id_{\MC}(f) 
				& = F (\id_{\MC}(f)) \\
				& = F(f)
			\end{align*} 
			Since $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$ are arbitrary, $ F \circ \id_{\MC} = F$.
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{ex:basics:functors:small_cat:0007}
		Let $\MC$ and $\MD$ be categories and $F:\MC \rightarrow \MD$. If $\MC$ is small, then $F$ is a set.
	\end{ex}
	
	\begin{proof}
		Suppose that $\MC$ is small. Then $\Obj(\MC)$ and $\Hom_{\MC}$ are sets. By definition, there exist $F_0: \Obj(\MC) \rightarrow \Obj(\MD)$ and $F_1: \Hom_{\MC} \rightarrow \Hom_{\MD}$ such that $F = (F_0, F_1)$. \rax{11001.1} implies that $F_0(\Obj(\MC))$ and $F_1(\Hom_{\MC})$ are sets. Therefore, $\Obj(\MC) \times F_0(\Obj(C))$ and $\Hom_{\MC} \times F_1(\Hom_{\MC})$ are sets. Hence $\MP(\Obj(\MC) \times F_0(\Obj(C)))$ and $\MP(\Hom_{\MC} \times F_1(\Hom_{\MC}))$ are sets. Since $F_0 \subset \Obj(\MC) \times F_0(\Obj(C))$ and $F_1 \subset \Hom_{\MC} \times F_1(\Hom_{\MC})$, we have that $F_0 \in \MP(\Obj(\MC) \times F_0(\Obj(C)))$ and $F_1 \in \MP(\Hom_{\MC} \times F_1(\Hom_{\MC}))$. Hence $F_0$ and $F_1$ are sets. Thus $F = (F_0, F_1)$ is a set. 
	\end{proof}

	\begin{ex} \lex{ex:basics:functors:small_cat:0008}
		Let $\MC$ and $\MD$ be categories. Suppose that $\MC$ is small. Then there exists a class $A$ such that for each class $F$, $F \in A$ iff $F: \MC \rightarrow \MD$.   
	\end{ex}
	
	\begin{proof} 
		Let $\MC$ and $\MD$ be categories. Suppose that $\MC$ is small. Define $\phi$ by 
		$$\phi(F) : F : \MC \rightarrow \MD$$ 
		Then there exists a class $A$ such that for each set $F$, $F \in A$ iff $\phi(F)$. Let $F$ be a class. Suppose that $F \in A$. By \rd{11001}, $F$ is a set. Since $F$ is a set and $F \in A$, we have that $\phi(F)$. Hence $F: \MC \rightarrow \MD$. \\
		Conversely, suppose that $F: \MC \rightarrow \MD$. \rex{ex:basics:functors:small_cat:0007} implies that $F$ is a set. Since $F$ is a set and $\phi(F)$ is true, we have that $F \in A$. 
	\end{proof}
	
	\begin{defn} \ld{def:basics:functors:small_cat:0009}
		We define $\tbf{Cat}$ by 
		\begin{itemize}
			\item $\Obj(\tbf{Cat}) = \{\MC: \MC \text{ is a small category}\}$.
			\item for $\MC,\MD \in \Obj(\tbf{Cat})$, 
			$$\Hom_{\tbf{Cat}}(\MC,\MD) = \{F : F: \MC \rightarrow \MD \}$$
			\item for $\MC,\MD, \ME \in \Obj(\tbf{Cat})$, $F \in \Hom_{\tbf{Cat}}(\MC,\MD)$ and $G \in \Hom_{\tbf{Cat}}(\MD, \ME)$, $$G \circ_{\tbf{Cat}} F = G \circ F$$
		\end{itemize}
	\end{defn}


	\begin{ex} \lex{ex:basics:functors:small_cat:0010}
		We have that \tbf{Cat} is 
		\begin{enumerate}
			\item a category
			\item locally small
		\end{enumerate} 
	\end{ex}

	\begin{proof}\
		\begin{enumerate}
			\item \rex{ex:basics:functors:small_cat:0002} implies that composition is well defined. \rex{ex:basics:functors:small_cat:0003} implies that composition is associative. \rex{ex:basics:functors:small_cat:0005} and \rex{ex:basics:functors:small_cat:0006} imply the existence of identities.
			\item Let $\MC, \MD \in \Obj(\tbf{Cat})$ and $F \in \Hom_{\tbf{Cat}}(\MC, \MD)$. \rd{12002} implies that $\Obj(\MC)$, $\Obj(\MD)$, $\Hom_{\MC}$ and $\Hom_{\MD}$ are sets. Then $\Obj(\MD)^{\Obj(\MC)}$ and $\Hom_{\MD}^{ \Hom_{\MC}}$ are sets. Hence $ \Obj(\MD)^{\Obj(\MC)} \times  \Hom_{\MD}^{ \Hom_{\MC}}$ is a set. Let $F \in \Hom_{\tbf{Cat}}(\MC, \MD)$. Then there exist $F_0 \in \Obj(\MD)^{\Obj(\MC)} $ and $F_1 \in \Hom_{\MD}^{ \Hom_{\MC}}$ such that $F = (F_0, F_1)$. Therefore $F \in  \Obj(\MD)^{\Obj(\MC)} \times  \Hom_{\MD}^{ \Hom_{\MC}}$. Since $F \in \Hom_{\tbf{Cat}}(\MC, \MD)$ is arbitrary, 
			\begin{align*}
				\Hom_{\tbf{Cat}}(\MC, \MD) 
				& \subset \Obj(\MD)^{\Obj(\MC)} \times  \Hom_{\MD}^{ \Hom_{\MC}}
			\end{align*}
			which implies that $\Hom_{\tbf{Cat}}(\MC, \MD)$ is a set. Therefore, $\tbf{Cat}$ is locally small.
		\end{enumerate} 
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	















	\subsection{Comma Categories}

	
	\begin{defn} \ld{def:basics:functors:comma_cat:0001}
		Let $\MA$, $\MB$, $\MC$ be a categories and $S: \MA \rightarrow \MC$, $T: \MB \rightarrow \MC$ functors. We define the \textbf{comma category of $S$ to $T$}, denoted $(S \doar T)$, by 
		\begin{itemize}
			\item $\Obj(S \doar T) = \{(A, B, h): A \in \Obj(\MA), B \in \Obj(\MB) \text{, and } h \in \Hom_{\MC}(S(A), T(B))\}$
			\item For $(A_1, B_1, h_1), (A_2, B_2, h_2) \in \Obj(S \doar T)$, 
			\begin{align*}
				& \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2)) = \\
				& \quad \quad \{(\al, \be): \al \in \Hom_{\MA}(A_1, A_2) \text{, } \be \in \Hom_{\MB}(B_1, B_2) \text{ and } T(\be) \circ_{\MC} h_1 = h_2 \circ_{\MC} S(\al)\}
			\end{align*}
			i.e. for $(A_1, B_1, h_1), (A_2, B_2, h_2) \in \Obj(S \doar T)$, $\al \in \Hom_{\MA}(A_1, A_2)$ and $\be \in \Hom_{\MB}(B_1, B_2)$, $(\al, \be) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2))$ iff the following diagram commutes:
			\[ 
			\begin{tikzcd}
				S(A_1) \arrow[r, "S(\al)"] \arrow[d, "h_1"'] & S(A_2)  \arrow[d, "h_2"] \\
				T(B_1) \arrow[r, "T(\be)"']                 & T(B_2)
			\end{tikzcd}
			\]
			\item For 
			\begin{itemize}
				\item $(A_1, B_1, h_1), (A_2, B_2, h_2), (A_3, B_3, h_3) \in \Obj(S \doar T)$
				\item $(\al_{12}, \be_{12}) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2))$
				\item $(\al_{23}, \be_{23}) \in \Hom_{(S \doar T)}((A_2, B_2, h_2), (A_3, B_3, h_3))$
			\end{itemize}
			we define 
			$$(\al_{23}, \be_{23}) \circ_{(S \doar T)} (\al_{12}, \be_{12}) = (\al_{23} \circ_{\MA} \al_{12}, \be_{23} \circ_{\MB} \be_{12})$$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:functors:comma_cat:0002}
		Let $\MA$, $\MB$, $\MC$ be a categories and $S: \MA \rightarrow \MC$, $T: \MB \rightarrow \MC$ functors. Then $(S \doar T)$ is a category.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item \textbf{well-definedness of composition:} \\
			Let 
			\begin{itemize}
				\item $(A_1, B_1, h_1), (A_2, B_2, h_2), (A_3, B_3, h_3) \in \Obj(S \doar T)$
				\item $(\al_{12}, \be_{12}) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2))$ 
				\item $(\al_{23}, \be_{23}) \in \Hom_{(S \doar T)}((A_2, B_2, h_2), (A_3, B_3, h_3))$
			\end{itemize}
			By definition, $\al_{12} \in \Hom_{\MA}(A_1, A_2)$, $\al_{23} \in \Hom_{\MA}(A_2, A_3)$, $\be_{12} \in \Hom_{\MB}(B_1, B_2)$, $\be_{23} \in \Hom_{\MB}(B_2, B_3)$, $T(\be_{12}) \circ_{\MC} h_1 = h_2 \circ S(\al_{12})$ and $T(\be_{23}) \circ_{\MC} h_2 = h_3 \circ_{\MC} S(\al_{23})$, \\
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				S(A_1) \arrow[r, "S(\al_{12})"] \arrow[d, "h_1"'] & S(A_2)  \arrow[d, "h_2"] \arrow[r, "S(\al_{23})"] 
				& S(A_3) \arrow[d, "h_3"]\\
				T(B_1) \arrow[r, "T(\be_{12})"']                  & T(B_2)                   \arrow[r, "T(\be_{23})"'] 
				& T(B_3) 
			\end{tikzcd}
			\]
			Then $\al_{23} \circ_{\MA} \al_{12} \in \Hom_{\MA}(A_1, A_3)$, $\be_{23} \circ_{\MB} \be_{12} \in \Hom_{\MB}(B_1, B_3)$ and 
			\begin{align*}
				T(\be_{23} \circ_{\MB} \be_{12}) \circ_{\MC} h_1
				& = (T(\be_{23}) \circ_{\MC} T(\be_{12})) \circ_{\MC} h_1 \\
				& = T(\be_{23}) \circ_{\MC} (T(\be_{12}) \circ_{\MC} h_1) \\
				& = T(\be_{23}) \circ_{\MC} (h_2 \circ_{\MC} S(\al_{12})) \\
				& = (T(\be_{23}) \circ_{\MC} h_2) \circ_{\MC} S(\al_{12}) \\
				& = (h_3 \circ_{\MC} S(\al_{23})) \circ_{\MC} S(\al_{12}) \\
				& = h_3 \circ_{\MC} (S(\al_{23}) \circ_{\MC} S(\al_{12})) \\
				& = h_3 \circ_{\MC} S(\al_{23} \circ_{\MA} \al_{12})
			\end{align*}
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				S(A_1) \arrow[rr, "S(\al_{23} \circ_{\MA} \al_{12})"] \arrow[d, "h_1"']&  & S(A_3)  \arrow[d, "h_3"] \\
				T(B_1) \arrow[rr, "T(\be_{23} \circ_{\MB} \be_{12})"']                       &  & T(B_3)
			\end{tikzcd}
			\]
			Hence $(\al_{23} \circ_{\MA} \al_{12}, \be_{23} \circ_{\MB} \be_{12}) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_3, B_3, h_3))$ and composition is well defined. \\
			\item \textbf{associativity of composition:} \\
			Let 
			\begin{itemize}
				\item $(A_1, B_1, h_1), (A_2, B_2, h_2), (A_3, B_3, h_3), (A_4, B_4, h_4) \in \Obj(S \doar T)$
				\item $(\al_{12}, \be_{12}) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2))$ 
				\item $(\al_{23}, \be_{23}) \in \Hom_{(S \doar T)}((A_2, B_2, h_2), (A_3, B_3, h_3))$
				\item $(\al_{34}, \be_{34}) \in \Hom_{(S \doar T)}((A_3, B_3, h_3), (A_4, B_4, h_4))$
			\end{itemize}
			Then 
			\begin{align*}
				[ (\al_{34}, \be_{34}) \circ_{(S \doar T)} (\al_{23}, \be_{23}) ] \circ_{(S \doar T)} (\al_{12}, \be_{12})
				& = (\al_{34} \circ_{\MA} \al_{23}, \be_{34} \circ_{\MB} \be_{23}) \circ_{(S \doar T)} (\al_{12}, \be_{12}) \\
				& = ([\al_{34} \circ_{\MA} \al_{23}] \circ_{\MA} \al_{12}, [\be_{34} \circ_{\MB} \be_{23}] \circ_{\MB} \be_{12}) \\
				& =  (\al_{34} \circ_{\MA} [\al_{23} \circ_{\MA} \al_{12}], \be_{34} \circ_{\MB} [\be_{23} \circ_{\MB} \be_{12}]) \\
				& = (\al_{34}, \be_{34}) \circ_{(S \doar T)} (\al_{23} \circ_{\MA} \al_{12}, \be_{23} \circ_{\MB} \be_{12}) \\
				& = (\al_{34}, \be_{34}) \circ_{(S \doar T)} [(\al_{23}, \be_{23}) \circ_{(S \doar T)} (\al_{12}, \be_{12})]
			\end{align*}
			So composition is associative. \\
			\item \textbf{existence of identities:} \\
			Let
			\begin{itemize}
				\item $(A_1, B_1, h_1), (A_2, B_2, h_2), \in \Obj(S \doar T)$
				\item $(\al, \be) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2))$ 
			\end{itemize}
			By definition, 
			\begin{itemize}
				\item $\al \in \Hom_{\MA}(A_1, A_2)$, $\be \in \Hom_{\MB}(B_1, B_2)$
				\item $h_1 \in \Hom_{\MC}(S(A_1), T(B_1))$, $h_2 \in \Hom_{\MC}(S(A_2), T(B_2))$ 
				\item $T(\be) \circ h_1 = h_2 \circ S(\al)$
			\end{itemize}
			Since $\id_{A_1} \in \Hom_{\MA}(A_1, A_1)$, $\id_{B_1} \in \Hom_{\MB}(B_1, B_1)$, and
			\begin{align*}
				T(\id_{B_1}) \circ_{\MC}  h_1 
				& = \id_{T(B_1)} \circ_{\MC} h_1 \\
				& = h_1 \\
				& = h_1 \circ_{\MC} \id_{S(A_1)} \\
				& = h_1 \circ_{\MC} S(\id_{A_1}) 
			\end{align*}
			i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				S(A_1) \arrow[r, "S(\id_{A_1})"] \arrow[d, "h_1"']  & S(A_1)  \arrow[d, "h_1"] \\
				T(B_1) \arrow[r, "T(\id_{B_1})"']                   & T(B_1)
			\end{tikzcd}
			\]
			we have that $(\id_{A_1}, \id_{B_1}) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_1, B_1, h_1))$. Similarly $(\id_{A_2}, \id_{B_2}) \in \Hom_{(S \doar T)}((A_2, B_2, h_2), (A_2, B_2, h_2))$. Therefore
			\begin{align*}
				(\al, \be) \circ_{(S \doar T)} (\id_{A_1}, \id_{B_1}) 
				& = (\al \circ_{\MA} \id_{A_1}, \be \circ_{\MB} \id_{B_1}) \\
				& = (\al, \be)
			\end{align*}
			and 
			\begin{align*}
				(\id_{A_2}, \id_{B_2}) \circ_{(S\doar T)} (\al, \be) 
				& = (\id_{A_2} \circ_{\MA} \al ,  \id_{B_2} \circ_{\MB} \be ) \\
				& = (\al, \be)
			\end{align*}
			Since $(A_1, B_1, h_1), (A_2, B_2, h_2), \in \Obj(S \doar T)$ and\\ $(\al, \be) \in \Hom_{(S \doar T)}((A_1, B_1, h_1), (A_2, B_2, h_2))$ are arbitrary, we have that for each $(A, B, h) \in \Obj(S \doar T)$, $\id_{(A, B, h)} = (\id_A, \id_B)$.
		\end{itemize}
	\end{proof}
	
	\begin{defn}
		\tcr{define the arrow category of $\MC$} \href{URL}{text}
	\end{defn}

	\begin{note}
		\tcr{explain with diagram how in the case $\al = \Del^{\1}_X$ and how we can contract one edge of the rectangle diagram to get a triangle}
	\end{note}

	\begin{defn} \ld{def:basics:functors:comma_cat:0003}
		Let $\MC, \MD$ be a categories, $X \in \Obj(\MD)$ and $F: \MC \rightarrow \MD$. We define the \textbf{comma category from $X$ to $F$}, denoted $(X \doar F)$, by $(X \doar F) \defeq (\Del^{\1}_X \doar F)$. \\
		We may make the following identification:
		\begin{itemize}
			\item $\Obj(X \doar F) = \{(A, f): A \in \Obj(\MC) \text{ and } f \in \Hom_{\MD}(X, F(A))\}$ 
			\item For $(A_1, f_1), (A_2, f_2) \in \Obj(X \doar F)$, 
			$$\Hom_{(X \doar F)}((A_1, f_1), (A_2, f_2)) = \{\al \in \Hom_{\MC}(A_1, A_2) \text{ and } F(\al) \circ f_1 = f_2\}$$
			i.e. for $(A_1, f_1), (A_2, f_2) \in \Obj(X \doar F)$ and $\al \in \Hom_{A_1, A_2}$, $\al \in \Hom_{(X \doar F)}((A_1, f_1), (A_2, f_2))$ iff the following diagram commutes:
			\[ 
			\begin{tikzcd}
				&  X \arrow[dl, "f_1"']  \arrow[dr, "f_2"] & \\
				F(A_1)  \arrow[rr, "F(\al)"'] &&  F(A_2) \\ 
			\end{tikzcd}
			\]
			\item For 
			\begin{itemize}
				\item $(A_1, f_1), (A_2, f_2), (A_3, f_3) \in \Obj(X \doar F)$
				\item $\al \in \Hom_{(X \doar F)}((A_1, f_1), (A_2, f_2))$
				\item $\be \in \Hom_{(X \doar F)}((A_2, f_2), (A_3, f_3))$
			\end{itemize}
			we define 
			$$\be \circ_{(X \doar F)} \al = \be \circ_{\MC} \al $$
		\end{itemize}
	\end{defn}
	
	\begin{note}
		\tcr{note that the coslice category under $X$ is a comma categroy from $X$ to $\id_{\MC}$}
	\end{note}

	\begin{defn} \ld{def:basics:functors:comma_cat:0004}
		Let $\MC, \MD$ be a categories, $X \in \Obj(\MD)$ and $F: \MC \rightarrow \MD$. We define the \textbf{comma category from $F$ to $X$}, denoted $(F \doar X)$, by $(F \doar X) \defeq (F \doar \Del^{\1}_X)$.\\
		We may make the following identification:
		\begin{itemize}
			\item $\Obj(F \doar X) = \{(A, f): A \in \Obj(\MC) \text{ and } f \in \Hom_{\MD}(F(A), X)\}$ 
			\item For $(A_1, f_1), (A_2, f_2) \in \Obj(F \doar X)$, 
			$$\Hom_{(X \doar F)}((A_1, f_1), (A_2, f_2)) = \{\al \in \Hom_{\MC}(A_1, A_2) \text{ and } f_2 \circ F(\al)  = f_1\}$$
			i.e. for $(A_1, f_1), (A_2, f_2) \in \Obj(F \doar X)$ and $\al \in \Hom_{A_1, A_2}$, $\al \in \Hom_{(F \doar X)}((A_1, f_1), (A_2, f_2))$ iff the following diagram commutes:
			\[ 
			\begin{tikzcd}
				F(A_1) \arrow[dr, "f_1"'] \arrow[rr, "F(\al)"] &&  F(A_2) \arrow[dl, "f_2"]\\
				& X  & 
			\end{tikzcd}
			\]
			\item For 
			\begin{itemize}
				\item $(A_1, f_1), (A_2, f_2), (A_3, f_3) \in \Obj(F \doar X)$
				\item $\al \in \Hom_{(F \doar X)}((A_1, f_1), (A_2, f_2))$
				\item $\be \in \Hom_{(F \doar X)}((A_2, f_2), (A_3, f_3))$
			\end{itemize}
			we define 
			$$\be \circ_{(F \doar X)} \al = \be \circ_{\MC} \al $$
		\end{itemize}
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\begin{defn} \ld{12006}
		Let $\MC$ be a category and $X \in \Obj(\MC)$. We define the \textbf{arrow category of $\MC$}, denoted $\Arr(\MC)$, by $\Arr(\MC) \defeq (\id_{\MC} \downarrow \id_{\MC})$.
	\end{defn}
	
	\begin{defn} \ld{12007}
		Let $\MC$ be a category and $X \in \Obj(\MC)$. We define the \textbf{slice category of $\MC$ over $X$} or the \textbf{over category of $\MC$ over $X$}, denoted $\MC \downarrow X$, by $\MC \downarrow X \defeq (\id_{\MC} \downarrow X)$.
	\end{defn}
	
	
	\begin{defn} \ld{12008}
		Let $\MC$ be a category and $X \in \Obj(\MC)$. We define the \textbf{coslice category of $\MC$ over $X$} or the \textbf{under category of $\MC$ under $X$}, denoted $X \downarrow \MC$, by $X \downarrow \MC \defeq (X \downarrow \id_{\MC})$.
	\end{defn}

	\tcr{give examples in posets, and other}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Natural Transformations}
	
	\subsection{Introduction}
	
	\begin{defn} \ld{def:basics:nat_trans:intro:0001}
		Let $\MC$ and $\MD$ be categories, $F, G: \MC \rightarrow \MD$ and $ \al : \Obj(\MC) \rightarrow  \Hom_{\MD}$. Then $\al$ is said to be a \textbf{natural transformation from $F$ to $G$}, denoted $\al: F \Rightarrow G$, if
		\begin{enumerate}
			\item for each $A \in \Obj(\MC)$, $\al_A \in \Hom_{\MD}(F(A), G(A))$
			\item for each $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$, $G(f) \circ \al_A = \al_B \circ F(f)$, i.e. the following diagram commutes: 
			\[ 
			\begin{tikzcd}
				F(A)  \arrow[r, "\al_A"]  \arrow[d, "F(f)"']  & G(A)   \arrow[d, "G(f)"]\\
				F(B) \arrow[r, "\al_B"'] &  G(B) 
			\end{tikzcd}
			\]
		\end{enumerate}
	\end{defn}
	
	
	\begin{defn} \ld{def:basics:nat_trans:intro:0002} \tbf{Horizontal Composition:} \\
		Let $\MA, \MB, \MC$ be categories, $F, G:\MA \rightarrow \MB$, $F', G': \MB \rightarrow \MC$ functors and $\al: F \Rightarrow G$, $\al' : F' \Rightarrow G'$ natural transformations. We define the \textbf{horizontal composition of $\be$ with $\al$}, denoted $\be * \al: F' \circ F \Rightarrow G' \circ G$, by  
		$$(\al' * \al)_A = \al'_{G(A)} \circ F' (\al_A)$$ 
	\end{defn}
	
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0003}
		Let $\MA, \MB, \MC$ be categories, $F, G:\MA \rightarrow \MB$, $F', G': \MB \rightarrow \MC$ functors and $\al: F \Rightarrow G$, $\al' : F' \Rightarrow G'$ natural transformations. Then $ \al' \circ \al: F' \circ F \Rightarrow G' \circ G$ is a natural transformation.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A \in \Obj(\MA)$. Since $\al: F \Rightarrow G$, we have that $\al_A \in \Hom_{\MB}(F(A), G(A))$. Since $F':\MB \rightarrow \MC$, we have that 
			\begin{align*}
				F'(\al_A) 
				& \in \Hom_{\MC}(F'(F(A)), F'(G(A))) \\
				& = \Hom_{\MC}(F' \circ F(A), F' \circ G(A)).
			\end{align*}
			Since $G:\MA \rightarrow \MB$, we have that $G(A) \in \Obj(\MB)$. Since $\al':F' \Rightarrow G'$, we have that  
			\begin{align*}
				\al'_{G(A)} 
				& \in \Hom_{\MC}(F'(G(A)), G'(G(A))) \\
				& = \Hom_{\MC}(F' \circ G(A), G' \circ G(A)). 
			\end{align*}
			Therefore 
			\begin{align*}
				(\al' * \al)_A 
				& = \al'_{G(A)} \circ F' (\al_A) \\
				& \in \Hom_{\MC}(F' \circ F(A), G' \circ G(A)).
			\end{align*}
			Since $A \in \Obj(\MA)$ is arbitrary, we have that for each $A \in \Obj(\MA)$, $(\al' * \al)_A \in \Hom_{\MC}(F' \circ F(A), G' \circ G(A))$.
			\item Let $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$. Since $F,G:\MA \rightarrow \MB$, we have that $F(f) \in \Hom_{\MB}(F(A_1), F(A_2))$ and $G(f) \in \Hom_{\MB}(G(A_1), G(A_2))$. Since $\al: F \Rightarrow G$, we have that for each $k \in [2]$, $\al_{A_k} \in \Hom_{\MB}(F(A_k), G(A_k))$ and $G(f) \circ \al_{A_1} = \al_{A_2} \circ F(f)$, i.e. the following diagram commutes: 
			\[ 
			\begin{tikzcd}
				F(A_1)  \arrow[r, "\al_{A_1}"]  \arrow[d, "F(f)"']  & G(A_1)   \arrow[d, "G(f)"]\\
				F(A_2) \arrow[r, "\al_{A_2}"'] &  G(A_2) 
			\end{tikzcd}
			\]
			Since $F',G': \MB \rightarrow \MC$, we have that 
			\begin{align*}
				F' \circ F(f)
				& = F'(F(f)) \\
				& \in \Hom_{\MC}(F'(F(A_1)), F'(F(A_2))) \\
				& = \Hom_{\MC}(F' \circ F(A_1), F' \circ F(A_2)),
			\end{align*}
			\begin{align*}
				F' \circ G(f)
				& = F'(G(f)) \\
				& \in \Hom_{\MC}(F'(G(A_1)), F'(G(A_2))) \\
				& = \Hom_{\MC}(F' \circ G(A_1), F' \circ G(A_2)),
			\end{align*}
			\begin{align*}
				G' \circ G(f)
				& = G'(G(f)) \\
				& \in \Hom_{\MC}(G'(G(A_1)), G'(G(A_2))) \\
				& = \Hom_{\MC}(G' \circ G(A_1), G' \circ G(A_2)),
			\end{align*}
			and for each $k \in [2]$, 
			\begin{align*}
				F'(\al_{A_k}) 
				& \in \Hom_{\MC}(F'(F(A_k)), F'(G(A_k))) \\
				& = \Hom_{\MC}(F' \circ F(A_k), F' \circ G(A_k)).
			\end{align*}
			Since $\al': F' \Rightarrow G'$, we have that for each $k \in [2]$, 
			\begin{align*}
				\al'_{G(A_k)}
				& \in \Hom_{\MC}(F'(G(A_k)), G'(G(A_k))) \\
				& = \Hom_{\MC}(F' \circ G(A_k), G' \circ G(A_k)).
			\end{align*}
			Therefore 
			\begin{align*}
				[F' \circ G (f)] \circ F'(\al_{A_1})
				& = F'(G(f)) \circ F'(\al_{A_1}) \\
				& = F'(G(f) \circ \al_{A_1}) \\
				& = F'(\al_{A_2} \circ F(f)) \\
				& = F'(\al_{A_2}) \circ F'(F(f)) \\
				& = F'(\al_{A_2}) \circ [F' \circ F(f)],
			\end{align*}
			and 
			\begin{align*}
				[G' \circ G(f)] \circ \al'_{G(A_1)}
				& = G'(G(f)) \circ \al'_{G(A_1)} \\
				& = \al'_{G(A_2)} \circ F'(G(f)) \\
				& =  \al'_{G(A_2)} \circ [F' \circ G(f)],
			\end{align*}
			i.e. the following diagram commutes: 
			\[ 
			\begin{tikzcd}
				F' \circ F(A_1)  \arrow[r, "F'(\al_{A_1})"]  \arrow[d, "F' \circ F(f)"']  & F' \circ G(A_1)   \arrow[d, "F' \circ G(f)"] \arrow[r, "\al'_{G(A_1)}"]    & G' \circ G(A_1)   \arrow[d, "G' \circ G(f)"] \\
				F' \circ F(A_2) \arrow[r, "F'(\al_{A_2})"'] &  F' \circ G(A_2) \arrow[r, "\al'_{G(A_2)}"'] &  G' \circ G(A_2) 
			\end{tikzcd}
			\] 
			Hence 
			\begin{align*}
				[G' \circ G(f)] \circ (\al' * \al)_{A_1}
				& = [G' \circ G(f)] \circ [\al'_{G(A_1)} \circ F'(\al_{A_1})] \\
				& = ([G' \circ G(f)] \circ \al'_{G(A_1)}) \circ F'(\al_{A_1}) \\
				& = (\al'_{G(A_2)} \circ [F' \circ G(f)]) \circ F'(\al_{A_1}) \\
				& = \al'_{G(A_2)} \circ ([F' \circ G(f)] \circ F'(\al_{A_1})) \\
				& = \al'_{G(A_2)} \circ (F'(\al_{A_2}) \circ [F' \circ F(f)]) \\
				& = [\al'_{G(A_2)} \circ F'(\al_{A_2})] \circ [F' \circ F(f)] \\
				& = (\al' * \al)_{A_2} \circ [F' \circ F(f)],
			\end{align*}
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				F' \circ F(A_1)  \arrow[r, "(\al' * \al)_{A_1}"]  \arrow[d, "F' \circ F(f)"']  & G' \circ G(A_1)   \arrow[d, "G' \circ G(f)"]\\
				F' \circ F(A_2) \arrow[r, "(\al' * \al)_{A_2}"'] &  G' \circ G(A_2) 
			\end{tikzcd}
			\]
			Since $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$ are arbitrary, we have that for each $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$, $[G' \circ G(f)] \circ (\al' * \al)_{A_1} = (\al' * \al)_{A_2} \circ [F' \circ F(f)]$.
		\end{enumerate}
		Thus $\al' * \al: F' \circ F \Rightarrow G' \circ G$.
	\end{proof}
	
	
	
	
	\begin{defn} \ld{def:basics:nat_trans:intro:0004} \tbf{Whiskering:}
		\begin{itemize}
			\item 
			\item 
		\end{itemize}
		\tcr{FINISH!!!}
	\end{defn}
	
	
	

	\tcr{talk about following example}
	\href{https://pseudonium.github.io/2026/01/20/Preimages_Preserve_Subset_operations.html}{preimages and set comprehension vs post composition and predicates}
	\tcr{will need to talk about contravariant functors from $\text{preim}, \text{pred}$, denoted $F,G:\bSet \rightarrow \bSet$ respectively given by $F(X) \defeq \MP(X)$, $F(f) \defeq f^{-1}$ and $G(X) \defeq \{0,1\}^X$, $G(f) \defeq - \circ f$.}	
	This post/functor is interesting because it highlights the associativity of $(\text{NOT} \circ \phi) \circ f = \text{NOT} \circ (\phi \circ f)$ as a commutativity $f^{-1}(A^c) = (f^{-1}(A))^c$. That is if $X = f^{-1}$ and $Y = -^c$, then $XYA = YXA$ so that $XY = YX$. It begs the question whether or not commutativity can always be recast as associativity in some other context. 
	
	
	\tcr{below is wild speculation and off topic question}
	The author writes that associativity shows you that for any appropriate $f, \phi$, post composing with $\text{NOT}$ first and then pre composing with $f$ vs precomposing with $f$ first then poste composing with $\text{NOT}$ are the same thing and in a sense orthogonal and independent, as in they do not affect the outcome. So is there a general view in which associativity (or via natural transformation commutativity) is a measure of independence? 
	
	Can we connect this with probability/physics in an information theoretic sense using the motivation/intuition that the kl divergence (or other notion of info loss) is a functor? i.e. $XY = YX$ or $x \circ (y \circ a) = (x \circ y) \circ a$ iff $\text{info\_loss}[\text{joint}(X,Y), \otimes(X,Y)] = 0$ or some generalization? We would need a notion of joint for $X$ and $Y$ and a (not product because category of prob dists doesnt have products) tensor product, so maybe we need to consider monoidal cats) 
	
	what $X,Y$ would correspond to classical/quantum probability? In the classical/quantum case, $X,Y$ are marginal systems and $\text{joint}(X,Y)$ is the given bipartite system from which we isolate the marginals. In the classical case, $\text{info\_loss}[\text{joint}(X,Y), \otimes(X,Y)] = 0$ iff $\text{joint}(X,Y) = \otimes(X,Y)]$, that is, there is the two marginal states of the bipartite system contain as much information as the bipartite system itself, i.e. there is no interaction. Im not sure what the associated commuting/associative operations would be, but maybe we can get a clue from the above example or by looking further into similar examples, maybe toposes or other tools cover this? 
	
	If it were possible to find commutative/associative operations that capture two subsystems being independent and not having an interaction in the classical/quantum probabilistic sense, then this would seem to suggest that we would be able to recast interaction between subsystems in terms of some associative/commutative operations. How would this compare/contrast with the characterization of interaction via homological algebra using exactness? 
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	





	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Category of Functors}
	
	\begin{defn} \ld{def:basics:nat_trans:cat_funct:0001} \tbf{Vertical Composition:} \\
		Let $\MC$, $\MD$ be categories, $F, G, H:\MC \rightarrow \MD$ functors and $\al: F \Rightarrow G$, $\be : G \Rightarrow H$ natural transformations. We define the \textbf{vertical composition of $\be$ with $\al$}, denoted $\be \circ \al: F \Rightarrow H$, by 
		$$(\be \circ \al)_{A} = \be_A \circ \al_A$$ 
	\end{defn}
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0002}
		Let $\MC$, $\MD$ be categories, $F, G, H:\MC \rightarrow \MD$ functors and $\al: F \Rightarrow G$, $\be : G \Rightarrow H$ natural transformations. Then $ \be \circ \al: F \Rightarrow H$ is a natural transformation.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A \in \Obj(\MC)$. Since $\al_A \in \Hom_{\MD}(F(A), G(A))$ and $\be_A \in \Hom_{\MD}(G(A), H(A))$, we have that 
			\begin{align*}
				(\be \circ \al)_A 
				& = \be_A \circ \al_A \\
				& \in \Hom_{\MD}(F(A), H(A))
			\end{align*}
			\item Let $A,B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Since $\al:F \Rightarrow G$ and $\be: G \Rightarrow H$, $G(f) \circ \al_A = \al_B \circ F(f)$ and $H(f) \circ \be_A = \be_B \circ G(f)$. Therefore 
			\begin{align*}
				H(f) \circ (\be \circ \al)_A
				& = H(f) \circ (\be_A \circ \al_A) \\
				& = (H(f) \circ \be_A) \circ \al_A \\
				& = (\be_B \circ G(f)) \circ \al_A \\
				& = \be_B \circ (G(f)\circ \al_A) \\
				& = \be_B \circ (\al_B \circ F(f)) \\
				& = (\be_B \circ \al_B) \circ F(f) \\
				& = (\be \circ \al)_B \circ F(f)
			\end{align*}
		\end{enumerate}
		So $\be \circ \al: F \Rightarrow H$ is a natural transformation. 
	\end{proof}

	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0003}
		Let $\MC$, $\MD$ be categories, $F, G, H, K:\MC \rightarrow \MD$ functors and $\al: F \Rightarrow G$, $\be : G \Rightarrow H$ and $\gam: H \Rightarrow K$ natural transformations. Then $$(\gam \circ \be) \circ \al = \gam \circ (\be \circ \al)$$
	\end{ex}

	\begin{proof}
		Let $A \in \Obj(\MC)$. By definition,  
		\begin{align*}
			[(\gam \circ \be) \circ \al]_{A} 
			& = (\gam \circ \be)_A \circ \al_{A} \\
			& = (\gam_A \circ \be_A) \circ \al_A \\
			& = \gam_A \circ (\be_A \circ \al_A) \\
			& = \gam_A \circ (\be \circ \al)_A \\
			& = [\gam \circ (\be \circ \al)]_A \\
		\end{align*}
		Since $A \in \Obj(\MC)$ is arbitrary, 
		$$(\gam \circ \be) \circ \al = \gam \circ (\be \circ \al)$$
	\end{proof}

	\begin{defn} \ld{def:basics:nat_trans:cat_funct:0004}
		Let $\MC$, $\MD$ be categories and $F: \MC \rightarrow \MD$. We define the \textbf{identity natural transformation from $F$ to $F$}, denoted $\id_F: F \Rightarrow F$, by 
		$$(\id_F)_A = \id_{F(A)}^{\MD}$$
	\end{defn}
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0005}
		Let $\MC$, $\MD$ be categories and $F: \MC \rightarrow \MD$. Then $\id_F: F \Rightarrow F$ is a natural transformation.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				(\id_F)_A 
				& = \id_{F(A)}^{\MD} \\
				& \in \Hom_{\MD}(F(A), F(A))
			\end{align*}
			\item Let $A,B \in \Obj(\MC)$, $f \in \Hom_{\MC}(A,B)$. Then 
			\begin{align*}
				F(f) \circ_{\MD} (\id_F)_A
				& = F(f) \circ_{\MD} \id_{F(A)}^{\MD} \\
				& = F(f) \\
				& = \id_{F(B)}^{\MD} \circ_{\MD} F(f) \\
				& = (\id_F)_{B} \circ_{\MD} F(f),
			\end{align*}
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				F(A)  \arrow[r, "(\id_F)_A"]  \arrow[d, "F(f)"']  & F(A)   \arrow[d, "F(f)"]\\
				F(B) \arrow[r, "(\id_F)_B"] &  F(B). \\
			\end{tikzcd}
			\]
		\end{enumerate}
	\end{proof}

	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0006}
		Let $\MC$, $\MD$ be categories, $F,G: \MC \rightarrow \MD$ and $\al : F \Rightarrow G$. Then 
		\begin{enumerate}
			\item $\id_{G} \circ \al = \al$
			\item $\al \circ \id_F = \al$
		\end{enumerate} 
	\end{ex}

	\begin{proof}\
		\begin{enumerate}
			\item Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				(\id_{G} \circ \al)_{A}
				& = (\id_G)_A \circ \al_A \\
				& = \id_{G(A)} \circ \al_A \\
				& = \al_A 
			\end{align*}
			Since $A \in \Obj(C)$ is arbitrary, $\id_{G} \circ \al = \al$
			\item Let $A \in \Obj(\MC)$. Then
			\begin{align*}
				(\al \circ \id_F)_{A}
				& = \al_A \circ (\id_F)_A \\
				& = \al_A \circ \id_{F(A)} \\
				& = \al_A 
			\end{align*}
			Since $A \in \Obj(C)$ is arbitrary, $\al \circ \id_F = \al$.
		\end{enumerate}
	\end{proof}

	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0007}
		Let $\MC$ and $\MD$ be categories, $F,G: \MC \rightarrow \MD$ and $\al: F \Rightarrow G$. If $\MC$ is small, then $\al$ is a set.
	\end{ex}

	\begin{proof}
		Suppose that $\MC$ is small. Then $\Obj(\MC)$ is a set. Since $\al: \Obj(\MC) \rightarrow \Hom_{\MD}$, \rax{11001.1} implies that $\al(\Obj(\MC))$ is a set. Then $ \Obj(\MC) \times \al(\Obj(\MC))$ is a set. Therefore $\MP(\Obj(\MC) \times \al(\Obj(\MC)))$ is a set. Since $\al \subset \Obj(\MC) \times \al(\Obj(\MC))$, we have that $\al \in \MP(\Obj(\MC) \times \al(\Obj(\MC)))$ which implies that $\al$ is a set. 
	\end{proof}

	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0008}
			Let $\MC$ and $\MD$ be categories and $F,G: \MC \rightarrow \MD$. If $\MC$ is small, then there exists a class $A$ such that for each class $\al$, $\al \in A$ iff $\al: F \Rightarrow G$. 
	\end{ex}

	\begin{proof}
		Suppose that $\MC$ is small. Define $\phi$ by 
		$$\phi(\al): \al: F \Rightarrow G$$
		\rax{11002} implies that there exists a class $A$ such that for each set $\al$, $\al \in A$ iff $\phi(\al)$. 
		Let $\al$ be a class. Suppose that $\al \in A$. By \rd{11001}, $\al$ is a set. Since $\al$ is a set and $\al \in A$, we have that $\phi(\al)$. Hence $\al:F \Rightarrow G$. \\
		Conversely, suppose that $\al: F \Rightarrow G$.  Since $\MC$ is small, \rex{ex:basics:nat_trans:cat_funct:0007} implies that $\al$ is a set. Since $\phi(\al)$, we have that $\al \in A$. 
	\end{proof}
	
	\begin{defn} \ld{def:basics:nat_trans:cat_funct:0009}
		Let $\MC$ and $\MD$ be categories. Suppose that $\MC$ is small. We define the \textbf{functor category from $\MC$ to $\MD$}, denoted $\MD^{\MC}$, by 
		\begin{itemize}
			\item $\Obj(\MD^{\MC}) = \{F: F: \MC \rightarrow \MD\}$
			\item For $F, G \in \Obj(\MD^{\MC})$, $\Hom_{\MD^{\MC}}(F, G) = \{\al: \al: F \Rightarrow G \}$
			\item For $F, G, H \in \Obj(\MD^{\MC})$, $\al \in \Hom_{\MD^{\MC}}(F, G)$ and $\be \in \Hom_{\MD^{\MC}}(G, H)$, 
			$\be \circ_{\MD^{\MC}} \al = \be \circ \al $
		\end{itemize} 
	\end{defn}

	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0010}
		Let $\MC$ and $\MD$ be categories. Suppose that $\MC$ is small. Then $\MD^{\MC}$ is a category.
	\end{ex}

	\begin{proof}\
		\rex{ex:basics:nat_trans:cat_funct:0002} implies that composition is well-defined. \rex{ex:basics:nat_trans:cat_funct:0003} implies that composition is associative. \rex{ex:basics:nat_trans:cat_funct:0005} and \rex{ex:basics:nat_trans:cat_funct:0006} imply the existence of identities.  
	\end{proof}
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0011}
		Let $\MC$ and $\MD$ be categories. Suppose that $\MC$ and $\MD$ are small. Then $\MD^{\MC}$ is small.
	\end{ex}
	
	\begin{proof}
		We have that 
		\begin{align*}
			\text{$\MC$ and $\MD$ are small}
			& \iff \Obj(\MC), \Obj(\MD), \Hom_{\MC}, \Hom_{\MD} \in \Obj(\bSet) \\
			& \iff \Obj(\MD)^{\Obj(\MC)}, \Hom_{\MD}^{\Hom_{\MC}} \in \Obj(\bSet) \\
			& \iff \Obj(\MD)^{\Obj(\MC)} \times \Hom_{\MD}^{\Hom_{\MC}} \in \Obj(\bSet).
		\end{align*}
		Since $\MD^{\MC} \subset \Obj(\MD)^{\Obj(\MC)} \times \Hom_{\MD}^{\Hom_{\MC}}$ and $\MC$, $\MD$ are small, we have that $\MD^{\MC} \in \Obj(\bSet)$. Thus $\MD^{\MC}$ is small.
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Diagonal Functor}

	\begin{defn} \ld{def:basics:nat_trans:diag_funct:0001}
		Let $\MC$, $\MD$ be categories, $X, Y \in \Obj(\MD)$ and $f \in \Hom_{\MD}(X, Y)$. We define the \textbf{constant natural transformation on $\MC$ at $f$}, denoted $\del^{\MC}_f: \Del^{\MC}_X \Rightarrow \Del^{\MC}_Y$, by
		$$(\del^{\MC}_f)_A = f$$
	\end{defn}
	
	\begin{ex} \lex{ex:basics:nat_trans:diag_funct:0002}
		Let $\MC$, $\MD$ be categories, $X, Y \in \Obj(\MD)$ and $f \in \Hom_{\MD}(X, Y)$. Then $\del^{\MC}_f: \Del^{\MC}_X \Rightarrow \Del^{\MC}_Y $ is a natural transformation.
	\end{ex}
	
	\begin{proof} \
		\begin{enumerate}
			\item By definition, for each $A \in \Obj(\MC)$ $(\del^{\MC}_f)_A \in \Hom_{\MD}(\Del^{\MC}_X(A), \Del^{\MC}_Y(A))$.
			\item Let $A, B \in \Obj(\MC)$ and $g \in \Hom_{\MC}(A, B)$. Then 
			\begin{align*}
				\Del^{\MC}_Y(g) \circ (\del^{\MC}_f)_A 
				& = \id_Y \circ f \\
				& = f \\
				& = f \circ \id_X \\
				& = (\del^{\MC}_f)_B \circ \Del^{\MC}_X(g)  
			\end{align*}
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}[baseline= 7]
				\Del^{\MC}_X(A)  \arrow[r, "(\del^{\MC}_f)_A"]  \arrow[d, "\Del^{\MC}_X(g)"']  & \Del^{\MC}_Y(A)   \arrow[d, "\Del^{\MC}_Y(g)"]\\
				\Del^{\MC}_X(B) \arrow[r, "(\del^{\MC}_f)_B"] &  \Del^{\MC}_Y(B) \\
			\end{tikzcd}
			=
			\begin{tikzcd}[baseline= 7]
				X  \arrow[r, "f"]  \arrow[d, "\id_X"']  & Y   \arrow[d, "\id_Y"]\\
				X \arrow[r, "f"] &  Y \\
			\end{tikzcd}
			\]
		\end{enumerate}
		So $\del^{\MC}_f: \Del^{\MC}_X \Rightarrow \Del^{\MC}_Y$ is a natural transformation.
	\end{proof}
	 
	\begin{ex} \lex{ex:basics:nat_trans:diag_funct:0003}
		Let $\MC, \MD$ be categories, $X, Y, Z \in \Obj(\MD)$, $f \in \Hom_{\MD}(X,Y)$ and $g \in \Hom_{\MD}(Y,Z)$. Then $\del^{\MC}_{g \circ f} = \del^{\MC}_g \circ \del^{\MC}_f$.
	\end{ex}

	\begin{proof}
		Let $A \in \Obj(\MC)$. Then 
		\begin{align*}
			(\del^{\MC}_{g \circ f})_A
			& = g \circ f \\
			& = (\del^{\MC}_g)_A \circ (\del^{\MC}_f)_A \\
			& = (\del^{\MC}_g \circ \del^{\MC}_f)_A
		\end{align*}
		Since $A \in \Obj(\MC)$ is arbitrary, $\del^{\MC}_{g \circ f} = \del^{\MC}_g \circ \del^{\MC}_f$.
	\end{proof}

	\begin{ex} \lex{ex:basics:nat_trans:diag_funct:0004}
		Let $\MC, \MD$ be categories and $X \in \Obj(\MD)$. Then $\del^{\MC}_{\id_X} = \id_{\Del^{\MC}_X}$.
	\end{ex}

	\begin{proof}
		Let $A \in \Obj(\MC)$. Then 
		\begin{align*}
			(\del^{\MC}_{\id_X})_A
			& = \id_X \\
			& = \id_{\Del^{\MC}_X(A)} \\
			& = (\id_{\Del^{\MC}_X})_A 
		\end{align*}
		Since $A \in \Obj(\MC)$ is arbitrary, $\del^{\MC}_{\id_X} = \id_{\Del^{\MC}_X}$
	\end{proof}

	\begin{defn} \ld{def:basics:nat_trans:diag_funct:0005}
		Let $\MC$, $\MD$ be categories. Suppose that $\MC$ is small. We define the \textbf{$\MC$-ary diagonal functor} on $\MD$, denoted by $\Del^{\MC}: \MD \rightarrow \MD^{\MC}$, by
		\begin{itemize}
			\item $\Del^{\MC}(X) = \Del^{\MC}_X$
			\item $\Del^{\MC}(f) = \del^{\MC}_f$
		\end{itemize}
	\end{defn}

	\begin{ex} \lex{ex:basics:nat_trans:diag_funct:0006}
		Let $\MC$, $\MD$ be categories. Suppose that $\MC$ is small. Then $\Del^{\MC}: \MD \rightarrow \MD^{\MC}$ is a functor.
	\end{ex}

	\begin{proof}\
		\begin{enumerate}
			\item \rex{ex:basics:nat_trans:diag_funct:0002} implies that for each $X, Y \in \Obj(\MD)$ and $f \in \Hom_{\MD}(X, Y)$, $\Del^{\MC}(f) \in \Hom_{\MD^{\MC}} (\Del^{\MC}(X), \Del^{\MC}(Y))$
			\item \rex{ex:basics:nat_trans:diag_funct:0003} implies that for each $X, Y, Z \in \Obj(\MD)$, $f \in \Hom_{\MD}(X, Y)$ and $g \in \Hom_{\MD}(Y, Z)$, $\Del^{\MC}(g \circ f) = \Del^{\MC}(g) \circ \Del^{\MC}(f)$
			\item \rex{ex:basics:nat_trans:diag_funct:0004} implies that for each $X \in \Obj(\MD)$, $\Del^{\MC}(\id_X) = \id_{\Del^{\MC}(X)}$
		\end{enumerate}
		 So $\Del^{\MC} : \MD \rightarrow \MD^{\MC}$ is a functor.
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Isomorphisms}
	
	\subsection{Introduction}
	
	\begin{defn} 
		Let $\MC$ be a category.
		\begin{itemize}
			\item Let $A \in \Obj(\MC)$
			\begin{itemize}
				\item Let $f \in \Hom_{\MC}(A, A)$. Then $f$ is said to be an \textbf{endomorphism},
				\item We define $\End_{\MC}(A) \defeq \Hom_{\MC}(A, A)$.
			\end{itemize}
			\item We define $\End_{\MC} \defeq \bigcup\limits_{A \in \Obj(\MC)} \End_{\MC}(A)$.
		\end{itemize}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category
		\begin{itemize}
			\item Let $A, B \in \Obj(\MC)$.
			\begin{itemize}
				\item Let $f \in \Hom_{\MC}(A,B)$. Then $f$ is said to be an \textbf{isomorphism} if there exists $g \in \Hom_{\MC}(B, A)$ such that $g \circ f = \id_A$ and $f \circ g = \id_B$.
				\item We define $\Iso_{\MC}(A,B) \defeq \{f \in \Hom_{\MC}(A,B): \text{$f$ is an isomorphism}\}$
			\end{itemize}
			\item We define $\Iso_{\MC} \defeq \bigcup\limits_{(A,B) \in \Obj(\MC)^2} \Iso_{\MC}(A,B)$.
		\end{itemize}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category.
		\begin{itemize}
			\item Let $A \in \Obj(\MC)$
			\begin{itemize}
				\item Let $f \in \Iso_{\MC}(A, A)$. Then $f$ is said to be an \textbf{automorphism},
				\item We define $\Aut_{\MC}(A) \defeq \Iso_{\MC}(A, A)$.
			\end{itemize}
			\item We define $\Aut_{\MC} \defeq \bigcup\limits_{A \in \Obj(\MC)} \Aut_{\MC}(A)$.
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{15003} \textbf{Uniqueness of Inverses:} \\
		Let $\MC$ be a category, $A,B \in \Obj(\MC)$ and $f \in \Iso_{\MC}(A, B)$. Then there exists a unique $g \in \Iso_{\MC}(B, A)$ such that $g \circ f = \id_A$ and $f \circ g = \id_B$.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item \tbf{Existence:} \\
			By definition, since $f$ is an isomorphism, there exists $g \in \Hom_{\MC}(B, A)$ such that $g \circ f = \id_{A}$ and $f \circ g = \id_B$. By definition, $g \in \Iso_{\MC}(B, A)$.
			\item \tbf{Uniqueness: } \\
			Let $g' \in \Iso_{\MC}(B, A)$. Suppose that $g' \circ f = \id_A$, $f \circ g' = \id_B$. Then 
			\begin{align*}
				g'
				& = g' \circ \id_{B} \\
				& = g' \circ (f \circ g) \\
				& = (g' \circ f) \circ  g \\
				& = \id_A \circ g \\
				& = g
			\end{align*}
		\end{itemize}
	\end{proof}
	
	\begin{defn} \ld{15003.1}
		Let $\MC$ be a category, $A,B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$. Suppose that $f$ is an isomorphism. We define the \textbf{inverse of $f$}, denoted $f^{-1} \in \Iso_{\MC}(B, A)$, to be the unique $g \in \Iso_{\MC}(B, A)$ such that $g \circ f = \id_A$ and $f \circ g = \id_B$.
	\end{defn}
	
	\begin{ex} \lex{15004}
		Let $\MC$ be a category and $A \in \Obj(\MC)$. Then $\id_A \in \Aut_{\MC}(A)$ and $(\id_A)^{-1} = \id_A$. 
	\end{ex}
	
	\begin{proof}
		Since $\id_A \circ \id_A = \id_A$, we have that $\id_A \in \Aut_{\MC}(A)$ and $(\id_A)^{-1} = \id_A$. 
	\end{proof}
	
	\begin{ex} \lex{15005}
		Let $\MC$ be a category and $A, B \in \Obj(\MC)$. Then for each $f \in \Iso_{\MC}(A, B)$, $(f^{-1})^{-1} = f$.
	\end{ex}
	
	\begin{proof}
		Let $f \in \Iso_{\MC}(A, B)$. By definition, $f \circ f^{-1} = \id_{B}$ and $f^{-1} \circ f = \id_A$. Hence $(f^{-1})^{-1} = f$.
	\end{proof}
	
	\begin{ex} \lex{15006}
		Let $\MC$ be a category and $A,B,C \in \Obj(\MC)$. Then for each $f \in \Iso_{\MC}(A, B)$ and $g \in \Iso_{\MC}(B, C)$, $g \circ f \in \Iso_{\MC}(A, C)$ and $(g \circ f)^{-1} = f^{-1} \circ g^{-1}$. 
	\end{ex}
	
	\begin{proof}
		Let $f \in \Iso_{\MC}(A, B)$ and $g \in \Iso_{\MC}(B, C)$. Then 
		\begin{align*}
			(f^{-1} \circ g^{-1}) \circ (g \circ f) 
			& = ((f^{-1} \circ g^{-1}) \circ g) \circ f \\
			& = (f^{-1} \circ (g^{-1} \circ g)) \circ f \\
			& = (f^{-1} \circ \id_B) \circ f \\
			& = f^{-1} \circ f \\
			& = \id_{A}
		\end{align*}
		and 
		\begin{align*}
			(g \circ f) \circ (f^{-1} \circ g^{-1}) 
			& = ((g \circ f) \circ f^{-1}) \circ g^{-1} \\
			& = (g \circ (f \circ f^{-1})) \circ g^{-1} \\
			& = (g \circ \id_{B}) \circ g^{-1} \\
			& = g \circ  g^{-1} \\
			& = \id_{C}.
		\end{align*}
		Hence $g \circ f \in  \Iso_{\MC}(A, C)$ and $(g \circ f)^{-1} = f^{-1} \circ g^{-1}$.
	\end{proof}
	
	\begin{defn} \ld{15007}
		Let $\MC$ be a category. 
		\begin{itemize}
			\item Let $A,B \in \Obj(\MC)$. Then $A$ is said to be \textbf{isomorphic} to $B$ if $\Iso_{\MC}(A, B) \neq \varnothing$.
			\item We define the \tbf{isomorphism class relation on $\Obj(\MC)$}, denoted ${\cong_{\MC}} \in \MR(A, B)$, by $A \cong_{\MC} B$ iff $A$ is isomorphic to $B$. 
		\end{itemize}
	\end{defn}
	
	\begin{note}
		When the context is clear, we may write $\cong$ in place of $\cong_{\MC}$.
	\end{note}
	
	\begin{ex} \lex{15008}
		Let $\MC$ be a category. Then ${\cong} \in \Equi(\Obj(C))$ \tcr{does $\MC$ neet to be small or just locally small?}.
	\end{ex}
	
	\begin{proof} \
		\begin{enumerate}
			\item \textbf{reflexivity: } \\
			Let $A \in \Obj(\MC)$. \rex{15004} implies that $\id_A \in \Aut(A)$. Thus $A \cong A$. Since $A \in \Obj(\MC)$ is arbitrary, we have that for each $A \in \Obj(\MC)$, $A \cong A$ and thus $\cong$ is reflexive. 
			\item \textbf{symmetry: } \\
			Let $A, B \in \Obj(\MC)$. Suppose that $A \cong B$. Then there exists $f \in \Iso_{\MC}(A,B)$. \rex{15005} implies that $f^{-1} \in \Iso_{\MC}(B, A)$. Hence $B \cong A$.  Since $A, B \in \Obj(\MC)$ with $A \cong B$ are arbitrary, we have that for each $A, B \in \Obj(\MC)$, $A \cong B$ implies that $B \cong A$ and thus $\cong$ is reflexive. 
			\item \textbf{transitivity: }
			Let $A, B, C \in \Obj(\MC)$. Suppose that $A \cong B$ and $B \cong C$. Then there exist $f \in \Iso_{\MC}(A,B)$ and $g \in \Iso_{\MC}(B, C)$. \rex{15006} implies that $g \circ f \in \Iso_{\MC}(A, C)$. Thus $A \cong C$. Since $A, B, C \in \Obj(\MC)$ with $A \cong B$ and $B \cong C$ are arbitrary, we have that for each $A, B, C \in \Obj(\MC)$, $A \cong B$ and $B \cong C$ implies that $A \cong C$ and thus $\cong$ is transitive. 
		\end{enumerate}
		Thus ${\cong} \in \Equi(\Obj(C))$.
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Isomorphisms between Categories}
	
	\begin{ex}
		Let $\MC, \MD \in \Obj(\Cat)$ and $F \in \Hom_{\Cat}(\MC, \MD)$. Write $F = (F_0, F_1)$. Then $F \in \Iso_{\Cat}$ iff $F_0, F_1 \in \Iso_{\bSet}$
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item $(\implies)$: \\
			Suppose that $F \in \Iso_{\Cat}$. Then there exists $G \in \Hom_{\Cat}(\MD, \MC)$ such that $G \circ_{\Cat} F = \id_{\MC}$ and $F \circ_{\Cat} G = \id_{\MD}$. Write $G = (G_0, G_1)$. By \rd{def:basics:functors:small_cat:0001}, we have that $G_0 \circ_{\bSet} F_0 = \id_{\Obj(\MC)}^{\bSet}$, $F_0 \circ_{\bSet} G_0 = \id_{\Obj(\MD)}^{\bSet}$, $G_1 \circ_{\bSet} F_1 = \id_{\Hom_{\MC}}^{\bSet}$ and $F_1 \circ_{\bSet} G_1 = \id_{\Hom_{\MD}}^{\bSet}$. Hence $F_0, G_0 \in \Iso_{\bSet}$.  
			\item $(\impliedby)$: \\
			Suppose that $F_0, F_1 \in \Iso_{\bSet}$. Define $G_0 \defeq F_0^{-1}$ and  $G_1 \defeq F_1^{-1}$.
			\begin{enumerate}
				\item Let $A', B' \in \Obj(\MD)$ and $f' \in \Hom_{\MD}(A', B')$. Define $f \in \Hom_{\MC}$ and $A,B \in \Obj(\MC)$ by $f \defeq G_1(f')$, $A \defeq \dom(f)$ and $B \defeq \cod(f)$. Since $F \in \Hom_{\Cat}(\MC, \MD)$, we have that 
				\begin{align*}
					f'
					& = F_1(f) \\
					& \in \Hom_{\MD}(F_0(A), F_0(B)).
				\end{align*}   
				Since $f' \in \Hom_{\MD}(A', B')$, we have that 
				\begin{align*}
					A'
					& = \dom(f') \\
					& = F_0(A).
				\end{align*}
				Similarly, $B' = F_0(B)$. Hence $G_0(A') = A$, $G_0(B') = B$ and 
				\begin{align*}
					G_1(f')
					& = G_1(F_1(f)) \\
					& = f \\
					& \in \Hom_{\MC}(A, B) \\
					& =  \Hom_{\MC}(A, B) \\
					& = \Hom_{\MC}(G_0(A'), G_0(B')).
				\end{align*}
				\item Let $A',B', C' \in \Obj(\MD)$, $f' \in \Hom_{\MD}(A', B')$ and $g' \in \Hom_{\MD}(B', C')$. Define $f,g \in \Hom_{\MC}$ by $f \defeq G_1(f')$ and $g \defeq G_1(g')$. Then $F_1(f) = f'$ and $F_1(g) = g'$. Since $F \in \Hom_{\Cat}(\MC, \MD)$, we have that
				\begin{align*}
					G_1(g' \circ_{\MD} f')
					& = G_1(F_1(g) \circ_{\MD} F_1(f)) \\
					& = G_1(F_1( g \circ_{\MC} f)) \\
					& = g \circ_{\MC} f \\
					& = G_1(g') \circ_{\MC} G_1(f').
				\end{align*}
				\item Let $A' \in \Obj(\MD)$. Define $A \in \Obj(\MC)$ by $A \defeq G_0(A')$. Then $F_0(A) = A'$ and since $F \in \Hom_{\Cat}(\MC, \MD)$, we have that
				\begin{align*}
					G_1(\id_{A'}^{\MD})
					& = G_1(\id_{F_0(A)}^{\MD}) \\
					& = G_1(F_1(\id_A^{\MC})) \\
					& = \id_A^{\MC} \\
					& = \id_{G_0(A')}^{\MC}. 
				\end{align*}
			\end{enumerate}
			Hence $G \in \Hom_{\Cat}(\MD, \MC)$. By construction, $G \circ_{\Cat} F = \id_{\MC}$ and $F \circ_{\Cat} G = \id_{\MD}$. Thus $F \in \Iso_{\Cat}$.
		\end{itemize}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Natural Isomorphisms}
	
	\begin{defn} \ld{15011.1}
		Let $\MC$ and $\MD$ be categories, $F,G : \MC \rightarrow \MD$ and $\al: F \Rightarrow G$. Then $\al$ is said to be a \textbf{natural isomorphism} if for each $A \in \Obj(\MC)$, $\al_A \in \Iso_{\MD}(F(A), G(A))$. 
	\end{defn}
	
	\begin{defn} \ld{15011.2}
		Let $\MC$ and $\MD$ be categories, $F,G: \MC \rightarrow \MD$ and $\al : F \Rightarrow G$. Suppose that $\al$ is a natural isomorphism. We define $\al^{-1}: G \Rightarrow F$ by $(\al^{-1})_A = \al_A^{-1}$. 
	\end{defn}
	
	\begin{ex} \lex{15011.3}
		Let $\MC$ and $\MD$ be categories, $F,G: \MC \rightarrow \MD$ and $\al : F \Rightarrow G$. Suppose that $\al$ is a natural isomorphism. Then $\al^{-1}: G \Rightarrow F$ is a natural transformation
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A \in \Obj(\MC)$. Since $\al_A \in \Hom_{\MD}(F(A), G(A))$, we have that 
			\begin{align*}
				(\al^{-1})_A
				& = \al_A^{-1} \\
				& \in \Hom_{\MD}(G(A), F(A))
			\end{align*}
			\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Since $G(f) \circ \al_A = \al_B \circ F(f)$, i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				F(A)  \arrow[r, "\al_A"]  \arrow[d, "F(f)"']  & G(A)   \arrow[d, "G(f)"]\\
				F(B) \arrow[r, "\al_B"] &  G(B) \\
			\end{tikzcd}
			\]
			we have that 
			\begin{align*}
				F(f) \circ (\al^{-1})_A 
				& = F(f) \circ \al_A^{-1} \\
				& = \id_{F(B)} \circ (F(f) \circ \al_A^{-1}) \\
				& = (\al_B^{-1} \circ \al_B) \circ (F(f) \circ \al_A^{-1}) \\
				& = \al_B^{-1} \circ (\al_B \circ (F(f) \circ \al_A^{-1})) \\
				& = \al_B^{-1} \circ ((\al_B \circ F(f)) \circ \al_A^{-1}) \\
				& = \al_B^{-1} \circ ((G(f) \circ \al_A) \circ \al_A^{-1}) \\
				& = \al_B^{-1} \circ (G(f) \circ (\al_A \circ \al_A^{-1})) \\
				& = \al_B^{-1} \circ (G(f) \circ \id_{G(A)}) \\
				& = \al_B^{-1} \circ G(f) \\
				& = (\al^{-1})_B \circ G(f) 
			\end{align*}
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				G(A)  \arrow[r, "(\al^{-1})_A"]  \arrow[d, "G(f)"']  & F(A)   \arrow[d, "F(f)"]\\
				G(B) \arrow[r, "(\al^{-1})_B"] &  F(B) \\
			\end{tikzcd}
			\]
			So $\al^{-1}: G \Rightarrow F$.
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15011.4}
		Let $\MC$ and $\MD$ be categories, $F,G: \MC \rightarrow \MD$ and $\al : F \Rightarrow G$. Suppose that $\al$ is a natural isomorphism. Then $\al^{-1} \circ \al = \id_F$ and $\al \circ \al^{-1} = \id_G$.
	\end{ex}
	
	\begin{proof}
		Let $A \in \Obj(\MC)$. Then 
		\begin{align*}
			(\al^{-1} \circ \al )_A 
			& = (\al^{-1})_A \circ \al_A \\
			& = \al_A^{-1} \circ \al_A \\
			& = \id_{F(A)} \\
			& = (\id_F)_A
		\end{align*}
		and 
		\begin{align*}
			(\al \circ \al^{-1} )_A 
			& = \al_A \circ (\al^{-1})_A\\
			& = \al_A \circ \al_A^{-1}\\
			& = \id_{G(A)} \\
			& = (\id_G)_A
		\end{align*}
		Since $A \in \Obj(\MC)$ is arbitrary, $\al^{-1} \circ \al = \id_F$ and $\al \circ \al^{-1} = \id_G$.
	\end{proof}
	
	\begin{ex} \lex{15011.5}
		Let $\MC$ and $\MD$ be categories. Suppose that $\MC$ is small. Let $F,G \in \Obj(\MD^{\MC})$ and $\al \in \Hom_{\MD^{\MC}}(F, G)$. Then $\al$ is a natural isomorphism iff $\al \in \Iso_{\MD^{\MC}}(F, G)$. 
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item $(\implies)$: \\
			Suppose that $\al$ is a natural isomorphism. \rex{15011.4} implies that $\al \in \Iso_{\MD^{\MC}}(F, G)$. 
			\item $(\impliedby)$: \\
			Suppose that $\al \in \Iso_{\MD^{\MC}}(F, G)$. Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				\al_A \circ (\al^{-1})_A
				& = (\al \circ \al^{-1})_A \\
				& = (\id_{G})_A \\
				& = \id_{G(A)} \\
			\end{align*}
			and similarly, $\al_A^{-1} \circ \al_A = \id_{F(A)}$. Thus $\al_A \in \Iso_{\MD}(F(A), G(A))$. Since $A \in \Obj(\MC)$ is arbitrary, we have that for each $A \in \Obj(\MC)$, $\al_A \in \Iso_{\MD}(F(A), G(A))$. By definition, $\al$ is a natural isomorphism.
		\end{itemize}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\chapter{Fundamental Structures}
	
	
	\section{Initial and Terminal Objects}
	
	\begin{defn} \ld{15012}
		Let $\MC$ be a category and $0 \in \Obj(\MC)$ and $1 \in \Obj(\MC)$. Then 
		\begin{itemize}
			\item $0$ is said to be \textbf{$\MC$-initial} if for each $A \in \Obj(\MC)$, there exists $f \in \Hom_{\MC}(0, A)$ such that $\Hom_{\MC}(0, A) = \{f\}$. 
			\item $1$ is said to be \textbf{$\MC$-terminal} if for each $A \in \Obj(\MC)$, there exists $f \in \Hom_{\MC}(A, 1)$ such that $\Hom_{\MC}(A, 1) = \{f\}$. \tcr{redo, use duality}
		\end{itemize}
	\end{defn}
	
	\begin{note}
		When the context is clear, we say ``initial" and ``terminal" in place of ``$\MC$-initial" and ``$\MC$-terminal". 
	\end{note}
	
	\begin{ex} \lex{15012.1}
		Let $\MC$ be a category and $0 \in \Obj(\MC)$ and $1 \in \Obj(\MC)$. Then 
		\begin{enumerate}
			\item $0$ is $\MC$-initial iff $0$ is $\op{\MC}$-terminal
			\item $1$ is $\MC$-terminal iff $1$ is $\op{\MC}$-initial
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{itemize}
				\item $(\implies)$: \\
				Suppose that $0$ is $\MC$-initial. Let $A \in \Obj(\op{\MC})$. Since $\Obj(\op{\MC}) = \Obj(\MC)$, we have that $A \in \Obj(\MC)$. Since $0$ is $\MC$-initial, there exists $f \in \Hom_{\MC}(0,A)$ such that $\Hom_{\MC}(0,A) = \{f\}$. Then 
				\begin{align*}
					\Hom_{\op{\MC}}(A, 0) 
					& = \Hom_{\MC}(0, A) \\
					& = \{f\}.
				\end{align*}
				Since $A$ is arbitrary, we have that for each $A \in \Obj(\op{\MC})$, there exists $f \in \Hom_{\op{\MC}}(A, 0)$ such that $\Hom_{\op{\MC}}(A, 0) = \{f\}$. Thus $0$ is $\op{\MC}$-terminal.
				\item $(\impliedby)$: \\
				Suppose that $0$ is $\op{\MC}$-terminal. Let $A \in \Obj(\MC)$. Since $\Obj(\MC) = \Obj(\op{\MC})$, we have that $A \in \Obj(\op{\MC})$. Since $0$ is $\op{\MC}$-terminal, there exists $f \in \Hom_{\op{\MC}}(A,0)$ such that $\Hom_{\op{\MC}}(0,A) = \{f\}$. Then 
				\begin{align*}
					\Hom_{\MC}(0, A) 
					& = \Hom_{\op{\MC}}(A, 0) 
					& = \{f\}.
				\end{align*}
				Since $A$ is arbitrary, we have that for each $A \in \Obj(\MC)$, there exists $f \in \Hom_{\MC}(0, A) $ such that $\Hom_{\MC}(0, A)  = \{f\}$. Thus $0$ is $\MC$-initial.
			\end{itemize}
			\item Set $\MD \defeq \op{\MC}$. \rex{12005.1} implies that $\op{\MD} = \MC$. Then
			\begin{align*}
				\text{$1$ is $\MC$-terminal}
				& \iff \text{$1$ is $\MC$-terminal} \\
				& \iff \text{$1$ is $\op{\MD}$-terminal} \\
				& \iff \text{$1$ is $\MD$-initial}, \quad \text{(by \tcr{(reference) prev part})} \\
				& \iff \text{$1$ is $\op{\MC}$-initial}.
			\end{align*}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15013}
		Let $\MC$ be a category and $0 \in \Obj(\MC)$. 
		\begin{enumerate}
			\item If $0$ is initial, then $\Hom_{\MC}(0, 0) = \{\id_0\}$.
			\item If $1$ is terminal, then $\Hom_{\MC}(1, 1) = \{\id_1\}$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Suppose that $0$ is initial. Then there exists a $f \in \Hom_{\MC}(0,0)$ such that $\Hom_{\MC}(0, 0) = \{f\}$. Since $\id_1 \in \Hom_{\MC}(0,0)$, $f = \id_1$ and therefore $\Hom_{\MC}(0, 0) = \{\id_1\}$.
			\item \tcr{use duality}. 
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15014}
		Let $\MC$ be a category and $0, 0', 1, 1' \in \Obj(\MC)$. 
		\begin{enumerate}
			\item If $0$ and $0'$ are initial, then 
			\begin{enumerate}
				\item $0 \cong_{\MC} 0'$,
				\item $\Hom_{\MC}(0, 0') = \Iso_{\MC}(0,0')$.
			\end{enumerate}
			\item If $1$ and $1'$ are terminal, then 
			\begin{enumerate}
				\item $1 \cong_{\MC} 1'$,
				\item $\Hom_{\MC}(1, 1') = \Iso_{\MC}(1,1')$.
			\end{enumerate}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Suppose that $0$ and $0'$ are initial. 
			\begin{enumerate}
				\item By definition, there exist $f \in \Hom_{\MC}(0, 0')$ and $f' \in \Hom_{\MC}(0', 0)$ such that $\Hom_{\MC}(0, 0') = \{f\}$ and $\Hom_{\MC}(0', 0) = \{f'\}$, i.e. we have the following commutative diagram:
				\[ 
				\begin{tikzcd}[baseline= 7]
					\arrow[loop left, "f' \circ f"] 0 \arrow[r, bend right= 60, "f", swap] & 0' \arrow[l, bend left=-60, "f'", swap] \arrow[loop right, "f \circ f'"] \\
				\end{tikzcd}
				\]
				\rex{15013} implies that $f' \circ f = \id_{0}$ and $f \circ f' = \id_{0'}$. Hence $f \in \Iso_{\MC}(0,0')$. Since $\Iso_{\MC}(0,0') \neq \varnothing$, we have that $0 \cong_{\MC} 0'$.
				\item Since
				\begin{align*}
					\Iso_{\MC}(0,0')
					& \subset \Hom_{\MC}(0, 0') \\
					& = \{f\} \\
					& \subset \Iso_{\MC}(0,0'),
				\end{align*}
				we have that $\Hom_{\MC}(0, 0') = \Iso_{\MC}(0,0')$.
			\end{enumerate}
			\item \tcr{use duality}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15015}
		Let $X, Y \in \Obj(\bSet)$. Then
		\begin{enumerate}
			\item $X$ is initial iff $X = \varnothing$.
			\item $Y$ is terminal iff $Y \cong_{\bSet} \{\varnothing\}$. 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{itemize}
				\item $(\implies)$: \\
				Suppose that $X$ is initial. Since $\Hom_{\bSet}(X, \{0,1\}) \cong_{\bSet} \MP(X)$, we have that  
				\begin{align*}
					\# \Hom_{\bSet}(X, \{0,1\}) = 1
					& \iff \# \MP(X) = 1 \\
					& \iff \MP(X) = \{\varnothing\} \\
					& \iff X = \varnothing.
				\end{align*}
				Since $X$ is initial, there exists $f \in \Hom_{\bSet}(X, \{0,1\})$ such that $\Hom_{\bSet}(X, \{0,1\}) = \{f\}$. Thus $X = \varnothing$. 
				\item $(\impliedby)$: \\
				Suppose that $X = \varnothing$. Let $A \in \Obj(\bSet)$. 
				\begin{itemize}
					\item We note that for each $f \in \Hom_{\bSet}$,
					\begin{align*}
						f \in \Hom_{\bSet}(X, A) 
						& \iff f \in \Hom_{\bSet}(\varnothing, A) \\
						& \implies f \subset \varnothing \times A \\
						& = \iff f \subset \varnothing \\
						& \iff f = \varnothing.
					\end{align*}
					Thus for each $f \in \Hom_{\bSet}(X, A)$, $f \in \{\varnothing\}$. Hence $\Hom_{\bSet}(X, A) \subset \{\varnothing\}$. 
					\item Since  
					\begin{align*}
						\varnothing 
						& \in \Hom_{\bSet}(\varnothing, A) \\
						& = \Hom_{\bSet}(X, A),
					\end{align*}
					we have that $\{\varnothing\} \subset \Hom_{\bSet}(X, A)$.
				\end{itemize} 
				Thus $\Hom_{\bSet}(X, A) = \{\varnothing\}$. Therefore $X$ is initial.
			\end{itemize}
			\item 
			\begin{itemize}
				\item $(\implies)$: \\
				Suppose that $Y$ is terminal. Since $\# \Hom_{\bSet}(\{\varnothing\}, Y) = \# Y$, we have that 
				\begin{align*}
					\# \Hom_{\bSet}(\{\varnothing\}, Y) = 1
					& \iff \# Y = 1 \\
					& \iff Y \cong_{\bSet} \{\varnothing\}.
				\end{align*}
				Since $Y$ is terminal, there exists $f \in \Hom_{\bSet}(\{\varnothing\}, Y)$ such that $\Hom_{\bSet}(\{\varnothing\}, Y) = \{f\}$. Thus $Y \cong_{\bSet} \{\varnothing\}$.
				\item $(\impliedby)$: \\
				Suppose that $Y \cong_{\bSet} \{\varnothing\}$. Then there exists $y \in Y$ such that $Y = \{y\}$. Let $A \in \Obj(\bSet)$. Define $f_0 \in \Hom_{\bSet}(A, Y)$ by $f_0(a) \defeq y$. Let $f \in \Hom_{\bSet}(A, Y)$. Let $a \in A$. Since 
				\begin{align*}
					f(a) 
					& \in Y \\
					& = \{y\}, 
				\end{align*}
				we have that $f(a) = y$. Since $a \in A$ is arbitrary, we have that for each $a \in A$, 
				\begin{align*}
					f(a) 
					& = y \\
					& = f_0(a). 
				\end{align*}
				Thus $f = f_0$. Since $f \in \Hom_{\bSet}(A, Y)$ is arbitrary, we have that for each $f \in \Hom_{\bSet}(A, Y)$, $f = f_0$. Hence $\Hom_{\bSet}(A, Y) = \{f_0\}$. Since $A \in \Obj(\bSet)$ is arbitrary, we have that for each $A \in \Obj(\bSet)$, there exists $f_0 \in \Hom_{\bSet}(A, Y)$ such that $\Hom_{\bSet}(A, Y) = \{f_0\}$. Thus $Y$ is terminal. 
			\end{itemize}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15015.1}
		Let $\MC$ be a category. Suppose that $\MC$ is locally small. Let $X \in \Obj(\MC)$. Then 
		\begin{enumerate}
			\item $X$ is $\MC$-initial iff for each $A \in \Obj(\MC)$, $\Hom_{\MC}(X, A)$ is $\bSet$-terminal.
			\item $X$ is $\MC$-terminal iff for each $A \in \Obj(\MC)$, $\Hom_{\MC}(A, X)$ is $\bSet$-terminal.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item We have that
			\begin{align*}
				\text{$X$ is $\MC$-initial}
				& \iff \text{for each $A \in \Obj(\MC)$, $\# \Hom_{\MC}(X, A) = 1$} \\
				& \iff \text{for each $A \in \Obj(\MC)$, $\# \Hom_{\MC}(X, A) \cong_{\bSet} \{\varnothing\}$} \\
				& \iff \text{for each $A \in \Obj(\MC)$, $\# \Hom_{\MC}(X, A)$ is $\bSet$-terminal}, \quad \text{(by \rex{15015})}.
			\end{align*}
			\item We have that
			\begin{align*}
				\text{$X$ is $\MC$-terminal}
				& \iff \text{$X$ is $\op{\MC}$-initial}, \quad \text{(by \rex{15012.1})} \\
				& \iff \text{for each $A \in \Obj(\op{\MC})$, $\Hom_{\op{\MC}}(X, A)$ is $\bSet$-terminal}, \quad \text{(by \tcr{ref prev part})} \\
				& \iff  \text{for each $A \in \Obj(\MC)$, $\Hom_{\MC}(A, X)$ is $\bSet$-terminal}
			\end{align*}
		\end{enumerate}
	\end{proof}
	
	
	\begin{ex} \lex{15016}
		We have that 
		\begin{enumerate}
			\item $\0$ is $\Cat$-initial.
			\item $\1$ is $\Cat$-terminal. 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		\begin{enumerate}
			\item Let $\MC \in \Obj(\Cat)$. It is clear that $\Hom_{\Cat}(\0, \MC) = \{E_\MC\}$. Hence $\0$ is $\Cat$-initial. \tcr{Fill out like below ex}
			\item Let $\MC \in \Obj(\Cat)$. Let $F:\MC \rightarrow \1$. Since $\Obj(\1) = \{*\}$ and $\Hom_{\1}(*, *) = \{\id_*^{\1}\}$, we have for each $A,B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$, $F(A) = *$ and $F(f) = \id_*^{\1}$. Thus $F = \Del^{\MC}_*$. Since $F:\MC \rightarrow \1$ is arbitrary, we have that for each $F:\MC \rightarrow \1$, $F = \Del^{\MC}_*$. Thus $\Hom_{\Cat}(\MC, \1) = \{ \Del^{\MC}_* \}$. Since $\MC \in \Obj(\Cat)$ is arbitrary, we have that for each $\MC \in \Obj(\Cat)$, $\Hom_{\Cat}(\MC, \1) = \{ \Del^{\MC}_* \}$. Hence $\1$ is $\Cat$-terminal.
		\end{enumerate}
	\end{proof}
	
	\begin{defn} \ld{15017}
		Let $\MC$, $\MD$ be categories and $0,1 \in \Obj(\MD)$ and $F: \MC \rightarrow \MD$. Suppose that $0$ is $\MD$-initial and $1$ is $\MD$-terminal. Then for each $A \in \Obj(\MC)$, there exists $f_A \in \Hom_{\MD}(0, F(A))$ and $g_A \in \Hom_{\MD}(F(A), 1)$ such that $\Hom_{\MD}(0, F(A)) = \{f_A\}$ and $\Hom_{\MD}(F(A), 1) = \{g_A\}$. We define the 
		\begin{itemize}
			\item \textbf{initial natural transformation induced by $0$ from $\Del^{\MC}_0$ to $F$}, denoted $\eta^{(0,F)}: \Del^{\MC}_0 \Rightarrow F$, by 
			$\eta^{(0,F)}_A \defeq f_A$.
			\item \textbf{terminal natural transformation induced by $1$ from $F$ to $\Del^{\MC}_1$}, denoted $\phi^{(F,1)}: F \Rightarrow \Del^{\MC}_1$, by 
			$\phi^{(F,1)}_A \defeq g_A$.
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{15018}
		Let $\MC$, $\MD$ be categories and $0 \in \Obj(\MD)$ and $F: \MC \rightarrow \MD$. Suppose that $0$ is $\MD$-initial and $1$ is $\MD$-terminal. Then 
		\begin{enumerate}
			\item $\eta^{(0,F)}: \Del^{\MC}_0 \Rightarrow F$ is a natural transformation.
			\item $\phi^{(F,1)}: F \Rightarrow \Del^{\MC}_1$ is a natural transformation.
		\end{enumerate}
	\end{ex}
	
	\begin{proof} \
		\begin{enumerate}
			\item 
			\begin{enumerate}
				\item By definition, for each $A \in \Obj(\MC)$, $\eta^{(0,F)}_A \in \Hom_{\MD}(\Del^{\MC}_0(A), F(A))$
				\item Let $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A, B)$. Since 
				\begin{align*}
					F(f) \circ \eta^{(0,F)}_A 
					& \in \Hom_{\MD}(0, F(B)) \\
					& = \{\eta^{(0,F)}_B\}
				\end{align*}
				we have that 
				\begin{align*}
					F(f) \circ \eta^{(0,F)}_A 
					& = \eta^{(0,F)}_B \\
					& = \eta^{(0,F)}_B \circ \id_0^{\MC} 
				\end{align*}
				i.e. the following diagram commutes:
				\[ 
				\begin{tikzcd}[baseline= 7]
					\Del^{\MC}_0(A)  \arrow[r, "\eta^{(0,F)}_A"]  \arrow[d, "\Del^{\MC}_0(f)"']  & F(A)   \arrow[d, "F(f)"]\\
					\Del^{\MC}_0(B) \arrow[r, "\eta^{(0,F)}_B"'] &  F(B) \\
				\end{tikzcd}
				=
				\begin{tikzcd}[baseline= 7]
					0  \arrow[r, "\eta^{(0,F)}_A"]  \arrow[d, "\id_0^{\MC}"']  & F(A)   \arrow[d, "F(f)"]\\
					0 \arrow[r, "\eta^{(0,F)}_B"'] &  F(B) 
				\end{tikzcd}
				\]
			\end{enumerate}
			So $\eta^{(0,F)}: \Del^{\MC}_0 \Rightarrow F$ is a natural transformation.
			\item \tcr{FINISH!!!}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15020}
		Let $\MC$, $\MD$ be categories and $0,1 \in \Obj(\MD)$. Suppose that $\MC$ is small.
		\begin{enumerate}
			\item If $0$ is $\MD$-initial, then $\Del^{\MC}_0$ is $\MD^{\MC}$-initial. 
			\item If $1$ is $\MD$-terminal, then $\Del^{\MC}_1$ is $\MD^{\MC}$-terminal. 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Suppose that $0$ is $\MD$-initial. Let $F \in \Obj(\MD^{\MC})$, $\al \in \Hom_{\MD^{\MC}}(\Del^{\MC}_0, F)$ and $A \in \Obj(\MC)$. Then
			\begin{align*}
				\al_A 
				& \in \Hom_{\MD}(\Del^{\MC}_0(A), F(A)) \\
				& =  \Hom_{\MD}(0, F(A)) \\
				& = \{\eta^{(0,F)}_A\}
			\end{align*}
			Hence $\al_A = \eta^{(0,F)}_A$. Since $A \in \Obj(\MC)$ is arbitrary, we have that for each $A \in \Obj(\MC)$, $\al_A = \eta^{(0,F)}_A$. Thus $\al = \eta^{(0,F)}$. Since $\al \in  \Hom_{\MD^{\MC}}(\Del^{\MC}_0, F)$ is arbitrary, we have that for each $\al \in \Hom_{\MD^{\MC}}(\Del^{\MC}_0, F)$, $\al = \eta^{(0,F)}$. This $\Hom_{\MD^{\MC}}(\Del^{\MC}_0, F) = \{\eta^{(0,F)}\}$. Therefore $\Del^{\MC}_0$ is $\MD^{\MC}$-initial.
			\item \tcr{use duality}
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Products and Coproducts}
	
	\begin{defn}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)}, $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$ and $X \in \Obj(\MC)$. 
		\begin{itemize}
			\item 
			\begin{itemize}
				\item Let $(\pi_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X, X_{\al})$. Then $(X, (\pi_{\al})_{\al \in A})$ is said to be a \tbf{$\MC$-product of $(X_{\al})_{\al \in A}$} if for each $Y \in \Obj(\MC)$ and $(p_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(Y, X_{\al})$, there exists a unique $\phi \in \Hom_{\MC}(Y, X)$ such that for each $\al \in A$, from $\pi_{\al} \circ_{\MC} \phi = p_{\al}$, i.e. the following diagram commutes: 
				\[ 
				\begin{tikzcd}[baseline= 7]
					Y   \arrow[d, "\phi"', dashed]  \arrow[ddr, "p_{\al}"]    &  \\
					X \arrow[dr, "\pi_{\al}"']                        & \\
					& X_{\al}   
				\end{tikzcd}
				\] 
				\item We define 
				$$\Prod_{\MC}((X_{\al})_{\al \in A}) \defeq \bigg \{(X, (\pi_{\al})_{\al \in A}) \in \Obj(\MC) \times \prod\limits_{\al \in A} \Hom_{\MC}(X, X_{\al}): \text{$(X, (\pi_{\al})_{\al \in A})$ is a $\MC$-product of $(X_{\al})_{\al \in A}$} \bigg \}.$$
			\end{itemize}
			\item 
			\begin{itemize}
				\item Let $(\iota_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, X)$. Then $(X, (\iota_{\al})_{\al \in A})$ is said to be a \tbf{$\MC$-coproduct of $(X_{\al})_{\al \in A}$} if for each $Y \in \Obj(\MC)$ and $(i_{\al})_{\al \in A} \in \prod\limits_{\al \in A}\Hom_{\MC}(X_{\al}, Y)$, there exists a unique $\phi \in \Hom_{\MC}(X, Y)$ such that for each $\al \in A$, from $\phi \circ_{\MC} \iota_{\al} = i_{\al}$, i.e. the following diagram commutes: 
				\[ 
				\begin{tikzcd}[baseline= 7]
					& X_{\al} \arrow[dl, "\iota_{\al}"'] \arrow[ddl, "i_{\al}"] & \\
					X \arrow[d, "\phi"', dashed] & \\
					Y 
				\end{tikzcd}
				\] 
				\item We define 
				$$\Coprod_{\MC}((X_{\al})_{\al \in A}) \defeq \bigg \{(X, (\iota_{\al})_{\al \in A}) \in \Obj(\MC) \times \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, X): \text{$(X, (\iota_{\al})_{\al \in A})$ is a $\MC$-coproduct of $(X_{\al})_{\al \in A}$} \bigg \}.$$
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)} and $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$. Then 
		\begin{enumerate}
			\item $\Prod_{\op{\MC}}((X_{\al})_{\al \in A}) = \Coprod_{\MC}((X_{\al})_{\al \in A})$.
			\item $\Coprod_{\op{\MC}}((X_{\al})_{\al \in A}) = \Prod_{\MC}((X_{\al})_{\al \in A})$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{itemize}
				\item Let $(X, (\pi_{\al})_{\al \in A}) \in \Prod_{\op{\MC}}((X_{\al})_{\al \in A})$. We note that $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$, $X \in \Obj(\MC)$ and $(\pi_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, X)$. Let $Y \in \Obj(\MC)$ and $(i_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, Y)$. 
				\begin{itemize}
					\item \tbf{Existence:} \\
					Then $Y \in \Obj(\op{\MC})$ and $(i_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\op{\MC}}(Y, X_{\al})$. Since $(X, (\pi_{\al})_{\al \in A}) \in \Prod_{\op{\MC}}((X_{\al})_{\al \in A})$, there exists a unique $\phi \in \Hom_{\op{\MC}}(Y,X)$ such that for each $\al \in A$, $\pi_{\al} \circ_{\op{\MC}} \phi = i_{\al}$. Then $\phi \in \Hom_{\MC}(X, Y)$ and for each $\al \in A$, $\phi \circ_{\MC} \pi_{\al} = i_{\al}$. 
					\item \tbf{Uniqueness:} \\
					Let $\phi' \in \Hom_{\MC}(X, Y)$. Suppose that for each $\al \in A$,  $\phi' \circ_{\MC} \pi_{\al} = i_{\al}$. Then $\phi' \in \Hom_{\op{\MC}}(Y, X)$ and for each $\al \in A$, $\pi_{\al} \circ_{\op{\MC}} \phi' = i_{\al}$. Uniqueness of $\phi$ implies that $\phi' = \phi$.
				\end{itemize}
				Since $Y \in \Obj(\MC)$ and $(i_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, Y)$ are arbitrary, we have that for each $Y \in \Obj(\MC)$ and $(i_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, Y)$, there exists a unique $\phi \in \Hom_{\MC}(X, Y)$ such that for each $\al \in A$, $\phi \circ_{\MC} \pi_{\al} = i_{\al}$. Thus $(X, (\pi_{\al})_{\al \in A}) \in \Coprod_{\MC}((X_{\al})_{\al \in A})$. Since $(X, (\pi_{\al})_{\al \in A}) \in \Prod_{\op{\MC}}((X_{\al})_{\al \in A})$ is arbitrary, we have that for each $(X, (\pi_{\al})_{\al \in A}) \in \Prod_{\op{\MC}}((X_{\al})_{\al \in A})$, $(X, (\pi_{\al})_{\al \in A}) \in \Coprod_{\MC}((X_{\al})_{\al \in A})$. Hence $\Prod_{\op{\MC}}((X_{\al})_{\al \in A}) \subset \Coprod_{\MC}((X_{\al})_{\al \in A})$.
				\item \tcr{Similar, fill out!!!}
			\end{itemize}
			Since $\Prod_{\op{\MC}}((X_{\al})_{\al \in A}) \subset \Coprod_{\MC}((X_{\al})_{\al \in A})$ and $\Coprod_{\MC}((X_{\al})_{\al \in A}) \subset \Prod_{\op{\MC}}((X_{\al})_{\al \in A})$, we have that $\Prod_{\op{\MC}}((X_{\al})_{\al \in A}) = \Coprod_{\MC}((X_{\al})_{\al \in A})$. 
			\item \tcr{The prev part (ref)} implies that 
			\begin{align*}
				\Coprod_{\op{\MC}}((X_{\al})_{\al \in A})
				& = \Prod_{\op{(\op{\MC})}}((X_{\al})_{\al \in A}) \\
				& = \Prod_{\MC}((X_{\al})_{\al \in A}).
			\end{align*}
		\end{enumerate}
	\end{proof}
	
	\begin{ex}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)} and $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$. Then 
		\begin{enumerate}
			\item for each $(X, (\pi^X_{\al})_{\al \in A}), (Y, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$, $X \cong_{\MC} Y$. 
			\item for each $(X, (\iota^X_{\al})_{\al \in A}), (Y, (\iota^Y_{\al})_{\al \in A}) \in \Coprod_{\MC}((X_{\al})_{\al \in A})$, $X \cong_{\MC} Y$. 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $(X, (\pi^X_{\al})_{\al \in A}), (Y, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$. 
			\begin{itemize}
				\item 
				\begin{itemize}
					\item By definition, there exists a unique $\phi_{Y,X} \in \Hom_{\MC}(Y,X)$ such that for each $\al \in A$, $\pi^X_{\al} \circ_{\MC} \phi_{Y,X} = \pi^Y_{\al}$. Similarly, there exists a unique $\phi_{X,Y} \in \Hom_{\MC}(X,Y)$ such that for each $\al \in A$, $\pi^Y_{\al} \circ_{\MC} \phi_{X,Y} = \pi^X_{\al}$. 
					\begin{align*}
						\pi^Y_{\al} \circ_{C} (\phi_{X, Y} \circ_{\MC} \phi_{Y,X})
						& = (\pi^Y_{\al} \circ_{\MC} \phi_{X, Y}) \circ_{\MC} \phi_{Y,X} \\
						& = \pi^X_{\al} \circ_{\MC} \phi_{Y,X} \\
						& = \pi^Y_{\al}.
					\end{align*}
					\item By definition, there exists a unique $\phi \in \Hom_{\MC}(Y,Y)$ such that $\pi^Y_{\al} \circ \phi = \pi^Y_{\al}$.
					\item We note that $\pi^Y_{\al} \circ \id_Y^{\MC} = \pi^Y_{\al}$.
				\end{itemize}
				Thus the following diagrams commutes:				
				\[ 
				\begin{tikzcd}[baseline= 7]
					Y   \arrow[d, "\phi_{X, Y} \circ_{\MC} \phi_{Y,X}"', dashed]  \arrow[ddr, "\pi_{\al}"]    &  \\
					Y \arrow[dr, "\pi_{\al}"']                        & \\
					& X_{\al}   
				\end{tikzcd}
				\begin{tikzcd}[baseline= 7]
					Y   \arrow[d, "\phi"', dashed]  \arrow[ddr, "\pi_{\al}"]    &  \\
					Y \arrow[dr, "\pi_{\al}"']                        & \\
					& X_{\al}   
				\end{tikzcd}
				\begin{tikzcd}[baseline= 7]
					Y   \arrow[d, "\id_Y^{\MC}"', dashed]  \arrow[ddr, "\pi_{\al}"]    &  \\
					Y \arrow[dr, "\pi_{\al}"']                        & \\
					& X_{\al}   
				\end{tikzcd}
				\] 
				Uniqueness of $\phi$ then implies that
				\begin{align*}
					\phi_{X,Y} \circ_{\MC} \phi_{Y,X}
					& = \phi \\
					& = \id_Y^{\MC},
				\end{align*} 
				\item Similarly, $\phi_{Y,X} \circ_{\MC} \phi_{X,Y} = \id_X^{\MC}$. 
			\end{itemize}
			Hence $\phi_{Y,X} \in \Iso_{\MC}(Y,X)$ and $X \cong_{\MC} Y$. Since $(X, (\pi^X_{\al})_{\al \in A}), (Y, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$ are arbitrary, we have that for each $(X, (\pi^X_{\al})_{\al \in A}), (Y, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$, $X \cong_{\MC} Y$.
			\item Let $(X, (\iota^X_{\al})_{\al \in A}), (Y, (\iota^Y_{\al})_{\al \in A}) \in \Coprod_{\MC}((X_{\al})_{\al \in A})$. \tcr{The prev ex (ref)} implies that $(X, (\iota^X_{\al})_{\al \in A}), (Y, (\iota^Y_{\al})_{\al \in A}) \in \Prod_{\op{\MC}}((X_{\al})_{\al \in A})$. \tcr{The prev part (ref)} then implies that $X \cong_{\op{\MC}} Y$. \tcr{An exercise in isomorphism section (ref)} implies that $X \cong_{\MC} Y$.
		\end{enumerate}
	\end{proof}
	
	\begin{note}\
		\begin{itemize}
			\item 
			\begin{itemize}
				\item If $(X, (\pi_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$, we may write $\prod\limits_{\al \in A} X_{\al}$ in place of $X$.
				\item If $(X, (\iota_{\al})_{\al \in A}) \in \Coprod_{\MC}((X_{\al})_{\al \in A})$, we may write $\coprod\limits_{\al \in A} X_{\al}$ in place of $X$.
			\end{itemize}
			\item If $A = \{1,2\}$, we may write 
			\begin{itemize}
				\item $\Prod_{\MC}(X_1, X_2)$ and $\Coprod_{\MC}(X_1, X_2)$ in place of $\Prod_{\MC}((X_{\al})_{\al \in A})$ and $\Coprod_{\MC}((X_{\al})_{\al \in A})$ respectively. 
				\item $X_1 \times X_2$ in place of $\prod\limits_{\al \in A} X_{\al}$ and $X_1 \coprod X_2$ in place of $\coprod\limits_{\al \in A} X_{\al}$
			\end{itemize}
		\end{itemize}
	\end{note}
	
	\begin{ex}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)}, $X \in \Obj(\MC)$, $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$, $(\prod\limits_{\al \in A} X_{\al}, (\pi_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$ and $f,g \in \Hom_{\MC}(X, \prod\limits_{\al \in A} X_{\al})$. If for each $\al \in A$, $\pi_{\al} \circ_{\MC} f = \pi_{\al} \circ_{\MC} g$, then $f = g$. 
	\end{ex}
	
	\begin{proof}
		Suppose that for each $\al \in A$, $\pi_{\al} \circ_{\MC} f = \pi_{\al} \circ_{\MC} g$. Since $(\pi_{\al} \circ_{\MC} g)_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X, X_{\al})$ and $(\prod\limits_{\al \in A} X_{\al}, (\pi_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$, there exists a unique $\phi \in \Hom_{\MC}(X, \prod\limits_{\al \in A} X_{\al})$ such that for each $\al \in A$, $\pi_{\al} \circ_{\MC} \phi = \pi_{\al} \circ_{\MC} g$, i.e. the following diagram commutes: 
		\[
		\begin{tikzcd}[baseline= 7]
			X   \arrow[d, "\phi"', dashed]  \arrow[ddr, "\pi_{\al} \circ_{\MC} g"]    &  \\
			\prod\limits_{\al \in A} X_{\al} \arrow[dr, "\pi_{\al}"']                        & \\
			& X_{\al}   
		\end{tikzcd}
		\]
		Since for each $\al \in A$, $\pi_{\al} \circ_{\MC} f = \pi_{\al} \circ_{\MC} g$ and $\pi_{\al} \circ_{\MC} g = \pi_{\al} \circ_{\MC} g$, uniqueness of $\phi$ implies that 
		\begin{align*}
			f
			& = \phi \\
			& = g.
		\end{align*}
	\end{proof}
	
	\begin{defn}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)}, $(X_{\al})_{\al \in A}, (Y_{\al})_{\al \in A} \in \Obj(\MC)^A$, $(f_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, Y_{\al})$, $(\prod\limits_{\al \in A} X_{\al}, (\pi^X_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$ and $(\prod\limits_{\al \in A} Y_{\al}, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((Y_{\al})_{\al \in A})$. We define the \tbf{$\MC$-product of $(f_{\al})_{\al \in A}$}, denoted $\prod\limits_{\al \in A} f_{\al} \in \Hom_{\MC}(\prod\limits_{\al \in A} X_{\al}, \prod\limits_{\al \in A} Y_{\al})$, to be the unique $f \in \Hom_{\MC}(\prod\limits_{\al \in A} X_{\al}, \prod\limits_{\al \in A} Y_{\al})$ such that for each $\al \in A$, $\pi^Y_{\al} \circ_{\MC} f = f_{\al} \circ \pi^X_{\al}$, i.e the following diagram commutes:
		\[
		\begin{tikzcd}[baseline= 7]
			\prod\limits_{\al \in A} X_{\al}   \arrow[d, "f"', dashed]  \arrow[ddr, "f_{\al} \circ_{\MC} \pi^X_{\al}"]    &  \\
			\prod\limits_{\al \in A} Y_{\al} \arrow[dr, "\pi^Y_{\al}"']                        & \\
			& Y_{\al}   
		\end{tikzcd}
		\] 
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)}, $(X_{\al})_{\al \in A}, (Y_{\al})_{\al \in A} \in \Obj(\MC)^A$, $(f_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, Y_{\al})$, $(\prod\limits_{\al \in A} X_{\al}, (\pi^X_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$ and $(\prod\limits_{\al \in A} Y_{\al}, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((Y_{\al})_{\al \in A})$. Then $(\pi^X_{\al}, \pi^Y_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\Arr(\MC)}(\prod\limits_{\al \in A} f_{\al}, f_{\al})$.
	\end{ex}
	
	\begin{proof}
		By construction, for each $\al \in A$, 
		\begin{align*}
			f_{\al} \circ_{\MC} \pi^X_{\al}
			& = \pi^Y_{\al} \circ_{\MC} \prod\limits_{\al \in A} f_{\al},
		\end{align*}
		i.e. the following diagram commutes:
		\[ 
		\begin{tikzcd}[baseline= 7]
			\prod\limits_{\al \in A} X_{\al}  \arrow[r, "\pi^X_{\al}"]  \arrow[d, "\prod\limits_{\al \in A} f_{\al}"']  & X_{\al}   \arrow[d, "f_{\al}"]\\
			\prod\limits_{\al \in A} Y_{\al} \arrow[r, "\pi^Y_{\al}"'] &  Y_{\al}
		\end{tikzcd}
		\]
		Thus $(\pi^X_{\al}, \pi^Y_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\Arr(\MC)}(\prod\limits_{\al \in A} f_{\al}, f_{\al})$.
	\end{proof}
	
	\tcr{Next exercise shows that the product of morphisms is in fact a product object in the arrow category}
	
	\begin{ex}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)}, $(X_{\al})_{\al \in A}, (Y_{\al})_{\al \in A} \in \Obj(\MC)^A$, $(f_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\MC}(X_{\al}, Y_{\al})$, $(\prod\limits_{\al \in A} X_{\al}, (\pi^X_{\al})_{\al \in A}) \in \Prod_{\MC}((X_{\al})_{\al \in A})$ and $(\prod\limits_{\al \in A} Y_{\al}, (\pi^Y_{\al})_{\al \in A}) \in \Prod_{\MC}((Y_{\al})_{\al \in A})$. Define $(\pi_{\al})_{\al \in A} \in  \prod\limits_{\al \in A}\Hom_{\Arr(\MC)}(\prod\limits_{\al \in A} f_{\al}, f_{\al})$ by $\pi_{\al} \defeq (\pi^X_{\al}, \pi^Y_{\al})$. Then  $(\prod\limits_{\al \in A} f_{\al}, \pi_{\al}) \in \Prod_{\Arr(\MC)}((f_{\al})_{\al \in A})$.
	\end{ex}
	
	\begin{proof}
		Let $g \in \Obj(\Arr(\MC))$ and $(p_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\Arr(\MC)}(g, f_{\al})$. Define $A,B \in \Obj(\MC)$ by $A \defeq \dom_{\MC}(g)$ and $B \defeq \cod_{\MC}(g)$. Write $p_{\al} = (p^A_{\al}, p^A_{\al})$. We note that 
		\begin{itemize}
			\item By definition, for each $\al \in A$, $f_{\al} \circ_{\MC} p^A_{\al} = p^B_{\al} \circ_{\MC} g$, i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}[baseline= 7]
				A  \arrow[r, "p^A_{\al}"]  \arrow[d, "g"']  & X_{\al}   \arrow[d, "f_{\al}"]\\
				B \arrow[r, "p^B_{\al}"'] &  Y_{\al}
			\end{tikzcd}
			\]
			\item By construction, for each $\al \in A$, $f_{\al} \circ_{\MC} \pi^X_{\al} = \pi^Y_{\al} \circ_{\MC} \prod\limits_{\al \in A} f_{\al}$, i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}[baseline= 7]
				\prod\limits_{\al \in A} X_{\al}  \arrow[r, "\pi^X_{\al}"]  \arrow[d, "\prod\limits_{\al \in A} f_{\al}"']  & X_{\al}   \arrow[d, "f_{\al}"]\\
				\prod\limits_{\al \in A} Y_{\al} \arrow[r, "\pi^Y_{\al}"'] &  Y_{\al}
			\end{tikzcd}
			\]
		\end{itemize}
		\begin{itemize}
			\item \tbf{Existence:} \\
			By definition, there exists a unique $\phi_X \in \Hom_{\MC}(A, \prod\limits_{\al \in A} X_{\al})$ such that for each $\al \in A$, $\pi^X_{\al} \circ_{\MC} \phi_X = p^A_{\al}$, i.e. the following diagram commutes: 
			\begin{tikzcd}[baseline= 7]
				A   \arrow[d, "\phi_X"', dashed]  \arrow[ddr, "p^A_{\al} "]    &  \\
				\prod\limits_{\al \in A} X_{\al} \arrow[dr, "\pi^X_{\al}"']                        & \\
				& X_{\al}   
			\end{tikzcd}
			Similiarly, there exists a unique $\phi_Y \in \Hom_{\MC}(B, \prod\limits_{\al \in A} Y_{\al})$ such that for each $\al \in A$, $\pi^Y_{\al} \circ_{\MC} \phi_Y = p^B_{\al}$, i.e. the following diagram commutes:
			\[
			\begin{tikzcd}[baseline= 7]
				B   \arrow[d, "\phi_Y"', dashed]  \arrow[ddr, "p^B_{\al} "]    &  \\
				\prod\limits_{\al \in A} Y_{\al} \arrow[dr, "\pi^Y_{\al}"']                        & \\
				& Y_{\al}   
			\end{tikzcd}
			\]
			Then for each $\al \in A$,
			\begin{align*}
				\pi^Y_{\al} \circ_{\MC} (\prod\limits_{\al \in A} f_{\al} \circ_{\MC} \phi_X)
				& = (\pi^Y_{\al} \circ_{\MC} \prod\limits_{\al \in A} f_{\al}) \circ_{\MC} \phi_X \\
				& = (f_{\al} \circ_{\MC} \pi^X_{\al}) \circ_{\MC} \phi_X \\
				& = f_{\al} \circ_{\MC} (\pi^X_{\al} \circ_{\MC} \phi_X) \\
				& = f_{\al} \circ_{\MC} p^A_{\al} \\
				& = p^B_{\al} \circ_{\MC} g \\
				& = (\pi^Y_{\al} \circ_{\MC} \phi_Y) \circ_{\MC} g \\
				& = \pi^Y_{\al} \circ_{\MC} (\phi_Y \circ_{\MC} g).
			\end{align*}
			\tcr{the prev ex (ref)} then implies that $\prod\limits_{\al \in A} f_{\al} \circ_{\MC} \phi_X = \phi_Y \circ_{\MC} g$, i.e. the following diagram commutes: 
			\[
			\begin{tikzcd}[baseline= 7]
				A  \arrow[r, "\phi_X"]  \arrow[d, "g"']  & \prod\limits_{\al \in A} X_{\al}   \arrow[d, "\prod\limits_{\al \in A} f_{\al}"]\\
				B \arrow[r, "\phi_Y"'] &  \prod\limits_{\al \in A} Y_{\al}
			\end{tikzcd}
			\]
			Thus $(\phi_X, \phi_Y) \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$. Define $\phi \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$ by $\phi \defeq (\phi_X, \phi_Y)$. Let $\al \in A$. Since 
			$\pi^X_{\al} \circ_{\MC} \phi_X = p^A_{\al}$ and $\pi^Y_{\al} \circ_{\MC} \phi_Y = p^B_{\al}$, we have that 
			\begin{align*}
				\pi_{\al} \circ_{\Arr(\MC)} \phi
				& = (\pi^X_{\al}, \pi^Y_{\al}) \circ_{\Arr(\MC)}  (\phi_X, \phi_Y) \\
				& = (\pi^X_{\al} \circ_{\MC} \phi_X, \pi^Y_{\al} \circ_{\MC} \phi_Y) \\
				& = (p^A_{\al}, p^B_{\al}) \\
				& = p_{\al}.
			\end{align*}
			Since $\al \in A$ is arbitrary, we have that for each $\al \in A$, $\pi_{\al} \circ_{\Arr(\MC)} \phi = p_{\al}$,
			i.e. the following diagram commutes:
			\[
			\begin{tikzcd}[baseline= 7]
				g   \arrow[d, "\phi"', dashed]  \arrow[ddr, "p_{\al} "]    &  \\
				\prod\limits_{\al \in A} f_{\al} \arrow[dr, "\pi_{\al}"']                        & \\
				& f_{\al}
			\end{tikzcd}
			\]
			\item \tbf{Uniqueness:} \\
			Let $\phi' \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$. Write $\phi' = (\phi'_X, \phi'_Y)$. Suppose that for each $\al \in A$, $\pi_{\al} \circ_{\Arr(\MC)} \phi' = p_{\al}$, i.e. the following diagram commutes: 
			\[
			\begin{tikzcd}[baseline= 7]
				g   \arrow[d, "\phi'"', dashed]  \arrow[ddr, "p_{\al} "]    &  \\
				\prod\limits_{\al \in A} f_{\al} \arrow[dr, "\pi_{\al}"']                        & \\
				& f_{\al}
			\end{tikzcd}
			\]
			Let $\al \in A$. Then 
			\begin{align*}
				(\pi^X_{\al} \circ_{\MC} \phi'_X,  \pi^Y_{\al} \circ_{\MC} \phi'_Y) 
				& = (\pi^X_{\al}, \pi^Y_{\al}) \circ_{\Arr(\MC)} (\phi'_X, \phi'_Y) \\
				& = \pi_{\al} \circ_{\Arr(\MC)} \phi' \\
				& = p_{\al} \\
				& = (p^A_{\al}, p^B_{\al}). 
			\end{align*}
			Therefore $\pi^X_{\al} \circ_{\MC} \phi'_X = p^A_{\al}$ and $\pi^Y_{\al} \circ_{\MC} \phi'_Y = p^B_{\al}$. Since $\al \in A$ is arbitrary, we have that for each $\al \in A$, $\pi^X_{\al} \circ_{\MC} \phi'_X = p^A_{\al}$ and $\pi^Y_{\al} \circ_{\MC} \phi'_Y = p^B_{\al}$, i.e. the following diagrams commute:
			\[
			\begin{tikzcd}[baseline= 7]
				A   \arrow[d, "\phi'_X"', dashed]  \arrow[ddr, "p^A_{\al} "]    &  \\
				\prod\limits_{\al \in A} X_{\al} \arrow[dr, "\pi^X_{\al}"']                        & \\
				& X_{\al}   
			\end{tikzcd}
			\begin{tikzcd}[baseline= 7]
				B   \arrow[d, "\phi'_Y"', dashed]  \arrow[ddr, "p^B_{\al} "]    &  \\
				\prod\limits_{\al \in A} Y_{\al} \arrow[dr, "\pi^Y_{\al}"']                        & \\
				& Y_{\al}   
			\end{tikzcd}
			\]
			Uniqueness of $\phi_X$ and $\phi_Y$ imply that $\phi'_X = \phi_X$ and $\phi'_Y = \phi_Y$. Thus 
			\begin{align*}
				\phi'
				& = (\phi'_X, \phi'_Y) \\
				& = (\phi_X, \phi_Y) \\
				& = \phi.
			\end{align*}
			Since $\phi' \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$ is arbitrary, we have that for each $\phi' \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$, $\phi' = \phi$. 
		\end{itemize}
		Thus there exists a unique $\phi \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$ such that for each $\al \in A$, $\pi_{\al} \circ_{\Arr(\MC)} \phi = p_{\al}$. Since $g \in \Obj(\Arr(\MC))$ and $(p_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\Arr(\MC)}(g, f_{\al})$ are arbitrary, we have that for each $g \in \Obj(\Arr(\MC))$ and $(p_{\al})_{\al \in A} \in \prod\limits_{\al \in A} \Hom_{\Arr(\MC)}(g, f_{\al})$, there exists a unique $\phi \in \Hom_{\Arr(\MC)}(g, \prod\limits_{\al \in A} f_{\al})$ such that for each $\al \in A$, $\pi_{\al} \circ_{\Arr(\MC)} \phi = p_{\al}$,
		i.e. the following diagram commutes:
		\[
		\begin{tikzcd}[baseline= 7]
			g   \arrow[d, "\phi"', dashed]  \arrow[ddr, "p_{\al} "]    &  \\
			\prod\limits_{\al \in A} f_{\al} \arrow[dr, "\pi_{\al}"']                        & \\
			& f_{\al}
		\end{tikzcd}
		\]
		Hence $(\prod\limits_{\al \in A} f_{\al}, (\pi_{\al})_{\al \in A}) \in \Prod_{\Arr(\MC)}((f_{\al})_{\al \in A})$.
	\end{proof}
	
	\begin{defn}
		Let $\MC$ be a category. Then $\MC$ is said to have all
		\begin{itemize}
			\item \tbf{products} if for each $A \in \Obj(\bSet)$ and $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$, $\Prod_{\MC}((A_{\al})_{\al \in A}) \neq \varnothing$,
			\item \tbf{coproducts} if for each $A \in \Obj(\bSet)$ and $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$, $\Prod_{\MC}((A_{\al})_{\al \in A}) \neq \varnothing$,
			\item \tbf{finite products} if for each $A, B \in \Obj(\MC)$, $\Prod_{\MC}(A,B) \neq \varnothing$,
			\item \tbf{finite coproducts} if for each $A, B \in \Obj(\MC)$, $\Coprod_{\MC}(A,B) \neq \varnothing$,
		\end{itemize}
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Equalizers and Coequalizers}
	
	\begin{defn}
		Let $\MC$ be a category. Let $A,B \in \Obj(\MC)$ and $g,h \in \Hom_{\MC}(A,B)$. 
		\begin{itemize}
			\item Let $C \in \Obj(\MC)$.
			\begin{itemize}
				\item Let $f \in \Hom_{\MC}(C, A)$. Then $(C, f)$ is said to be a \tbf{$\MC$-equalizer of $g$ and $h$} if 
				\begin{enumerate}
					\item $g \circ_{\MC} f = h \circ_{\MC} f$, i.e. the following diagram commutes:
					\[ 
					\begin{tikzcd}[baseline= 7]
						&                                   & B \\
						C \arrow[r, "f"]  & A \arrow[ur, "g"] \arrow[dr, "h"'] &   \\
						&                                   & B \\
					\end{tikzcd}
					\]
					\item for each $C' \in \Obj(\MC)$ and $f' \in \Hom_{\MC}(C', A)$, if $g \circ_{\MC} f' = h \circ_{\MC} f'$, then there exists a unique $\phi \in \Hom_{\MC}(C', C)$ such that $f \circ_{\MC} \phi = f'$, i.e. the following diagram commutes:
					\[ 
					\begin{tikzcd}[baseline= 7]
						C' \arrow[dr, "f'"] \arrow[dd, "\phi"', dashed]&     & B \\
						& A \arrow[ur, "g"] \arrow[dr, "h"'] &   \\
						C \arrow[ur, "f"'] &                                  & B \\
					\end{tikzcd}
					\]
				\end{enumerate} 
				\item Let $f \in \Hom_{\MC}(B, C)$. Then $(C, f)$ is said to be a \tbf{$\MC$-coequalizer} of $g$ and $h$ if 
				\begin{enumerate}
					\item $f \circ_{\MC} g = f \circ_{\MC} h$, i.e. the following diagram commutes:
					\[ 
					\begin{tikzcd}[baseline= 7]
						A \arrow[dr, "g"]  &                   &  \\
						& B \arrow[r, "f"]  & C  \\
						A \arrow[ur, "h"']  &                   & \\
					\end{tikzcd}
					\]
					\item for each $C' \in \Obj(\MC)$ and $f' \in \Hom_{\MC}(B, C')$, if $ f' \circ_{\MC} g = f' \circ_{\MC} h$, then there exists a unique $\phi \in \Hom_{\MC}(C, C')$ such that $\phi \circ_{\MC} f = f'$, i.e. the following diagram commutes:
					\[ 
					\begin{tikzcd}[baseline= 7]
						A \arrow[dr, "g"]  &                   & C \arrow[dd, "\phi", dashed]\\
						& B \arrow[ur, "f"]  \arrow[dr, "f'"'] &   \\
						A \arrow[ur, "h"']  &                  & C' \\
					\end{tikzcd}
					\]
				\end{enumerate} 
			\end{itemize}
			\item We define 
			\begin{itemize}
				\item $\Eqzr_{\MC}(g,h) \defeq \{(C, f) \in \Obj(\MC) \times \Hom_{\MC}: \text{$\cod_{\MC}(f) = A$ and $f$ is a $\MC$-equalizer of $g$ and $h$}\}$
				\item $\Coeqzr_{\MC}(g,h) \defeq \{(C, f) \in \Obj(\MC) \times \Hom_{\MC}: \text{$\dom_{\MC}(f) = B$ and $f$ is a $\MC$-coequalizer of $g$ and $h$}\}$
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category. 
		\begin{itemize}
			\item Let $C \in \Obj(\MC)$ and $f \in \Hom_{\MC}$. Then $(C, f)$ is said to be a
			\begin{enumerate}
				\item $\MC$-equalizer if there exist $A,B \in \Obj(\MC)$ and $g,h \in \Hom_{\MC}(A,B)$ such that $f \in \Hom_{\MC}(C, A)$ and $f$ is a $\MC$-equalizer of $g$ and $h$. 
				\item $\MC$-coequalizer if there exist $A,B \in \Obj(\MC)$ and $g,h \in \Hom_{\MC}(A,B)$ such that $f \in \Hom_{\MC}(B, C)$ and $f$ is a $\MC$-coequalizer of $g$ and $h$. 
			\end{enumerate}
			\item We define 
			\begin{itemize}
				\item $\Eqzr_{\MC} \defeq \{(C,f) \in \Obj(\MC) \times \Hom_{\MC}: \text{$(C,f)$ is a $\MC$-equalizer}\}$
				\item $\Coeqzr_{\MC} \defeq \{(C,f) \in \Obj(\MC) \times \Hom_{\MC}: \text{$(C,f)$ is a $\MC$-coequalizer}\}$
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category. Then
		\begin{enumerate}
			\item for each $A,B \in \Obj(\MC)$ and $g,h \in \Hom_{\op{\MC}}(A,B)$, 
			\begin{enumerate}
				\item $\Eqzr_{\op{\MC}}(g, h) = \Coeqzr_{\MC}(g,h)$
				\item $\Coeqzr_{\op{\MC}}(g,h) = \Eqzr_{\MC}(g,h)$
			\end{enumerate}
			\item 
			\begin{enumerate}
				\item $\Eqzr_{\op{\MC}} = \Coeqzr_{\MC}$
				\item $\Coeqzr_{\op{\MC}} = \Eqzr_{\MC}$
			\end{enumerate}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{enumerate}
				\item 
				\begin{itemize}
					\item Let $(C,f) \in \Eqzr_{\op{\MC}}(f,g)$. By definition \tcr{(ref def)}, $C \in \Obj(\op{\MC})$, $f \in \Hom_{\op{\MC}}(C, A)$ and
					\begin{itemize}
						\item $g \circ_{\op{\MC}} f = h \circ_{\op{\MC}} f$,
						\item for each $C' \in \Obj(\op{\MC})$ and $f' \in \Hom_{\op{\MC}}(C', A)$, if $g \circ_{\op{\MC}} f' = h \circ_{\op{\MC}} f'$, then there exists a unique $\phi \in \Hom_{\op{\MC}}(C', C)$ such that $f \circ_{\op{\MC}} \phi = f'$. 
					\end{itemize}
					We note that $g,h \in \Hom_{\MC}(B, A)$ and $f \in \Hom_{\MC}(B, C)$.  
					\begin{enumerate}
						\item Thus
						\begin{align*}
							f \circ_{\MC} g 
							& = g \circ_{\op{\MC}} f \\
							& = h \circ_{\op{\MC}} f \\
							& = f \circ_{\MC} h.
						\end{align*}
						\item Let $C' \in \Obj(\MC)$ and $f' \in \Hom_{\MC}(B, C')$. Suppose that $f' \circ_{\MC} g = f' \circ_{\MC} h$. Then $f' \in \Hom_{\op{\MC}}(C', B)$ and  
						\begin{align*}
							g \circ_{\op{\MC}} f' 
							& = f' \circ_{\MC} g \\
							& = f' \circ_{\MC} h \\
							& = h \circ_{\op{\MC}} f'.
						\end{align*}
						Thus there exists a unique $\phi \in \Hom_{\op{\MC}}(C', C)$ such that $f \circ_{\op{\MC}} \phi = f'$. Therefore there exists a unique $\phi \in \Hom_{\MC}(C, C')$ such that 
						\begin{align*}
							\phi \circ_{\MC} f 
							& = f \circ_{\op{\MC}} \phi \\
							& = f'.
						\end{align*}
						Since $C' \in \Obj(\MC)$ and $f' \in \Hom_{\MC}(B, C')$ are arbitrary, we have that for each $C' \in \Obj(\MC)$ and $f' \in \Hom_{\MC}(B, C')$, there exists a unique $\phi \in \Hom_{\MC}(C, C')$ such that $\phi \circ_{\MC} f = f'$.
					\end{enumerate}
					Thus $(C,f) \in \Coeqzr_{\MC}(f,g)$. Since $(C,f) \in \Eqzr_{\op{\MC}}(f,g)$ is arbitrary, we have that for each $(C,f) \in \Eqzr_{\op{\MC}}(f,g)$, $(C,f) \in \Coeqzr_{\MC}(f,g)$. Thus $\Eqzr_{\op{\MC}}(f,g) \subset \Coeqzr_{\MC}(f,g)$.
					\item Similarly, $\Coeqzr_{\MC}(f,g) \subset \Eqzr_{\op{\MC}}(f,g)$. \tcr{show details}
				\end{itemize}
				Since $\Eqzr_{\op{\MC}}(f,g) \subset \Coeqzr_{\MC}(f,g)$ and $\Coeqzr_{\MC}(f,g) \subset \Eqzr_{\op{\MC}}(f,g)$, we have that $\Eqzr_{\op{\MC}}(f,g) = \Coeqzr_{\MC}(f,g)$
				\item \tcr{Similar}
			\end{enumerate}
			\item \tcr{FINISH!!!}
		\end{enumerate}
		\tcr{FINISH!!!}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Pullbacks and Pushouts}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Exponentials}
	
	\begin{defn}
		Let $\MC$ be a category. Suppose that $\MC$ has finite products. Let $B,C \in \Obj(\MC)$. 
		\begin{itemize}
			\item 
			\begin{itemize}
				\item Let $D \in \Obj(\MC)$ and $\eval: D \times B \rightarrow C$. Then $(D, \eval)$ is said to be a \tbf{$\MC$-exponential object of $B$ and $C$} if for each $A \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A \times B, C)$, there exists a unique $\phi \in \Hom_{\MC}(A, D)$ such that $\eval \circ_{\MC} (\phi \times \id_B^{\MC}) = f$, i.e. the following diagram commutes: 
				\[ 
				\begin{tikzcd}[baseline= 7]
					A \arrow[d, "\phi"', dashed] & A \times B  \arrow[d, "\phi \times \id_B^{\MC}"', dashed]  \arrow[dr, "f", dashed] &  \\
					D                           & D \times B  \arrow[r, "\eval"'] & C 
				\end{tikzcd}
				\]
				\item We define 
				$$\Exp_{\MC}(B, C) \defeq \bigg \{(D, \eval) \in \coprod\limits_{D \in \Obj(\MC)}\Hom_{\MC}(D \times B, C): \text{$(D, \eval)$ is a $\MC$-exponential of $B$ and $C$} \bigg \}.$$
			\end{itemize}
			\item We define \tcr{define coexponential objects} \tbf{}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category, $A$ a set \tcr{(class?)} and $(X_{\al})_{\al \in A} \in \Obj(\MC)^A$. Then 
		\begin{enumerate}
			\item $\Exp_{\op{\MC}}(B, C) = \Coexp_{\MC}(B, C)$.
			\item $\Coexp_{\op{\MC}}(B, C) = \Exp_{\MC}(B, C)$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		
	\end{proof}
	
	\begin{ex}
		
	\end{ex}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Monomorphisms and Epimorphisms}
	
	\subsection{Introduction}
	
	\begin{defn} \ld{15009}
		Let $\MC$ be a category and $A,B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Then $f$ is said to be 
		\begin{itemize}
			\item 
			a \textbf{monomorphism} if for each $C \in \Obj(C)$ and $g,h \in \Hom_{\MC}(C, A)$, $f \circ g = f \circ h$ implies that $g = h$, i.e. we have the following implication of commutative diagrams: 
			\[ 
			\begin{tikzcd}[baseline= 7]
				C \arrow[dr, "g"]&                                   & \\
				& A \arrow[r, "f"] & B  \\
				C \arrow[ur, "h"']&                                   & \\
			\end{tikzcd}
			\implies
			\begin{tikzcd}[baseline= 7]
				C \arrow[bend right=60, swap]{r}{h} \arrow[bend right=-60]{r}{g} & A  \\
			\end{tikzcd}
			\]
			\item 
			an \textbf{epimorphism} if for each $C \in \Obj(C)$ and $g,h \in \Hom_{\MC}(B, C)$, $g \circ f = h \circ f$ implies that $g = h$, i.e. we have the following implication of commutative diagrams: \\
			\[ 
			\begin{tikzcd}[baseline= 7]
				&                                   & C \\
				A \arrow[r, "f"]  & B \arrow[ur, "g"] \arrow[dr, "h"'] &   \\
				&                                   & C \\
			\end{tikzcd}
			\implies
			\begin{tikzcd}[baseline= 7]
				B \arrow[bend right=60, swap]{r}{h} \arrow[bend right=-60]{r}{g} & C  \\
			\end{tikzcd}
			\]
		\end{itemize}
		\tcr{make note about common short-hand using parallel arrows}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category.
		\begin{itemize}
			\item We define 
			\begin{itemize}
				\item $\Mono_{\MC} \defeq \{f \in \Hom_{\MC}:\text{$f$ is a monomorphism}\}$
				\item $\Epi_{\MC} \defeq \{f \in \Hom_{\MC}:\text{$f$ is a epimorphism}\}$
			\end{itemize}
			\item Let $A, B \in \Obj(\MC)$. We define 
			\begin{itemize}
				\item $\Mono_{\MC}(A,B) \defeq \Mono_{\MC} \cap \Hom_{\MC}(A,B)$.
				\item $\Epi_{\MC}(A,B) \defeq \Epi_{\MC} \cap \Hom_{\MC}(A,B)$.
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category. Then
		\begin{enumerate}
			\item for each $A,B \in \Obj(\MC)$,
			\begin{enumerate}
				\item $\Mono_{\op{\MC}}(A,B) = \Epi_{\MC}(B,A)$
				\item $\Epi_{\op{\MC}}(A,B) = \Mono_{\MC}(B,A)$
			\end{enumerate}
			\item 
			\begin{enumerate}
				\item $\Mono_{\op{\MC}} = \Epi_{\MC}$
				\item $\Epi_{\op{\MC}} = \Mono_{\MC}$
			\end{enumerate}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\tcr{FIX!!!}
		\begin{enumerate}
			\item 
			\begin{enumerate}
				\item Let $A,B \in \Obj(\MC)$.
				\begin{itemize}
					\item Let $m \in \Mono_{\op{\MC}}(A,B)$. Then $m \in \Hom_{\MC}(B,A)$. Let $C \in \Obj(\MC)$ and $f,g \in \Hom_{\MC}(A, C)$. Suppose that $f \circ_{\MC} m = g \circ_{\MC} m$. Then $m \circ_{\op{\MC}} f = m \circ_{\op{\MC}} g$. Since $m \in \Mono_{\op{\MC}}$, we have that $f = g$. Since $C \in \Obj(\MC)$ and $f,g \in \Hom_{\MC}(A, C)$ are arbitrary, we have that for each $C \in \Obj(\MC)$ and $f,g \in \Hom_{\MC}(A, C)$, $f \circ_{\MC} m = g \circ_{\MC} m$ implies that $f = g$. Thus $m \in \Epi_{\MC}(B,A)$. Since $m \in \Mono_{\op{\MC}}(A,B)$ is arbitrary, we have that for each $m \in \Mono_{\op{\MC}}(A,B)$, $m \in \Epi_{\MC}(B,A)$. Hence $\Mono_{\op{\MC}}(A,B) \subset \Epi_{\MC}(B,A)$. 
					\item Let $e \in \Epi_{\MC}(B,A)$. Then $e \in \Hom_{\op{\MC}}(A,B)$. Let $C \in \Obj(\op{\MC})$ and $f,g \in \Hom_{\op{\MC}}(C, A)$. Suppose that $e \circ_{\op{\MC}} f = e \circ_{\op{\MC}} g$. Then $f \circ_{\MC} e = g \circ_{\MC} e$. Since $e \in \Epi_{\MC}$, we have that $f = g$. Since $C \in \Obj(\op{\MC})$ and $f,g \in \Hom_{\op{\MC}}(C, A)$ are arbitrary, we have that for each $C \in \Obj(\op{\MC})$ and $f,g \in \Hom_{\op{\MC}}(C, A)$, $e \circ_{\op{\MC}} f = e \circ_{\op{\MC}} g$ implies that $f = g$. Thus $e \in \Mono_{\op{\MC}}(A, B)$. Since $e \in \Epi_{\MC}(B,A)$ is arbitrary, we have that for each $e \in \Epi_{\MC}(B,A)$, $e \in \Mono_{\op{\MC}}(A, B)$. Hence $\Epi_{\MC}(B,A) \subset \Mono_{\op{\MC}}(A,B)$. 
				\end{itemize}
				Since $\Mono_{\op{\MC}}(A,B) \subset \Epi_{\MC}(B,A)$ and $\Epi_{\MC}(B,A) \subset \Mono_{\op{\MC}}(A,B)$, we have that $\Mono_{\op{\MC}}(A,B) = \Epi_{\MC}(B,A)$. 
				\item 
			\end{enumerate}
			\item 
			\begin{enumerate}
				\item 
				Since $A,B \in \Obj(\MC)$ are arbitrary, we have that for each $A,B \in \Obj(\MC)$, $\Mono_{\op{\MC}}(A,B) = \Epi_{\MC}(B,A)$. Hence 
				\begin{align*}
					\Mono_{\op{\MC}}
					& = \bigcup\limits_{(A,B) \in \Obj(\op{\MC})^2} \Mono_{\op{\MC}}(A,B) \\
					& = \bigcup\limits_{(A,B) \in \Obj(\MC)^2} \Mono_{\op{\MC}}(A,B) \\
					& = \bigcup\limits_{(B,A) \in \Obj(\MC)^2} \Epi_{\MC}(B,A) \\
					& = \Epi_{\MC}.
				\end{align*}
				\item \tcr{The previous part (ref needed)} implies that 
				\begin{align*}
					\Mono_{\MC}
					& = \Mono_{\op{(\op{\MC})}} \\
					& = \Epi_{\op{\MC}}.
				\end{align*}
			\end{enumerate}
		\end{enumerate}
	\end{proof}
	
	\begin{ex}
		Let $\MC$ be a category and $A,B,C \in \Obj(\MC)$. Then 
		\begin{enumerate}
			\item for each $f \in \Mono_{\MC}(A,B)$ and $g \in \Mono_{\MC}(B,C)$, $g \circ_{\MC} f \in \Mono_{\MC}(A,C)$,
			\item for each $f \in \Epi_{\MC}(A,B)$ and $g \in \Epi_{\MC}(B,C)$, $g \circ_{\MC} f \in \Epi_{\MC}(A,C)$. 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $f \in \Mono_{\MC}(A,B)$, $g \in \Mono_{\MC}(B,C)$, $X \in \Obj(\MC)$ and $\al,\be \in \Hom_{\MC}(X, A)$. We note that since 
			\begin{align*}
				(g \circ_{\MC} f) \circ_{\MC} \al = (g \circ_{\MC} f) \circ_{\MC} \be
				& \iff g \circ_{\MC} (f \circ_{\MC} \al) = g \circ_{\MC} (f \circ_{\MC} \be) \\
				& \implies f \circ_{\MC} \al = f \circ_{\MC} \be \quad \text{($g \in \Mono_{\MC}$)} \\
				& \implies \al = \be \quad \text{($f \in \Mono_{\MC}$)}.
			\end{align*} 
			Since $X \in \Obj(\MC)$ and $\al,\be \in \Hom_{\MC}(X, A)$ with $(g \circ_{\MC} f) \circ_{\MC} \al = (g \circ_{\MC} f) \circ_{\MC} \be$ are arbitrary, we have that for each $X \in \Obj(\MC)$ and $\al,\be \in \Hom_{\MC}(X, A)$, $(g \circ_{\MC} f) \circ_{\MC} \al = (g \circ_{\MC} f) \circ_{\MC} \be$ implies that $\al = \be$. Hence $g \circ_{\MC} f \in \Mono_{\MC}(A, C)$. Since $f \in \Mono_{\MC}(A,B)$ and $g \in \Mono_{\MC}(B,C)$ are arbitrary, we have that for each $f \in \Mono_{\MC}(A,B)$, $g \in \Mono_{\MC}(B,C)$, $g \circ_{\MC} f \in \Mono_{\MC}(A,C)$.
			\item Let $f \in \Epi_{\MC}(A,B)$ and $g \in \Epi_{\MC}(B,C)$. \rex{} \tcr{(ref prev ex)} implies that $f \in \Mono_{\op{\MC}}(B,A)$ and $g \in \Mono_{\op{\MC}}(C,B)$, \tcr{(ref prev part)} then implies that
			\begin{align*}
				g \circ_{\MC} f 
				& = f \circ_{\op{\MC}} g \\
				& \in \Mono_{\op{\MC}} \\
				& = \Epi_{\MC}(A,C).
			\end{align*} 
			Since $f \in \Epi_{\MC}(A,B)$ and $g \in \Epi_{\MC}(B,C)$ are arbitrary, we have that for each $f \in \Epi_{\MC}(A,B)$ and $g \in \Epi_{\MC}(B,C)$, $g \circ_{\MC} f \in \Epi_{\MC}(A,C)$.
		\end{enumerate}
	\end{proof}
	
	\begin{ex}
		Let $\MC$ be a category, $A,B, C \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$ and $g \in \Hom_{\MC}(B,C)$. Then
		\begin{enumerate}
			\item $g \in \Mono_{\MC}$ implies that $g \circ_{\MC} f \in \Mono_{\MC}$ iff $f \in \Mono_{\MC}$.
			\item $f \in \Epi_{\MC}$ implies that $g \circ_{\MC} f \in \Epi_{\MC}$ iff $g \in \Epi_{\MC}$.
		\end{enumerate} 
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Suppose that $g \in \Mono_{\MC}$. 
			\begin{itemize}
				\item $(\implies)$: \\
				Suppose that $g \circ_{\MC} f \in \Mono_{\MC}$. Let $D \in \Obj(\MC)$ and $\al,\be \in \Hom_{\MC}(D, A)$. Suppose that $f \circ_{\MC} \al = f \circ_{\MC} \be$. Then 
				\begin{align*}
					(g \circ_{\MC} f) \circ_{\MC} \al \\
					& = g \circ_{\MC} (f \circ_{\MC} \al) \\
					& = g \circ_{\MC} (f \circ_{\MC} \be) \\
					& = (g \circ_{\MC} f) \circ_{\MC} \be.
				\end{align*}
				Since $g \circ_{\MC} f \in \Mono_{\MC}$, $\al = \be$. Since $D \in \Obj(\MC)$ and $\al,\be \in \Hom_{\MC}(D, A)$ with $f \circ_{\MC} \al = f \circ_{\MC} \be$ are arbitrary, we have that for each $D \in \Obj(\MC)$ and $\al,\be \in \Hom_{\MC}(D, A)$, $f \circ_{\MC} \al = f \circ_{\MC} \be$ implies that $\al = \be$. Thus $f \in \Mono_{\MC}$.
				\item $(\impliedby)$: \\
				Suppose that $f \in \Mono_{\MC}$. Since $g \in \Mono_{\MC}$, \rex{} \tcr{(ref prev ex)} implies that $g \circ_{\MC} f \in \Mono_{\MC}$.
			\end{itemize}
			\item Suppose that $f \in \Epi_{\MC}$. \rex{} \tcr{(ref prev ex abotu duality)} implies that $f \in \Mono_{\op{\MC}}$. Then
			\begin{align*}
				g \circ_{\MC} f \in \Epi_{\MC}
				& \iff g \circ_{\MC} f \in \Mono_{\op{\MC}} \quad \text{(\tcr{ref prev ex about duality})} \\
				& \iff f \circ_{\op{\MC}} g \in \Mono_{\op{\MC}} \\
				& \iff g \in \Mono_{\op{\MC}} \quad \text{(\tcr{ref prev part})} \\
				& \iff g \in \Epi_{\MC} \quad \text{(\tcr{ref prev ex about duality})}.
			\end{align*}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{15011}
		Let $\MC$ be a category and $A,B \in \Obj(\MC)$. Then $\Iso_{\MC}(A, B) \subset \Mono_{\MC}(A, B) \cap \Epi_{\MC}(A, B)$. 
	\end{ex}
	
	\begin{proof}
		Let $f \in \Iso_{\MC}(A, B)$. 
		\begin{itemize}
			\item (monomorphism): \\
			Let $C \in \Obj(\MC)$ and $g, h \in \Hom_{\MC}(C, A)$. Suppose that $f \circ_{\MC} g = f \circ_{\MC} h$. Then
			\begin{align*}
				g 
				& = \id_A \circ_{\MC} g \\
				& = (f^{-1} \circ_{\MC} f) \circ_{\MC} g \\
				& = f^{-1} \circ_{\MC} (f \circ_{\MC} g) \\
				& = f^{-1} \circ_{\MC} (f \circ_{\MC} h) \\
				& = (f^{-1} \circ_{\MC} f) \circ_{\MC} h \\
				& = \id_A \circ_{\MC} h \\
				& = h
			\end{align*}
			Since $g, h \in \Hom_{\MC}(C, A)$ with $f \circ_{\MC} g = f \circ_{\MC} h$ are arbitrary, we have that for each $g, h \in \Hom_{\MC}(C, A)$, $f \circ_{\MC} g = f \circ_{\MC} h$ implies that $g = h$. Therefore $f \in \Mono_{\MC}(A, B)$.
			\item  (epimorphism): \\
			Let $C \in \Obj(\MC)$ and $g, h \in \Hom_{\MC}(B, C)$. Suppose that $ g \circ_{\MC} f = h \circ_{\MC} f$. Then
			\begin{align*}
				g 
				& = g \circ_{\MC} \id_B \\
				& = g \circ_{\MC} (f \circ_{\MC} f^{-1}) \\
				& = (g \circ_{\MC} f) \circ_{\MC} f^{-1} \\
				& = (h \circ_{\MC} f) \circ_{\MC} f^{-1} \\
				& = h \circ_{\MC} (f \circ_{\MC} f^{-1}) \\
				& = h \circ_{\MC} \id_B \\
				& = h
			\end{align*}
			Since $g, h \in \Hom_{\MC}(B, C)$ with $g \circ_{\MC} f = h \circ_{\MC} f$ are arbitrary, we have that for each $g, h \in \Hom_{\MC}(B, C)$, $g \circ_{\MC} f = h \circ_{\MC} f$ implies that $g = h$. Therefore $f \in \Epi_{\MC}(A, B)$. 
		\end{itemize}
		Thus $f \in \Mono_{\MC}(A, B) \cap \Epi_{\MC}(A, B)$. Since $f \in \Iso_{\MC}(A, B)$ is arbitrary, we have that for each $f \in \Iso_{\MC}(A, B)$, $f \in \Mono_{\MC}(A, B) \cap \Epi_{\MC}(A, B)$. Hence $\Iso_{\MC}(A, B) \subset \Mono_{\MC}(A, B) \cap \Epi_{\MC}(A, B)$.
	\end{proof}
	
	\begin{ex}
		Let $\MC$ be a category and $X \in \Obj(\MC)$. Then $\id_X \in \Mono_{\MC} \cap \Epi_{\MC}$.
	\end{ex}
	
	\begin{proof}
		\tcr{ref prev ex in isomorphism section} implies that $\id_X \in \Aut_{\MC}(X)$. \tcr{ref prev ex} implies that $\id_X \in \Mono_{\MC} \cap \Epi_{\MC}$.
	\end{proof}
	
	\begin{ex} \lex{15010}
		\tcr{mono/epi in $\bSet$}
		Let $A, B \in \Obj(\bSet)$ and $f \in \Hom_{\bSet}(A,B)$. Then 
		\begin{enumerate}
			\item $f$ is a monomorphism iff $f$ is injective
			\item $f$ is an epimorphism iff $f$ is surjective 
		\end{enumerate} 
		\tbf{Hint: } consider $C \defeq \{0\}$ and $C \defeq \{0,1\}$.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{itemize}
				\item $(\implies)$: \\
				Suppose that $f$ is injective. Let $C \in \Obj(\bSet)$ and $g,h \in \Hom_{\bSet}(C, A)$. Suppose that $f \circ_{\bSet} g = f \circ_{\bSet} h$. Let $x \in C$. Then $f(g(x)) = f(h(x))$. Injectivity of $f$ implies that $g(x) = h(x)$. Since $x \in C$ is arbitrary, $g = h$. Hence $f \in \Mono_{\bSet}$. \\
				\item $(\impliedby)$: \\
				Conversely, suppose that $f \in \Mono_{\bSet}$. Let $a, b \in A$. Suppose that $f(a) = f(b)$. Set $C = \{0\}$ and define $g,h: C \rightarrow A$ by $g(0) = a$ and $h(0) = b$. Then  
				\begin{align*}
					f \circ_{\bSet} g(0) 
					& = f(g(0)) \\
					& = f(a) \\
					& = f(b) \\
					& = f(h(0)) \\
					& = f \circ_{\bSet} h(0) 
				\end{align*}
				Therefore $f \circ_{\bSet} g = f \circ_{\bSet} h$. Since $f \in \Mono_{\bSet}$, we have that $g = h$. Hence 
				\begin{align*}
					a 
					& = g(0) \\
					& = h(0) \\
					& = b
				\end{align*}
				Since $a, b \in A$ with $f(a) = f(b)$ are arbitrary, we have that for each $a, b \in A$, $f(a) = f(b)$ implies that $a = b$. Thus $f$ is injective.
			\end{itemize}
			\item 
			\begin{itemize}
				\item $(\implies)$: \\
				Suppose that $f$ is surjective. Let $C \in \Obj(\MC)$ and $g,h \in \Hom_{\bSet}(B, C)$. Suppose that $g \circ_{\bSet} f = h \circ_{\bSet} f$. Let $y \in B$. Surjective of $f$ implies that there exists $x \in A$ such that $y = f(x)$. 
				Then 
				\begin{align*}
					g(y)
					& = g(f(x)) \\
					& = g \circ_{\bSet} f (x) \\
					& = h \circ_{\bSet} f (x) \\
					& = h(f(x)) \\
					& = h(y) 
				\end{align*}
				Since $y \in B$ is arbitrary, we have that for each $y \in B$, $g(y) = h(y)$. Hence $g = h$. Since $C \in \Obj(\MC)$ and $g,h \in \Hom_{\bSet}(B, C)$ with $g \circ_{\bSet} f = h \circ_{\bSet} f$ are arbitrary, we have that for each $C \in \Obj(\MC)$ and $g,h \in \Hom_{\bSet}(B, C)$, $g \circ_{\bSet} f = h \circ_{\bSet} f$ implies that $g = h$. Hence $f$ is an epimorphism. \\
				\item $(\impliedby)$: \\
				Conversely, suppose that $f$ is an epimorphism. Define $C \in \Obj(\bSet)$ and $g, h: B \rightarrow C$ by $C \defeq \{0,1\}$, $g \defeq \chi_{f(A)}$ and $h \defeq \chi_{B}$. Then $g \circ_{\bSet} f = h \circ_{\bSet} f$. Since $f \in \Epi_{\MC}$, $g = h$ and $f(A) = B$. Hence $f$ is surjective. 
			\end{itemize} 
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Extremal Monomorphisms and Epimorphisms}
	
	\begin{defn}
		Let $\MC$ be a category, $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Then $f$ is said to be an
		\begin{itemize}
			\item \tbf{extremal monomorphism} if 
			\begin{itemize}
				\item $f \in \Mono_{\MC}$ 
				\item for each $C \in \Obj(\MC)$, $e \in \Epi_{\MC}(A, C)$ and $g \in \Hom_{\MC}(C, B)$, $f = g \circ_{\MC} e$ implies that $e \in \Iso_{\MC}(A, C)$. 
			\end{itemize}
			\item \tbf{extremal epimorphism} if 
			\begin{itemize}
				\item $f \in \Epi_{\MC}$ 
				\item for each $C \in \Obj(\MC)$, $g \in \Hom_{\MC}(A, C)$ and $m \in \Mono_{\MC}(C, B)$, $f = m \circ_{\MC} g$ implies that $m \in \Iso_{\MC}(C, B)$. 
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category.
		\begin{itemize}
			\item We define 
			\begin{itemize}
				\item $\ExtMono_{\MC} \defeq \{f \in \Hom_{\MC}: \text{$f$ is an extremal monomorphism}\}$,
				\item $\ExtEpi_{\MC} \defeq \{f \in \Hom_{\MC}: \text{$f$ is an extremal epiorphism}\}$.
			\end{itemize}
			\item Let $A,B \in \Obj(\MC)$. We define 
			\begin{itemize}
				\item $\ExtMono_{\MC}(A,B) \defeq \ExtMono_{\MC} \cap \Hom_{\MC}(A,B)$,
				\item $\ExtEpi_{\MC}(A,B) \defeq \ExtEpi_{\MC} \cap \Hom_{\MC}(A,B)$.
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category. Then
		\begin{enumerate}
			\item for each $A,B \in \Obj(\MC)$,
			\begin{enumerate}
				\item $\ExtMono_{\op{\MC}}(A,B) = \ExtEpi_{\MC}(B,A)$
				\item $\ExtEpi_{\op{\MC}}(A,B) = \ExtMono_{\MC}(B,A)$
			\end{enumerate}
			\item 
			\begin{enumerate}
				\item $\ExtMono_{\op{\MC}} = \ExtEpi_{\MC}$
				\item $\ExtEpi_{\op{\MC}} = \ExtMono_{\MC}$
			\end{enumerate}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\tcr{FIX!!!}
		\begin{enumerate}
			\item Let $A,B \in \Obj(\MC)$. 
			\begin{itemize}
				\item Let $f \in \ExtMono_{\op{\MC}}(A, B)$. 
				\begin{itemize}
					\item Then $f \in \Mono_{\op{\MC}}(A, B)$. \tcr{ref prev ex in section on monomorphisms} implies that $f \in \Epi_{\MC}(B, A)$. 
					\item Let $C \in \Obj(\MC)$, $g \in \Hom_{\MC}(B,C)$ and $m \in \Mono_{\MC}(C,A)$. Suppose that $f = m \circ_{\MC} g$. Then $g \in \Hom_{\op{\MC}}(C,B)$, \tcr{a prev ex in section on monomorphs} implies that $m \in \Epi_{\op{\MC}}(A,C)$ and $f = g \circ_{\op{\MC}} m$. Since $f \in \ExtMono_{\op{\MC}}(A, B)$, we have that $m \in \Iso_{\op{\MC}}(B, C)$. \rex{} \tcr{(make and ref prev ex that $\Iso_{\MC} = \Iso_{\op{\MC}}$)} implies that $m \in \Iso_{\MC}(C, B)$. Since $C \in \Obj(\MC)$, $g \in \Hom_{\MC}(B,C)$ and $m \in \Mono_{\MC}(C,A)$ are arbitrary, we have that for each $C \in \Obj(\MC)$, $g \in \Hom_{\MC}(B,C)$ and $m \in \Mono_{\MC}(C,A)$, $f = m \circ_{\MC} g$ implies that $m \in \Iso_{\MC}(C, A)$.
				\end{itemize}
				Thus $f \in \ExtEpi_{\MC}(B, A)$. Since $f \in \ExtMono_{\op{\MC}}(A, B)$ is arbitrary, we have that for each $f \in \ExtMono_{\op{\MC}}(A, B)$, $f \in \ExtEpi_{\MC}(B, A)$. Hence $\ExtMono_{\op{\MC}}(A, B) \subset \ExtEpi_{\MC}(B, A)$.
				\item Let $f \in \ExtEpi_{\MC}(B, A)$. 
				\begin{itemize}
					\item Then $f \in \Epi_{\MC}(B, A)$. \tcr{ref prev ex in section on monomorphisms} implies that $f \in \Mono_{\op{\MC}}(A, B)$.
					\item  Let $C \in \Obj(\op{\MC})$, $e \in \Epi_{\op{\MC}}(A,C)$ and $g \in \Hom_{\op{\MC}}(C,B)$. Suppose that $f = g \circ_{\op{\MC}} e$. Then $g \in \Hom_{\MC}(B,C)$, \tcr{a prev ex in section on monomorphs} implies that $e \in \Mono_{\MC}(C, A)$ and $f = e \circ_{\MC} g$. Since $f \in \ExtEpi_{\MC}(B, A)$, we have that $e \in \Iso_{\MC}(C, A)$. \rex{} \tcr{(make and ref prev ex that $\Iso_{\MC} = \Iso_{\op{\MC}}$)} implies that $e \in \Iso_{\op{\MC}}(A, C)$. Since $C \in \Obj(\op{\MC})$, $e \in \Epi_{\op{\MC}}(A,C)$ and $g \in \Hom_{\op{\MC}}(C,B)$ are arbitrary, we have that for each $C \in \Obj(\op{\MC})$, $e \in \Epi_{\op{\MC}}(A,C)$ and $g \in \Hom_{\op{\MC}}(C,B)$, $f = g \circ_{\op{\MC}} e$ implies that $e \in \Iso_{\op{\MC}}(A, C)$.
				\end{itemize}
				Thus $f \in \ExtMono_{\op{\MC}}(A, B)$. Since $f \in \ExtEpi_{\MC}(B, A)$ is arbitrary, we have that for each $f \in \ExtMono_{\op{\MC}}(A, B)$, $f \in \ExtEpi_{\MC}(B, A)$. Hence $\ExtMono_{\op{\MC}}(A, B) \subset \ExtEpi_{\MC}(B, A)$.
			\end{itemize}
			Since $\ExtMono_{\op{\MC}}(A, B) \subset \ExtEpi_{\MC}(B, A)$ and $\ExtMono_{\op{\MC}}(A, B) \subset \ExtEpi_{\MC}(B, A)$, we have that $\ExtMono_{\op{\MC}}(A, B) = \ExtEpi_{\MC}(B, A)$. Since $A,B \in \Obj(\MC)$ are arbitrary, we have that for each $A,B \in \Obj(\MC)$, $\ExtMono_{\op{\MC}}(A, B) = \ExtEpi_{\MC}(B, A)$. Therefore 
			\begin{align*}
				\ExtMono_{\op{\MC}}
				& = \bigcup\limits_{(A,B) \in \Obj(\op{\MC})^2} \ExtMono_{\op{\MC}}(A,B) \\
				& = \bigcup\limits_{(A,B) \in \Obj(\MC)^2} \ExtMono_{\op{\MC}}(A,B) \\
				& = \bigcup\limits_{(B,A) \in \Obj(\MC)^2} \ExtEpi_{\MC}(B,A) \\
				& = \ExtEpi_{\MC}.
			\end{align*}
			\item \tcr{The previous part (ref needed)} implies that 
			\begin{align*}
				\ExtMono_{\MC}
				& = \ExtMono_{\op{(\op{\MC})}} \\
				& = \ExtEpi_{\op{\MC}}.
			\end{align*}
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Regular Monomorphisms and Epimorphisms}
	
	\begin{ex}
		Let $\MC$ be a category, $A,B \in \Obj(\MC)$ and $f,g \in \Hom_{\MC}(A,B)$.
		\tcr{Rewrite using notation $\Eqzr_{\MC}$}
		\begin{enumerate}
			\item Let $M \in \Obj(\MC)$ and $m \in \Hom_{\MC}(M, A)$. If $(M, m)$ is an equalizer of $f$ and $g$, then $m \in \Mono_{\MC}(M, A)$. 
			\item Let $E \in \Obj(\MC)$ and $e \in \Hom_{\MC}(B, E)$. If $(E, e)$ is a coequalizer of $f$ and $g$, then $e \in \Epi_{\MC}(B, E)$. 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Suppose that $(M, m)$ is an equalizer of $f$ and $g$. Let $C \in \Obj(\MC)$ and $\al, \be \in \Hom_{\MC}(C, M)$. Suppose that $m \circ_{\MC} \al = m \circ_{\MC} \be$. Since $(M, m)$ is an equalizer of $f$ and $g$, we have that $f \circ_{\MC} m = g \circ_{\MC} m$, i.e. the following diagram commutes: 
			\[ 
			\begin{tikzcd}[baseline= 7]
				&                                   & B \\
				M \arrow[r, "m"]  & A \arrow[ur, "f"] \arrow[dr, "g"'] &   \\
				&                                   & B \\
			\end{tikzcd}
			\]
			Define $M' \in \Obj(\MC)$ and $m' \in \Hom_{\MC}(M', A)$ by $M' \defeq C$ and $m' \defeq m \circ_{\MC} \al$. Then 
			\begin{align*}
				f \circ_{\MC} m'
				& = f \circ_{\MC} (m \circ_{\MC} \al) \\
				& = (f \circ_{\MC} m) \circ_{\MC} \al \\
				& = (g \circ_{\MC} m) \circ_{\MC} \al \\
				& = g \circ_{\MC} (m \circ_{\MC} \al) \\
				& = g \circ_{\MC} m'.
			\end{align*}
			Since $(E,m)$ is an equalizer of $f$ and $g$, there exists a unique $\phi \in \Hom_{\MC}(E', E)$ such that $m \circ_{\MC} \phi = m'$, i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}[baseline= 7]
				E' \arrow[dr, "m'"] \arrow[dd, "\phi"', dashed]&     & B \\
				& A \arrow[ur, "f"] \arrow[dr, "g"'] &   \\
				E \arrow[ur, "m"'] &                                  & B \\
			\end{tikzcd}
			\]
			Since $m \circ_{\MC} \al = m'$, uniqueness of $\phi$ implies that $\phi = \al$. Since 
			\begin{align*}
				m \circ_{\MC} \be 
				& = m \circ_{\MC} \al \\
				& = m',
			\end{align*}
			uniqueness of $\phi$ implies that $\phi = \be$. Hence $\al = \be$. Since $C \in \Obj(\MC)$ and $\al,\be \Hom_{\MC}(C,E)$ with $m \circ_{\MC} \al = m \circ_{\MC} \be$ are arbitrary, we have that for each $C \in \Obj(\MC)$ and $\al, \be \in \Hom_{\MC}(C, E)$, $m \circ_{\MC} \al = m \circ_{\MC} \be$ implies that $\al = \be$, i.e. we have the following implication of commutative diagrams: 
			\[ 
			\begin{tikzcd}[baseline= 7]
				C \arrow[dr, "\al"]&                                   & \\
				& E \arrow[r, "m"] & A  \\
				C \arrow[ur, "\be"']&                                   & \\
			\end{tikzcd}
			\implies
			\begin{tikzcd}[baseline= 7]
				C \arrow[bend right=60, swap]{r}{\be} \arrow[bend right=-60]{r}{\al} & E  \\
			\end{tikzcd}
			\]
			Thus $m \in \Mono_{\MC}(E, A)$.
			\item \tcr{FINISH!!!}
		\end{enumerate}
	\end{proof}
	
	\begin{defn}
		Let $\MC$ be a category, $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(A,B)$. Then $f$ is said to be a 
		\begin{itemize}
			\item \tbf{regular monomorphism} if there exists $C \in \Obj(\MC)$ and $g,h \in \Hom_{\MC}(B,C)$ such that $(A,f) \in \Eqzr_{\MC}(g,h)$.
			\item \tbf{regular epimorphism} if there exists $C \in \Obj(\MC)$ and $g,h \in \Hom_{\MC}(C,A)$ such that $(B,f) \in \Coeqzr_{\MC}(g,h)$.
		\end{itemize}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category.
		\begin{itemize}
			\item We define 
			\begin{itemize}
				\item $\RegMono_{\MC} \defeq \{f \in \Hom_{\MC}: \text{$f$ is a regular monomorphism}\}$,
				\item $\RegEpi_{\MC} \defeq \{f \in \Hom_{\MC}: \text{$f$ is a regular epiorphism}\}$.
			\end{itemize}
			\item Let $A,B \in \Obj(\MC)$. We define 
			\begin{itemize}
				\item $\RegMono_{\MC}(A,B) \defeq \RegMono_{\MC} \cap \Hom_{\MC}(A,B)$,
				\item $\RegEpi_{\MC}(A,B) \defeq \RegEpi_{\MC} \cap \Hom_{\MC}(A,B)$.
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category. Then
		\begin{enumerate}
			\item for each $A,B \in \Obj(\MC)$,
			\begin{enumerate}
				\item $\RegMono_{\op{\MC}}(A,B) = \RegEpi_{\MC}(B,A)$
				\item $\RegEpi_{\op{\MC}}(A,B) = \RegMono_{\MC}(B,A)$
			\end{enumerate}
			\item 
			\begin{enumerate}
				\item $\RegMono_{\op{\MC}} = \RegEpi_{\MC}$
				\item $\RegEpi_{\op{\MC}} = \RegMono_{\MC}$
			\end{enumerate}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		\tcr{FINISH!!!}
	\end{proof}
	
	\begin{ex}
		Let $\MC$ be a category. Then for each $A,B \in \Obj(\MC)$,
		\begin{enumerate}
			\item $\RegMono_{\MC}(A,B) \subset \ExtMono_{\MC}(A,B)$,
			\item $\RegEpi_{\MC}(A,B) \subset \ExtEpi_{\MC}(A,B)$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		Let $A,B \in \Obj(\MC)$. \tcr{FINISH!!!}
		\begin{enumerate}
			\item 
			\item 
		\end{enumerate}
	\end{proof}
	
	\begin{ex}
		Let $A,B \in \Obj(\bSet)$ and $f,g \in \Hom_{\bSet}(A,B)$. Then $(\Eqzr(f,g), \iota_{\Eqzr(f,g)}) \in \Eqzr_{\bSet}(f,g)$.
	\end{ex}
	
	\begin{proof}\
		Define $E \in \Obj(\bSet)$ by $E \defeq \Eqzr(f,g)$.
		\begin{enumerate}
			\item By definition, $E = \{x \in A: f(x) = g(x)\}$. Therefore for each $x \in E$,
			\begin{align*}
				f \circ_{\bSet} \iota_E(x)
				& = f(\iota_E(x)) \\
				& = f(x) \\
				& = g(x) \\
				& = g(\iota_E(x)) \\
				& = g \circ_{\bSet} \iota_E (x).
			\end{align*}
			Thus $f \circ_{\bSet} \iota_E = g \circ_{\bSet} \iota_E$. 
			\item Let $E' \in \Obj(\bSet)$ and $e' \in \Hom_{\bSet}(E',A)$. Suppose that $f \circ_{\bSet} e' = g \circ_{\bSet} e'$. Let $x \in E'$. Define $a \in A$ by $a \defeq e'(x)$. Then 
			\begin{align*}
				f(a)
				& = f(e'(x)) \\
				& = f \circ_{\bSet} e'(x) \\
				& = f \circ_{\bSet} e'(x) \\
				& = g(e'(x)) \\
				& = g(a).
			\end{align*}
			Thus $a \in \Eqzr(f,g)$. Therefore
			\begin{align*}
				e'(x)
				& = a \\
				& \in \Eqzr(f,g) \\
				& = E.
			\end{align*}
			Since $x \in E'$ is arbitrary, we have that for each $x \in E'$, $e'(x) \in E$.
			Define $\phi \in \Hom_{\bSet}(E', E)$ by $\phi(x) \defeq e'(x)$. 
			\begin{itemize}
				\item For each $x \in E'$,
				\begin{align*}
					\iota_E \circ_{\bSet} \phi(x) \\
					& = \iota_E(\phi(x)) \\
					& = \iota_E (e'(x)) \\
					& = e'(x).
				\end{align*}
				Thus $\iota_E \circ_{\bSet} \phi = e'$.
				\item Let $\phi' \in \Hom_{\bSet}(E', E)$. Suppose that $\iota_E \circ_{\bSet} \phi' = e'$. Then for each $x \in E'$,
				\begin{align*}
					\phi'(x)
					& = \iota_E (\phi'(x)) \\
					& = \iota_E \circ_{\bSet} \phi'(x) \\
					& = e'(x) \\
					& = \iota_E \circ_{\bSet} \phi(x) \\
					& = \iota_E (\phi(x)) 
					& = \phi(x).
				\end{align*}
				Hence $\phi' = \phi$. Since $\phi' \in \Hom_{\bSet}(E', E)$ with $\iota_E \circ_{\bSet} \phi' = e'$ is arbitrary, we have that for each $\phi' \in \Hom_{\bSet}(E', E)$, $\iota_E \circ_{\bSet} \phi' = e'$ implies that $\phi' = \phi$.
			\end{itemize} 
			Thus there exists a unique $\phi \in \Hom_{\bSet}(E', E)$ such that $\iota_E \circ_{\bSet} \phi = e'$. Since $E' \in \Obj(\bSet)$ and $e' \in \Hom_{\bSet}(E',A)$ with $f \circ_{\bSet} e' = g \circ_{\bSet} e'$ are arbitrary, we have that for each $E' \in \Obj(\bSet)$ and $e' \in \Hom_{\bSet}(E',A)$, $f \circ_{\bSet} e' = g \circ_{\bSet} e'$ implies that there exists a unique $\phi \in \Hom_{\bSet}(E', E)$ such that $\iota_E \circ_{\bSet} \phi = e'$. 
		\end{enumerate}
		Thus $(E, \iota_E) \in \Eqzr_{\bSet}(f,g)$. 
	\end{proof}
	
	\begin{ex}
		We have that $\RegMono_{\bSet} = \Mono_{\bSet}$.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item \tcr{a prev ex} implies that $\RegMono_{\bSet} \subset \Mono_{\bSet}$.
			\item Let $m \in \Mono_{\bSet}$. Define $M, A \in \Obj(\bSet)$ by $M \defeq \dom_{\bSet}(m)$ and $A \defeq \cod_{\bSet}(m)$. \tcr{a prev ex} implies that $m$ is injective. Define $B \in \Obj(\bSet)$ and $f,g \in \Hom_{\bSet}(A,B)$ by $B \defeq m(M) \cup \{0,1\}$ and
			\[
			f(x) \defeq 
			\begin{cases}
				x, & x \in m(M) \\
				0, & x \in m(M)^c,
			\end{cases}
			g(x) \defeq 
			\begin{cases}
				x, & x \in m(M) \\
				1, & x \in m(M)^c.
			\end{cases}
			\]
			Define $E \in \Obj(\bSet)$ by $E \defeq \Eqzr(f,g)$. Then 
			\begin{align*}
				E
				& = \Eqzr(f,g) \\
				& = \{x \in A: f(x) = g(x)\} \\
				& = m(M).
			\end{align*}
			\begin{enumerate}
				\item By construction, for each $x \in M$, 
				\begin{align*}
					f \circ_{\bSet} m(x)
					& = f(m(x)) \\
					& = g(m(x)) \quad \text{(since $m(x) \in E$)} \\
					& = g \circ_{\bSet} m(x).
				\end{align*}
				Thus $f \circ_{\bSet} m = g \circ_{\bSet} m$, i.e. the following diagram commutes: 
				\[ 
				\begin{tikzcd}[baseline= 7]
					&                                   & B \\
					M \arrow[r, "m"]  & A \arrow[ur, "f"] \arrow[dr, "g"'] &   \\
					&                                   & B \\
				\end{tikzcd}
				\]
				\item Let $M' \in \Obj(\bSet)$ and $m' \in \Hom_{\bSet}(M', A)$. Suppose that $f \circ_{\bSet} m' = g \circ_{\bSet} m'$. \rex{} \tcr{ref prev ex} implies that $(E, \iota_E) \in \Eqzr_{\bSet}(f,g)$. Thus 
				\begin{itemize}
					\item there exists a unique $\al \in \Hom_{\bSet}(M, E)$ such that $\iota_E \circ_{\bSet} \al = m$,
					\item there exists a unique $\al' \in \Hom_{\bSet}(M', E)$ such that $\iota_E \circ_{\bSet} \al' = m'$,
				\end{itemize}
				i.e. the following diagram commutes:
				\[ 
				\begin{tikzcd}[baseline= 7]
					M' \arrow[dr, "m'"] \arrow[bend right=60, swap, dashed]{dd}{\al'}&     & B \\
					M \arrow[r, "m"] \arrow[d, "\al"', dashed] & A \arrow[ur, "f"] \arrow[dr, "g"'] &   \\
					E \arrow[ur, "\iota_E"'] &                                  & B \\
				\end{tikzcd}
				\]
				Since $\iota_E \circ m|^E = m$, uniqueness of $\al$ implies that $\al = m|^E$. Since $m$ is injective, $m|^E \in \Iso_{\bSet}(M, E)$. 
				\begin{itemize}
					\item Define $\phi \in \Hom_{\bSet}(M', M)$ by $\phi' \defeq \al^{-1} \circ_{\bSet} \al'$. Then 
					\begin{align*}
						m \circ_{\bSet} \phi 
						& = (\iota_E \circ_{\bSet} m|^E) \circ_{\bSet} (\al^{-1} \circ_{\bSet} \al') \\
						& = \iota_E \circ_{\bSet} (m|^E \circ_{\bSet} \al^{-1}) \circ_{\bSet} \al' \\
						& = \iota_E \circ_{\bSet} (\al \circ_{\bSet} \al^{-1}) \circ_{\bSet} \al' \\
						& = \iota_E \circ_{\bSet} \id_E \circ_{\bSet} \al' \\
						& = \iota_E \circ_{\bSet} \al' \\
						& = m'.
					\end{align*}
					\item  
					\begin{itemize}
						\item Let $\phi_0 \in \Hom_{\bSet}(M', M)$. Suppose that $m \circ \phi_0 = m'$. Then 
						\begin{align*}
							\iota_E \circ_{\bSet} (\al \circ_{\bSet} \phi_0) 
							& = (\iota_E \circ_{\bSet} \al) \circ_{\bSet} \phi_0 \\
							& = (\iota_E \circ_{\bSet} m|^E) \circ_{\bSet} \phi_0 \\
							& = m \circ_{\bSet} \phi_0 \\
							& = m'.
						\end{align*}
						Uniqueness of $\al'$ implies that $\al \circ_{\bSet} \phi_0 = \al'$. Since $\phi_0 \in \Hom_{\bSet}(M', M)$ such that $m \circ \phi_0 = m'$ is arbitrary, we have that for each $\phi_0 \in \Hom_{\bSet}(M', M)$, $m \circ \phi_0 = m'$ implies that $\al \circ_{\bSet} \phi_0 = \al'$.
						\item In particular, \tcr{ref prev part (above)} implies that $\al \circ_{\bSet} \phi = \al'$.
						\item Let $\phi' \in \Hom_{\bSet}(M', M)$. Suppose that $m \circ \phi' = m'$. \tcr{ref above prev parts} implies that
						\begin{align*}
							\al \circ_{\bSet} \phi' 
							& = \al' \\
							& = \al \circ_{\bSet} \phi.
						\end{align*}
						Since 
						\begin{align*}
							\al
							& = m|^E \\
							& \in \Iso_{\bSet}(M,E) \\
							& \subset \Mono_{\bSet}(M, E),
						\end{align*}
						we have that $\phi' = \phi$. Since $\phi' \in \Hom_{\bSet}(M', M)$ with $m \circ \phi' = m'$ is arbitrary, we have that for each $\phi' \in \Hom_{\bSet}(M', M)$, $m \circ \phi' = m'$ implies that $\phi' = \phi$.
					\end{itemize}
				\end{itemize}
				Thus there exists a unique $\phi \in \Hom_{\bSet}(M', M)$ such that $m \circ_{\bSet} \phi = m'$. Since $M' \in \Obj(\bSet)$ and $m' \in \Hom_{\bSet}(M', A)$ with $f \circ_{\bSet} m' = g \circ_{\bSet} m'$ are arbitrary, we have that for each $M' \in \Obj(\bSet)$ and $m' \in \Hom_{\bSet}(M', A)$, $f \circ_{\bSet} m' = g \circ_{\bSet} m'$ implies that there exists a unique $\phi \in \Hom_{\bSet}(M', M)$ such that $m \circ_{\bSet} \phi = m'$, i.e. the following diagram commutes:
				\[ 
				\begin{tikzcd}[baseline= 7]
					M' \arrow[dr, "m'"] \arrow[dd, "\phi"', dashed]&     & B \\
					& A \arrow[ur, "f"] \arrow[dr, "g"'] &   \\
					M \arrow[ur, "m"'] &                                  & B \\
				\end{tikzcd}
				\]
			\end{enumerate}
			Therefore $(M, m) \in \Eqzr_{\bSet}(f,g)$. Hence $m \in \RegMono_{\bSet}$. Since $m \in \Mono_{\bSet}$ is arbitrary, we have that for each $m \in \Mono_{\bSet}$, $m \in \RegMono_{\bSet}$. Thus $\Mono_{\bSet} \subset \RegMono_{\bSet}$. 
		\end{itemize}
		Since $\RegMono_{\bSet} \subset \Mono_{\bSet}$ and $\Mono_{\bSet} \subset \RegMono_{\bSet}$, we have that $\RegMono_{\bSet} = \Mono_{\bSet}$.
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Subobjects and Quotient Objects}
	
	\begin{defn}
		\tcr{maybe move this to subsection on subcategories, define wide category generated by hom closed morphisms}
		Let $\MC$ be a category and $H \subset \Hom_{\MC}$. Then $H$ is said to be \tbf{hom closed} if 
		\begin{enumerate}
			\item 
			\item 
		\end{enumerate}
	\end{defn}
	
	\begin{defn}
		\tcr{define wide category with all morphisms mono, resp epi}
		Let $\MC$ be a category. We define 
		\begin{itemize}
			\item \tbf{the restriction of $\MC$ to $\Mono_{\MC}$,} denoted $\bMono(\MC, M)$, by
			\begin{itemize}
				\item $\Obj(\bMono(\MC, M)) \defeq \Obj(\MC)$
				\item For $A,B \in \Obj(\MC)$, $\Hom_{\bMono(\MC, M)}(A,B) \defeq \Mono_{\MC}(A,B)$
				\item For $A,B, C \in \Obj(\MC)$, $f \in \Hom_{\bMono(\MC, M)}(A, B)$ and $g \in \Hom_{\bMono(\MC, M)}(B, C)$, $g \circ_{\bMono(\MC, M)} f \defeq g \circ_{\MC} f$.
			\end{itemize}
			\item \tbf{the restriction of $\MC$ to $\Epi_{\MC}$,} denoted $\bEpi(\MC)$, by
			\begin{itemize}
				\item $\Obj(\bEpi(\MC)) \defeq \Obj(\MC)$
				\item For $A,B \in \Obj(\MC)$, $\Hom_{\bEpi(\MC)}(A,B) \defeq \Epi_{\MC}(A,B)$
				\item For $A,B, C \in \Obj(\MC)$, $f \in \Hom_{\bEpi(\MC)}(A, B)$ and $g \in \Hom_{\bEpi(\MC)}(B, C)$, $g \circ_{\bEpi(\MC)} f \defeq g \circ_{\MC} f$.
			\end{itemize}
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category. Then 
		\begin{enumerate}
			\item 
			\begin{enumerate}
				\item $\bMono(\MC, M)$ is a category ,
				\item $\bMono(\MC, M)$ is a wide subcategory of $\MC$,
			\end{enumerate}
			\item 
			\begin{enumerate}
				\item $\bEpi(\MC)$ is a category,
				\item $\bEpi(\MC)$ is a wide subcategory of $\MC$.
			\end{enumerate}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		\tcr{clear.} \tcr{fill out, ref exercies showing that composition of mono is mono, $\id_X$ is mono}
	\end{proof}
	
	\begin{ex}
		Let $\MC$ be a category and $X \in \Obj(\MC)$. Then 
		\begin{enumerate}
			\item $\bMono(\MC, M) / X$ is a \tcr{proset category}.
			\item 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		\begin{enumerate}
			\item Let $(A, f), (B, g) \in \bMono(\MC) / X$ and $\phi \in \Hom_{\bMono(\MC) / X}((A,f), (B,g))$. Then  
			\item 
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	\begin{defn}
		Let $\MC$ be a category, $M \subset \Mono_{\MC}$, $A, B \in \Obj(\MC)$ and $f \in \Mono_{\MC}(A,B)$. Then $(A, f)$ is said to be an \tbf{$M$-subobject} of $B$ if $f \in M$.
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category, $M \subset \Mono_{\MC}$ and $X \in \Obj(\MC)$. We define the \tbf{category of $M$-subobjects of $X$}, denoted $\Sub^M_{\MC}(X)$, by 
		\begin{itemize}
			\item $\Obj(\Sub^M_{\MC}(X)) \defeq \{(A, \al) \in \Obj(\MC/X): \text{$\al$ is an $M$-subobject of $X$}\}$
			\item for $(A,f), (B,g) \in \Obj(\Sub_{\MC}^M(X))$, $\Hom_{(\Sub_{\MC}^M(X))}((A,f), (B,g)) \defeq \Hom_{\MC/X}((A,f), (B,g))$
			\item 
		\end{itemize}
	\end{defn}
	
	
	\tcr{is there a notion of full subcategory generated by a set of objects? can we say that $\Sub_{\MC}^M(X)$ is the full subcategory of $\MC/X$ generated by the $M$-subobjects of $X$?}
	
	\begin{ex}
		\tcr{show $\Sub_{\MC}^M(X)$ is a preodered set/category, i.e. if $(A, f)$ and $(B,g)$ are $M$-subobjects of $X$, then $\# \Hom_{\Sub_{\MC}^M(X)}((A,f), (B,g)) \leq 1$.}
	\end{ex}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\chapter{Constructions on Categories}
	
	\section{Subcategories}
	
	\tcr{are subcategories subobjects in $\Cat$ where subobjects are defined as in `Elementary categories, elementary toposes` by mcLarty?, how to place this subsection?}\\
	
	TODO: move this subsection until after functors and natural transformations, maybe even after adjunctions. We definitely want to to be able to characterize subcategories as subobjects of categories and in terms of the inclusion functor, so maybe should come after monomorphisms, subobjects and functors.  We also want to describe subcategories generated by a subgraph, so we need to talk about the graph of a category and the adjoint of the forgetful functor from $\Cat$ to Graph, so maybe put after adjoints, then this will come after limits. Would like to cover the order of subcat, prodcat, coprodcat? quocat? projlimcat?, so need to check of the product cat can come after limits and adjoints and all that. also subobjects should come after slice categories, since we turn slice categories of wide categories generated by graphs whose edges belong to a class of monomorphisms into a proset, but if subobjects come after generated categories, they need to come after adjoints, so maybe we should later give examples of subobjects in Cat as subcats. This sounds good, so we can characterize subcats in terms of the inclusion functor and then then return to subcats as an example in the context of subobjects.\\
	
	The subcategories generated by a graph as an adjunction should also be applicable to describing the topology generated by a subset I think, not sure if there is a lattice formulation of this topic as well and if the adjunct description generalizes this lattice description. Maybe there is just a straight lattice based characteriszation of generated subcateogries when we order by inclusion functors.\\
	
	
	idea: see \href{https://math.stackexchange.com/questions/596071/subcategory-generated-by-a-graph}{https://math.stackexchange.com/questions/596071/subcategory-generated-by-a-graph}
	
	all we need to do is talk about galois connections between the posets of subcats and subgraphs. so we ccan just pull from the lattice notes here. With this, we can define subcategories generated by a subgraph at any time, so no need to discuss subcats after adjoints. so just talk about subcats/prodcats/etc after functors/nat trans/ but before subobjects?. 
	
	So: cats (and their graphs)     functors    natty transf    subcats (with gal conn between posets of subcats and graphs and then subcats generated by subgraphs)    iso/mono/epi     init/terminal   prod(including ) coprod   equal/coequal    pull/push-subobj?
	\tcr{END!!!!!!!!!!!!!!!!!!!!!END!!!!!!!!!!!!!!!!!!!!END!!!!!!!!!!!!!!!!!!!!END!!!!!!!!!!!!!!!!!!!!\\END!!!!!!!!!!!!!!!!!!!!END!!!!!!!!!!!!!!!!!!!!END!!!!!!!!!!!!!!!!!!!!END!!!!!!!!!!!!!!!!!!!!}
	
%	\begin{defn} \ld{def:basics:contructs:subcats:0001}
%		Let $\MC$ be a category. 
%		\begin{itemize}
%			\item Let $\MD_0, \MD_1$ be classes and $\dom, \cod: \MD_1 \rightarrow \MD_0$. Define $\MD_1^{(2)}\subset \MD_1 \times \MD_1$ by $\MD_1^{(2)} \defeq \{(g,f) \in \MD_1 \times \MD_1 : \dom(g) = \cod(f) \}$. Let $\circ: \MD_1^{(2)} \rightarrow \MD_1$. Then $(\MD_0, \MD_1, \dom, \cod, \circ)$ is said to be a \tbf{subcategory of $\MC$} if 
%			\begin{enumerate}
%				\item $(D_0, D_1, \dom, \cod, \circ)$ is a category
%				\item $D_0 \subset \Obj(\MC)$, $D_1 \subset \Hom_{\MC}$
%				\item $(\iota_{\MD_0}, \iota_{\MD_1})$ is a $((\MD_0, \MD_1, \dom, \cod, \circ), \MC)$-functor.
%			\end{enumerate} 
%			\item We define $\Subcat(\MC) \defeq \{\MD: \text{$\ML$ is a subcategory of $\MC$}\}$.
%			\item We define the \tbf{subcategory relation on $\Subcat(\MC)$}, denoted ${\leqcat} \subset \Subcat(\MC) \times \Subcat(\MC)$, by $\MD \leqcat \MC$ iff $\MD$ is a subcat of $\MC$.  
%		\end{itemize}
%	\end{defn}
%	
%	\begin{ex} \lex{ex:basics:contructs:subcats:0002}
%		Let $\MC$ and $\MD$ be quivers. Then $\MD \in \Subcat(\MC)$ iff 
%		\begin{enumerate}
%			\item $\Obj(\MD) \subset \Obj(\MC)$ and $\Hom_{\MD} \subset \Hom_{\MC}$
%			\item for each $X, Y \in \Obj(\MD)$, $\Hom_{\MC}(X,Y) \subset \Hom_{\MC}(X, Y)$. 
%			\item for each $X, Y, Z \in \Obj(\MD)$, $f \in \Hom_{\MD}(X,Y)$ and $g \in \Hom_{\MD}(Y, Z)$, $g \circ_{\MD} f = g \circ_{\MC} f$
%		\end{enumerate} 
%	\end{ex}
%	
%	\begin{proof}\
%		\begin{itemize}
%			\item $(\implies)$: \\
%			Suppose that $\MD \in \Subcat(\MC)$. Set $\iota_{\MD} \defeq (\iota_{\Obj(\MD)}, \iota_{\Hom_{\MD}})$. 
%			\begin{enumerate}
%				\item By \rd{def:basics:contructs:subcats:0001}, $\Obj(\MD) \subset \Obj(\MC)$ and $\Hom_{\MD} \subset \Hom_{\MD}$.
%				\item Let $X,Y \in \Obj(\MD)$. By \rd{def:basics:contructs:subcats:0001}, $X,Y \in \Obj(\MC)$
%				\item 
%			\end{enumerate}
%			
%			By \rd{def:basics:contructs:subcats:0001}, $\Obj(\MD) \subset \Obj(\MC)$, $\Hom_{\MD} \subset \Hom_{\MC}$ and $\iota_{\MD}$ is a $(\MD, \MC)$-functor. 
%			
%			
%			
%			Then $s_{\MQ} \circ \iota_{E_{\ML}} = \iota_{V_{\ML}} \circ s_{\ML}$ and $t_{\MQ} \circ \iota_{E_{\ML}} = \iota_{V_{\ML}} \circ t_{\ML}$, i.e. the following diagrams commute:
%			\[ 
%			\begin{tikzcd}
%				E_{\ML} \arrow[r, "\iota_{E_{\ML}}"] \arrow[d, "s_{\ML}"'] & E_{\MQ}  \arrow[d, "s_{\MQ}"] \\
%				V_{\ML} \arrow[r, "\iota_{V_{\ML}}"']                 & V_{\MQ}
%			\end{tikzcd}
%			\quad 
%			\begin{tikzcd}
%				E_{\ML} \arrow[r, "\iota_{E_{\ML}}"] \arrow[d, "t_{\ML}"'] & E_{\MQ}  \arrow[d, "t_{\MQ}"] \\
%				V_{\ML} \arrow[r, "\iota_{V_{\ML}}"']                 & V_{\MQ}
%			\end{tikzcd}
%			\]
%			Therefore
%			\begin{align*}
%				s_{\MQ}|_{E_{\ML}}
%				& = s_{\MQ} \circ \iota_{E_{\ML}} \\
%				& = \iota_{V_{\ML}} \circ s_{\ML} \\
%				& = s_{\ML}
%			\end{align*}
%			and 
%			\begin{align*}
%				t_{\MQ}|_{E_{\ML}}
%				& = t_{\MQ} \circ \iota_{E_{\ML}} \\
%				& = \iota_{V_{\ML}} \circ t_{\ML} \\
%				& = t_{\ML}.
%			\end{align*}
%			\item $(\impliedby)$: \\
%			Suppose that 
%			\begin{enumerate}
%				\item $V_{\ML} \subset V_{\MQ}$ and $E_{\ML} \subset E_{\MQ}$,
%				\item $s_{\MQ}|_{E_{\ML}} = s_{\ML}$ and $t_{\MQ}|_{E_{\ML}} = t_{\ML}$.
%			\end{enumerate} 
%			Then 
%			\begin{align*}
%				s_{\MQ} \circ \iota_{E_{\ML}} 
%				& = s_{\MQ}|_{E_{\ML}} \\
%				& = s_{\ML} \\
%				& = \iota_{V_{\ML}} \circ s_{\ML}
%			\end{align*}
%			and 
%			\begin{align*}
%				t_{\MQ} \circ \iota_{E_{\ML}} 
%				& = t_{\MQ}|_{E_{\ML}} \\
%				& = t_{\ML} \\
%				& = \iota_{V_{\ML}} \circ t_{\ML}.
%			\end{align*}
%		\end{itemize}
%	\end{proof}
	
	
%	\begin{ex}
%		Let $\MC$ and $\MD$ be quivers. Then $\MD \in \Subcat(\MC)$ iff 
%		\begin{enumerate}
%			\item $\Obj(\MD) \subset \Obj(\MC)$ and $\Hom_{\MD} \subset \Hom_{\MC}$
%			\item $\dom_{\MC}|_{\Hom{\MD}} = \dom_{\MD}$ and $\cod_{\MC}|_{\Hom{\MD}} = \cod_{\MD}$
%			\item for each $X, Y, Z \in \Obj(\MD)$, $f \in \Hom_{\MD}(X,Y)$ and $g \in \Hom_{\MD}(Y, Z)$, $g \circ_{\MD} f = g \circ_{\MC} f$
%		\end{enumerate} 
%	\end{ex}
%	
%	\begin{proof}\
%		\begin{itemize}
%			\item $(\implies)$: \\
%			Suppose that $\MD \in \Subcat(\MC)$. Then $\Obj(\MD) \subset \Obj(\MC)$, $\Hom_{\MD} \subset \Hom_{\MC}$ and $(\iota_{\Obj(\MD)}, \iota_{\Hom_{\MD}})$ is a $(\ML, \MQ)$-functor. Then $s_{\MQ} \circ \iota_{E_{\ML}} = \iota_{V_{\ML}} \circ s_{\ML}$ and $t_{\MQ} \circ \iota_{E_{\ML}} = \iota_{V_{\ML}} \circ t_{\ML}$, i.e. the following diagrams commute:
%			\[ 
%			\begin{tikzcd}
%				E_{\ML} \arrow[r, "\iota_{E_{\ML}}"] \arrow[d, "s_{\ML}"'] & E_{\MQ}  \arrow[d, "s_{\MQ}"] \\
%				V_{\ML} \arrow[r, "\iota_{V_{\ML}}"']                 & V_{\MQ}
%			\end{tikzcd}
%			\quad 
%			\begin{tikzcd}
%				E_{\ML} \arrow[r, "\iota_{E_{\ML}}"] \arrow[d, "t_{\ML}"'] & E_{\MQ}  \arrow[d, "t_{\MQ}"] \\
%				V_{\ML} \arrow[r, "\iota_{V_{\ML}}"']                 & V_{\MQ}
%			\end{tikzcd}
%			\]
%			Therefore
%			\begin{align*}
%				s_{\MQ}|_{E_{\ML}}
%				& = s_{\MQ} \circ \iota_{E_{\ML}} \\
%				& = \iota_{V_{\ML}} \circ s_{\ML} \\
%				& = s_{\ML}
%			\end{align*}
%			and 
%			\begin{align*}
%				t_{\MQ}|_{E_{\ML}}
%				& = t_{\MQ} \circ \iota_{E_{\ML}} \\
%				& = \iota_{V_{\ML}} \circ t_{\ML} \\
%				& = t_{\ML}.
%			\end{align*}
%			\item $(\impliedby)$: \\
%			Suppose that 
%			\begin{enumerate}
%				\item $V_{\ML} \subset V_{\MQ}$ and $E_{\ML} \subset E_{\MQ}$,
%				\item $s_{\MQ}|_{E_{\ML}} = s_{\ML}$ and $t_{\MQ}|_{E_{\ML}} = t_{\ML}$.
%			\end{enumerate} 
%			Then 
%			\begin{align*}
%				s_{\MQ} \circ \iota_{E_{\ML}} 
%				& = s_{\MQ}|_{E_{\ML}} \\
%				& = s_{\ML} \\
%				& = \iota_{V_{\ML}} \circ s_{\ML}
%			\end{align*}
%			and 
%			\begin{align*}
%				t_{\MQ} \circ \iota_{E_{\ML}} 
%				& = t_{\MQ}|_{E_{\ML}} \\
%				& = t_{\ML} \\
%				& = \iota_{V_{\ML}} \circ t_{\ML}.
%			\end{align*}
%		\end{itemize}
%	\end{proof}
	
	
	
	
	
	\begin{defn} \ld{def:basics:contructs:subcats:0001}
		Let $\MC$ be a category. 
		\begin{itemize}
			\item Let $\MD$ be categories. Then $\MD$ is said to be a \tbf{subcategory of $\MC$}, denoted $\MD \subset \MC$, if 
			\begin{enumerate}
				\item $\Obj(\MD) \subset \Obj(\MC)$
				\item for each $A, B \in \Obj(\MD)$, $\Hom_{\MD}(A,B) \subset \Hom_{\MC}(A, B)$
				\item for each $A,B,C \in \Obj(\MD)$, $f \in \Hom_{\MD}(A, B)$ and $g \in \Hom_{\MD}(B, C)$, $g \circ_{\MD} f = g \circ_{\MC} f$
				\item for each $A \in \Obj(\MD)$, $\id_A^{\MD} = \id_A^{\MC}$
			\end{enumerate}
			\item We define $\Subcat(\MC) \defeq \{\MD \in \Cat: \text{$\ML$ is a subcategory of $\MC$}\}$. \tcr{need to give more justification for why we restrict to $\Cat$, with universes, this should not be an issue, but need to formalize it}
			\item We define the \tbf{subcategory relation on $\Subcat(\MC)$}, denoted ${\leqcat} \subset \Subcat(\MC) \times \Subcat(\MC)$, by $\MD \leqcat \MC$ iff $\MD$ is a subcat of $\MC$.  
		\end{itemize}
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category and $\MD \in \Subcat(\MC)$. We define the \tbf{inclusion functor} from $\MD$ to $\MC$, denoted $\iota_{\MD}^{\MC}:\MD \rightarrow \MC$, by 
		\begin{itemize}
			\item $\iota_{\MD}^{\MC}(X) \defeq X, \quad X \in \Obj(\MD)$
			\item $\iota_{\MD}^{\MC}(f) \defeq f \in \Hom_{\MD}$
		\end{itemize}
	\end{defn}
	
	\begin{note}
		When the context is clear, we may write $\iota_{\MD}$ in place of $\iota_{\MD}^{\MC}$.
	\end{note}
	
	\begin{ex}
		Let $\MC$ be a category and $\MD \in \Subcat(\MC)$. Then $\iota_{\MD}:\MD \rightarrow \MC$ is a functor. 
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item Let $X, Y \in \Obj(\MD)$ and $f \in \Hom_{\MD}(X,Y)$. By \rd{def:basics:contructs:subcats:0001},
			\begin{align*}
				\iota_{\MD}(f)
				& = f \\
				& \in \Hom_{\MD}(X,Y) \\
				& \subset \Hom_{\MC}(X,Y) \\
				& = \Hom_{\MC}(\iota_{\MD}(X), \iota_{\MD}(Y)).
			\end{align*}
			\item Let $X,Y,Z \in \Obj(\MD)$, $g \in \Hom_{\MD}(X,Y)$ and $h \in \in \Hom_{\MD}(Y,Z)$. By \rd{def:basics:contructs:subcats:0001},
			\begin{align*}
				\iota_{\MD}(g \circ_{\MD} f)
				& = g \circ_{\MD} f \\
				& = g \circ_{\MC} f \\
				& = \iota_{\MD}(g) \circ_{\MC} \iota_{\MD}(f).
			\end{align*}
			\item Let $X \in \Obj(\MD)$. By \rd{def:basics:contructs:subcats:0001},
			\begin{align*}
				\iota_{\MD}(\id_X^{\MD})
				& = \id_X^{\MD} \\
				& = \id_X^{\MC} \\
				& = \id_{\iota_{\MD}(X)}^{\MC}.
			\end{align*}
		\end{itemize}
		Hence $\iota_{\MD}:\MD \rightarrow \MC$ is a functor. 
	\end{proof}
	
	\begin{defn}
		We define the \tbf{forgetful functor from $\Cat$ to $\bQuiv$}, denoted $\text{Forget}^{\Cat}_{\bQuiv}: \Cat \rightarrow \bQuiv$
		\tcr{finish}  
	\end{defn}
	
	\begin{defn}
		Let $\MC$ be a category and $H \subset \Hom_{\MC}$. We define the \tbf{subcategory of $\MC$ generated by $H$}, denoted $\SubcatGen(H, \MC)$, by $\SubcatGen(H, \MC) \defeq $
	\end{defn}
	
	\begin{ex}
		content...
	\end{ex}
	\begin{defn}
		
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	\begin{defn}
		Let $\MC$ and $\MD$ be categories. Suppose that $\MD$ is a subcategory of $\MC$. Then $\MC$ is said to be 
		\begin{itemize}
			\item \tbf{full} if for each $A, B \in \Obj(\MD)$, $\Hom_{\MD}(A,B) = \Hom_{\MC}(A,B)$,
			\item \tbf{wide} or \tbf{lluf} if for each $\Obj(\MD) = \Obj(\MC)$.
		\end{itemize}
	\end{defn}
	
	\begin{note}
		The motivation for the adjective ``lluf" seems to be that it is just ``full" backwards.  
	\end{note}
	
	\begin{ex}
		content...
	\end{ex}
	
	
	
	\begin{ex}
		\tcr{erase after making iff}
		Let $\MC$ be a category, $\MD_0 \subset \Obj(\MC)$ and $\MD_1 \subset \Hom_{\MC}$. Define $\MD_1^{(2)} \subset \MD_1 \times \MD_1$ by $\MD_1^{(2)} \defeq \{(g,f) \in \MD_1 \times \MD_1: \dom_{\MC}(g) = \cod_{\MC}(f)\}$. If 
		\begin{itemize}
			\item $\dom_{\MC}(\MD_1), \cod_{\MC}(\MD_1) \subset \MD_0$,
			\item $\circ_{\MC}(\MD_1^{(2)}) \subset \MD_1$,
			\item for each $X \in \MD_0$, $\id_X^{\MC} \in \MD_1$,
		\end{itemize}
		then 
		\begin{enumerate}
			\item $(\MD_0, \MD_1, \dom_{\MC}|_{\MD_1}, \cod_{\MC}|_{\MD_1}, \circ_{\MC}|_{\MD_1^{(2)}})$ is a category,
			\item $(\MD_0, \MD_1, \dom_{\MC}|_{\MD_1}, \cod_{\MC}|_{\MD_1}, \circ_{\MC}|_{\MD_1^{(2)}})$ is a subcategory of $\MC$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}
		Set $\dom_{\MD} \defeq \dom_{\MC}|_{\MD_1}$, $\cod_{\MD} \defeq \cod_{\MC}|_{\MD_1}$, $\circ_{\MD} \defeq \circ_{\MC}|_{\MD_1^{(2)}}$ and $\MD \defeq (\MD_0, \MD_1, \dom_{\MC}|_{\MD_1}, \cod_{\MC}|_{\MD_1}, \circ_{\MC}|_{\MD_1^{(2)}})$.
		\begin{enumerate}
			\item 
			\begin{enumerate}
				\item \tbf{(Composition:)} \\
				For each $(g,f) \in \MD_1^{(2)}$, 
				\begin{align*}
					\dom_{\MD}(g \circ_{\MD} f)
					& = \dom_{\MC}(g \circ_{\MC}) \\
					& = \dom_{\MC}(f) \\
					& = \dom_{\MD}(f).
				\end{align*}
				and 
				\begin{align*}
					\cod_{\MD}(g \circ_{\MD} f)
					& = \cod_{\MC}(g \circ_{\MC}) \\
					& = \cod_{\MC}(g) \\
					& = \cod_{\MD}(g).
				\end{align*}
				\item \tbf{(Associativity:)} \\
				For each $f,g,h \in \MD_1$, if $(g,f), (h,g) \in \MD_1^{(2)}$, then 
				\begin{align*}
					(h \circ_{\MD} g) \circ_{\MD} f 
					& = (h \circ_{\MC} g) \circ_{\MC} f \\
					& = h \circ_{\MC} (g \circ_{\MC} f) \\
					& = h \circ_{\MD} (g \circ_{\MD} f).
				\end{align*}  
				\item \tbf{(Identity:)} \\
				Let $X \in \MD_0$. Since $\id_X^{\MC} \in \MD_1$,  
				\begin{align*}
					\dom_{\MD}(\id_X^{\MC}) 
					& = \dom_{\MC}(\id_X^{\MC}) \\
					& = X,
				\end{align*}
				\begin{align*}
					\cod_{\MD}(\id_X^{\MC}) 
					& = \cod_{\MC}(\id_X^{\MC}) \\ 
					& = X,
				\end{align*}
				and for each $f, g \in \MD_1$, if $\dom_{\MD}(f) = X$ and $\cod_{\MD}(g) = X$, then 
				\begin{align*}
					f \circ_{\MD} \id_X^{\MC}
					& = f \circ_{\MC} \id_X^{\MC} \\
					& = f
				\end{align*}
				and 
				\begin{align*}
					\id_X^{\MC} \circ_{\MD} g 
					& = id_X^{\MC} \circ_{\MC} g \\
					& = g.
				\end{align*} 
			\end{enumerate}
			Hence $\MD$ is a category.
			\item Clear by construction.
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Product Categories}
	
	\subsection{Introduction}
	
	\begin{defn} \ld{def:basics:contructs:products:0001}
		Let $\MC$ and $\MD$ be categories. We define the \textbf{product category of $\MC$ and $\MD$}, denoted $\MC \times \MD$ by 
		\begin{itemize}
			\item $\Obj(\MC \times \MD) \defeq \Obj(\MC) \times \Obj(\MD)$
			\item for each $(A, A'), (B, B') \in \Obj(\MC \times \MD)$, 
			$$\Hom_{\MC \times \MD}((A, A'), (B, B')) \defeq \Hom_{\MC}(A, B) \times \Hom_{\MC}(A', B').$$
			\item for each  $(A, A'), (B, B'), (C, C') \in \Obj(\MC \times \MD)$, $(f, f') \in \Hom_{\MC \times \MD}((A, A'), (B, B'))$ and $(g, g') \in \Hom_{\MC \times \MD}((B, B'), (C, C'))$, 
			$$(g,g') \circ_{\MC \times \MD} (f, f') \defeq  (g \circ_{\MC} f, g' \circ_{\MD} f')$$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:products:0002}
		Let $\MC$ and $\MD$ be categories. Then $\MC \times \MD$ is a category. 
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item \textbf{well-definedness of composition: } \\ 
			Let $(A, A'), (B, B'), (C, C') \in \Obj(\MC \times \MD)$, $(f, f') \in \Hom_{\MC \times \MD}((A, A'), (B, B'))$ and $(g, g') \in \Hom_{\MC \times \MD}((B, B'), (C, C'))$. Then $f \in \Hom_{\MC}(A, B)$, $g \in \Hom_{\MC}(B, C)$, $f'  \in \Hom_{\MD}(A', B')$, and  $g' \in \Hom_{\MD}(B', C')$. Hence $g \circ_{\MC} f \in \Hom_{\MC}(A, C)$ and $g' \circ_{\MD} f' \in \Hom_{\MD}(A', C')$. Thus 
			\begin{align*}
				(g,g') \circ_{\MC \times \MD} (f, f') 
				&= (g \circ_{\MC} f, g' \circ_{\MD} f') \\
				& \in \Hom_{\MC \times \MD}((A, A'), (C, C'))
			\end{align*}
			Thus, composition is well defined. \\
			\item \textbf{associativity of composition:} \\
			Let $(A, A'), (B, B'), (C, C'), (D, D') \in \Obj(\MC \times \MD)$, $(f, f') \in \Hom_{\MC \times \MD}((A, A'), (B, B'))$, $(g, g') \in \Hom_{\MC \times \MD}((B, B'), (C, C'))$ and $(h, h') \in \Hom_{\MC \times \MD}((C, C'), (D, D'))$. Then 
			\begin{align*}
				[(h, h') \circ_{\MC \times \MD} (g , g') ] \circ_{\MC \times \MD} (f, f')
				& = (h \circ_{\MC} g, h' \circ_{\MD} g') \circ_{\MC \times \MD} (f, f') \\
				& = ((h \circ_{\MC} g) \circ_{\MC} f, (h' \circ_{\MD} g') \circ_{\MD} f') \\
				& = (h \circ_{\MC} ( g \circ_{\MC} f), h' \circ_{\MD} (g' \circ_{\MD} f')) \\
				& = (h, h') \circ_{\MC \times \MD} (g \circ_{\MC} f, g' \circ_{\MD} f') \\
				& = (h, h') \circ_{\MC \times \MD} [(g, g') \circ_{\MC \times \MD} (f, f')]
			\end{align*} 
			Thus composition is associative. \\
			\item \textbf{existence of identities: } \\
			Let $(A, B) \in \Obj(\MC \times \MD)$, $(f, f'), (g,g') \in \Hom_{\MC \times \MD}$. Suppose that $\dom_{\MC \times \MD}(f, f') = (A, B)$ and $\cod_{\MC \times \MD}(g, g') = (A, B)$. Then $\dom_{\MC}(f) = A$, $\dom_{\MD}(f') = B$, $\cod_{\MC}(g) = A$ and  $\cod_{\MD}(g') = B$. Hence
			\begin{align*}
				(f, f') \circ_{\MC \times \MD} (\id_A^{\MC}, \id_{B}^{\MD}) 
				& = (f \circ_{\MC} \id_A^{\MC}, f' \circ_{\MD} \id_{B}^{\MD}) \\
				& = (f, f)
			\end{align*}
			and
			\begin{align*}
				(\id_A^{\MC}, \id_{B}^{\MD})  \circ_{\MC \times \MD} (g, g')
				& = (\id_A^{\MC} \circ_{\MC} g , \id_{B}^{\MD} \circ_{\MD} g') \\
				& = (g, g')
			\end{align*}
			Therefore $\id_{(A, B)}^{\MC \times \MD} = (\id_A^{\MC}, \id_{B}^{\MD})$.
		\end{itemize}
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:products:0002.1}
		Let $\MC$ and $\MD$ be categories. Then $\MC$ and $\MD$ are small iff $\MC \times \MD$ is small.
	\end{ex}
	
	\begin{proof}
		We have that 
		\begin{align*}
			\text{$\MC$ and $\MD$ are small}
			& \iff \Obj(\MC), \Hom_{\MC}, \Obj(\MD), \Hom_{\MD} \in \Obj(\bSet) \\
			& \text{$\iff \Obj(\MC) \times \Obj(\MD) \in \Obj(\bSet)$ and $\Hom_{\MC} \times \Hom_{\MD} \in \Obj(\bSet)$} \\
			& \text{$\iff (\Obj(\MC \times \MD) \in \Obj(\bSet)$ and $\Hom_{\MC \times \MD} \in \Obj(\bSet)$} \\
			& \text{$\iff \MC \times \MD$ is small}.
		\end{align*}
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:products:0003}
		Let $\MA, \MB, \MC, \MD$ be categories and $F: \MA \rightarrow \MC$, $G: \MB \rightarrow \MD$. We define the \tbf{product functor of $F$ and $G$}, denoted $F \times G: \MA \times \MB \rightarrow  \MC \times \MD$, by 
		\begin{itemize}
			\item $F \times G(A, B) \defeq (F(A), G(B)), \quad (A, B) \in \Obj(\MA \times \MB)$,  
			\item $F \times G(f,g) \defeq (F(f), G(g)), \quad (f,g) \in \Hom_{\MA \times \MB}$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:products:0004}
		Let $\MA, \MB, \MC, \MD$ be categories and $F: \MA \rightarrow \MC$, $G: \MB \rightarrow \MD$. Then $F \times G$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $X, Y \in \Obj(\MA \times \MB)$ and $h \in \Hom_{\MA \times \MB}(X, Y)$. Then there exist $A_1, A_2 \in \Obj(\MA)$, $B_1, B_2 \in \Obj(\MB)$, $f \in \Hom_{\MA}(A_1, A_2)$ and $g \in \Hom_{\MB}(B_1, B_2)$ such that $X = (A_1, B_1)$, $Y = (A_2, B_2)$ and $h = (f, g)$. Since $F(f) \in \Hom_{\MC}(F(A_1), F(A_2))$ and $G(g) \in \Hom_{\MD}(G(B_1), G(B_2))$, we have that 
			\begin{align*}
				F \times G(h)
				& = F \times G(f,g) \\
				& = (F(f), G(g)) \\
				& \in \Hom_{\MA \times \MB} ((F(A_1), G(B_1)), (F(A_2), G(B_2))) \\
				& = \Hom_{\MA \times \MB} (F \times G(A_1, B_1), F \times G(A_2, B_2)) \\
				& = \Hom_{\MA \times \MB} (F \times G(X), F \times G(Y) ).
			\end{align*} 
			\item Let $X_1,X_2,X_3 \in \Obj(\MA \times \MB)$, $h_{1,2} \in \Hom_{\MA \times \MB}(X_1,X_2)$ and $h_{2,3} \in \Hom_{\MA \times \MB}(X_2, X_3)$. Then there exist $A_1, A_2, A_3 \in \Obj(\MA)$, $B_1, B_2, B_3 \in \Obj(\MB)$, $f_{1,2} \in \Hom_{\MA}(A_1, A_2)$, $g_{1,2} \in \Hom_{\MB}(B_1, B_2)$, $f_{2,3} \in \Hom_{\MA}(A_2, A_3)$ and $g_{2,3} \in \Hom_{\MB}(B_2, B_3)$, such that $X_1 = (A_1, B_1)$, $X_2 = (A_2, B_2)$, $X_3 = (A_3, B_3)$, $h_{1,2} = (f_{1,2}, g_{1,2})$ and $h_{2,3} = (f_{2,3}, g_{2,3})$. Then 
			\begin{align*}
				F \times G(h_{2,3} \circ_{\MA \times B} h_{1,2}) 
				& = F \times G ((f_{2,3}, g_{2,3}) \circ_{\MA \times \MB}, (f_{1,2}, g_{1,2})) \\
				& = F \times G (f_{2,3} \circ_{\MA} f_{1,2}, g_{2,3} \circ_{\MB} g_{1,2}) \\
				& = (F(f_{2,3} \circ_{\MA} f_{1,2}), G(g_{2,3} \circ_{\MB} g_{1,2})) \\
				& = (F(f_{2,3}) \circ_{\MC} F(f_{1,2}), G(g_{2,3}) \circ_{\MD} G(g_{1,2})) \\
				& = (F(f_{2,3}), G(g_{2,3})) \circ_{\MC \times \MD} (F(f_{1,2}), G(g_{1,2})) \\
				& = F \times G(f_{2,3}, g_{2,3}) \circ_{\MC \times \MD} F \times G(f_{1,2}, g_{1,2}) \\
				& = F \times G(h_{2,3}) \circ_{\MC \times \MD} F \times G(h_{1,2}).
			\end{align*}
			\item Let $X \in \Obj(\MA \times \MB)$. Then there exists $A \in \Obj(\MA)$ and $B \in \Obj(\MB)$ such that $X = (A, B)$. Then 
			\begin{align*}
				F \times G(\id_X^{\MA \times \MB})
				& = F \times G(\id_{(A,B)}^{\MA \times \MB}) \\
				& = F \times G(\id_A^{\MA}, \id_B^{\MB}) \\
				& = (F(\id_A^{\MA}), G(\id_B^{\MB})) \\
				& = (\id_{F(A)}^{\MC}, \id_{G(B)}^{\MD}) \\
				& = \id_{(F(A), G(B))}^{\MC \times \MD} \\
				& = \id_{F \times G(A,B)}^{\MC \times \MD} \\
				& = \id_{F \times G(X)}^{\MC \times \MD}.
			\end{align*}
		\end{enumerate}
		Hence $F \times G$ is a functor.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:products:0004.1}
		 Let $\MC_1, \MC_2, \MC_3 \MD_1, \MD_2, \MD_3 \in \Obj(\Cat)$, $F_{1,2} \in \Hom_{\Cat}(\MC_1, \MC_2)$, $F_{2,3} \in \Hom_{\Cat}(\MC_2, \MC_3)$, $G_{1,2} \in \Hom_{\Cat}(\MD_1, \MD_2)$ and $G_{2,3} \in \Hom_{\Cat}(\MD_2, \MD_3)$. Then 
		 $$(F_{2,3} \circ_{\Cat} F_{1,2}) \times (G_{2,3} \circ_{\Cat} G_{1,2}) = (F_{2,3} \times G_{2,3}) \circ_{\Cat} (F_{1,2} \times G_{1,2}).$$
	\end{ex}
	
	\begin{proof}
		\begin{itemize}
			\item For each $A \in \Obj(\MC_1)$ and $B \in \Obj(\MD_1)$, we have that 
			\begin{align*}
				[(F_{2,3} \circ_{\Cat} F_{1,2}) \times (G_{2,3} \circ_{\Cat} G_{1,2})](A,B)
				& = (F_{2,3} \circ_{\Cat} F_{1,2}(A), (G_{2,3} \circ_{\Cat} G_{1,2}(B)) \\
				& = (F_{2,3} (F_{1,2}(A)), G_{2,3}(G_{1,2}(B))) \\
				& = (F_{2,3} \times G_{2,3})(F_{1,2}(A), G_{1,2}(B)) \\
				& = (F_{2,3} \times  G_{2,3})((F_{1,2} \times G_{1,2})(A, B)) \\
				& = [(F_{2,3} \times G_{2,3}) \circ_{\Cat } (F_{1,2} \times G_{1,2})](A, B).
			\end{align*}
			\item For each $A_1, A_2 \in \Obj(\MC_1)$, $B_1, B_2 \in \Obj(\MD_1)$
			Then 
			\begin{align*}
				(F_{2,3} \circ_{\Cat} F_{1,2}) \times (G_{2,3} \circ_{\Cat} G_{1,2})(f,g)
				& = (F_{2,3} \circ_{\Cat} F_{1,2}(f), G_{2,3} \circ_{\Cat} G_{1,2}(g)) \\
				& = (F_{2,3}(F_{1,2}(f)), G_{2,3}(G_{1,2}(g)) \\
				& = (F_{2,3} \times G_{2,3})(F_{1,2}(f), G_{1,2}(g)) \\
				& = (F_{2,3} \times G_{2,3})((F_{1,2} \times G_{1,2})(f,g)) \\
				& = (F_{2,3} \times G_{2,3}) \circ_{\Cat}(f,g).
			\end{align*}
		\end{itemize}
		Hence $(F_{2,3} \circ_{\Cat} F_{1,2}) \times (G_{2,3} \circ_{\Cat} G_{1,2}) = (F_{2,3} \times G_{2,3}) \circ_{\Cat} (F_{1,2} \times G_{1,2})$.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:products:0004.2}
		Let $\MC, \MD \in \Obj(\Cat)$. Then $\id_{\MC}^{\Cat} \times \id_{\MD}^{\Cat} = \id_{\MC \times \MD}^{\Cat}$.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item For each $(A,B) \in \Obj(\MC \times \MD)$,
			\begin{align*}
				\id_{\MC}^{\Cat} \times \id_{\MD}^{\Cat}(A,B)
				& = (\id_{\MC}^{\Cat}(A), \id_{\MD}^{\Cat}(B)) \\
				& = (A, B) \\
				& = \id_{\MC \times \MD}^{\Cat}(A,B).
			\end{align*}
			\item For each $(f,g) \in \Hom_{\MC \times \MD}$, 
			\begin{align*}
				\id_{\MC}^{\Cat} \times \id_{\MD}^{\Cat}(f,g) \\
				& = (\id_{\MC}^{\Cat}(f), \id_{\MD}^{\Cat}(g)) \\
				& = (f, g) \\
				& = \id_{\MC \times \MD}^{\Cat}(f,g).
			\end{align*}
		\end{itemize}
		Hence $\id_{\MC}^{\Cat} \times \id_{\MD}^{\Cat} = \id_{\MC \times \MD}^{\Cat}$.
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:products:0004.3}
		We define the \tbf{product functor on $\Cat$}, denoted $(- \times -): \Cat \times \Cat \rightarrow \Cat$, by 
		\begin{itemize}
			\item $(- \times -) (\MA, \MB) \defeq \MA \times \MB , \quad (\MA, \MB) \in \Obj(\Cat \times \Cat)$,
			\item $(- \times -) (F, G) \defeq F \times G$, $\quad$ $(\MC_1, \MD_1), (\MC_1, \MD_2) \in \Obj(\Cat \times \Cat)$ and $(F, G) \in \Hom_{\Cat \times \Cat}((\MC_1, \MD_1), (\MC_2, \MD_2))$.
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:products:0004.4}
		We have that $(- \times -): \Cat \times \Cat \rightarrow \Cat$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $(\MC_1, \MD_1), (\MC_2, \MD_2) \in \Obj(\Cat \times \Cat)$ and $(F,G) \in \Hom_{\Cat \times \Cat}((\MC_1, \MD_1), (\MC_2, \MD_2))$. \rex{ex:basics:contructs:products:0004} implies that 
			\begin{align*}
				(- \times -)(F,G)
				& = F \times G \\
				& \in \Hom_{\Cat}(\MC_1 \times \MD_1, \MC_2 \times \MD_2) \\
				& = \Hom_{\Cat}((- \times -)(\MC_1, \MD_1), (- \times -)(\MC_2, \MD_2)).
			\end{align*}
			\item Let $(\MC_1, \MD_1), (\MC_2, \MD_2), (\MC_3, \MD_3) \in \Obj(\Cat \times \Cat)$, $(F_{1,2},G_{1,2}) \in \Hom_{\Cat \times \Cat}((\MC_1, \MD_1), (\MC_2, \MD_2))$ and $(F_{2,3},G_{2,3}) \in \Hom_{\Cat \times \Cat}((\MC_2, \MD_2), (\MC_3, \MD_3))$. \rex{ex:basics:contructs:products:0004.1} implies that
			\begin{align*}
				(- \times -)((F_{2,3},G_{2,3}) \circ_{\Cat \times \Cat} (F_{1,2},G_{1,2}))
				& = (- \times -)(F_{2,3} \circ_{\Cat} F_{1,2}, G_{2,3} \circ_{\Cat} G_{1,2}) \\
				& = (F_{2,3} \circ_{\Cat} F_{1,2}) \times (G_{2,3} \circ_{\Cat} G_{1,2}) \\
				& = (F_{2,3} \times G_{2,3}) \circ_{\Cat} (F_{1,2} \times G_{1,2}) \\
				& = (- \times -)(F_{2,3}, G_{2,3}) \circ_{\Cat} (- \times -)(F_{1,2}, G_{1,2}).
			\end{align*} 
			\item \rex{ex:basics:contructs:products:0004.2} implies that for each $(\MC, \MD) \in \Obj(\Cat \times \Cat)$, 
			\begin{align*}
				(- \times -)(\id_{(\MC, \MD)}^{\Cat \times \Cat})
				& = (- \times -)(\id_{\MC}^{\Cat}, \id_{\MD}^{\Cat}) \\
				& = \id_{\MC}^{\Cat} \times \id_{\MD}^{\Cat} \\
				& = \id_{\MC \times \MD}^{\Cat} \\
				& = \id_{(- \times -)(\MC, \MD)}^{\Cat}.
			\end{align*}
		\end{enumerate}
		Hence $(- \times -): \Cat \times \Cat \rightarrow \Cat$ is a functor.
	\end{proof}
	
	\begin{ex}
		\tcr{maybe switch order of 'basic construction and operations' and 'fundamental structures' and redo the previous exercises by showing that if $\MC$ has finite products, then $\times : \MC \times \MC \mapsto \MC$ given by $\times (A,B) \defeq A \times B$ and $\times(f, g) \defeq f \times g$ is a functor and then the previous exercise would be a corollary with $\MC = \Cat$ (if we show that $(\MC \times \MD, (\pi_{\MC}, \pi_{\MD})) \in \Prod_{\Cat}(\MC, \MD)$ and $F \times G$ is the product of morphisms in $\Cat$ as defined in the section on products in the basic ).}
	\end{ex}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Slicing}
	
	\begin{defn} \ld{def:basics:contructs:products:0005}
		Let $\MA, \MB, \MD$ be categories, $F: \MA \times \MB \rightarrow \MD$ and $A_0 \in \Obj(\MA)$, $B_0 \in \Obj(\MB)$. We define the 
		\begin{itemize}
			\item \tbf{slice functor of $F$ at $B_0$}, denoted $F(\cdot, B_0): \MA \rightarrow \MD$ by 
			\begin{itemize}
				\item $F(\cdot, B_0)(A) \defeq F(A, B_0), \quad A \in \Obj(\MA)$
				\item $F(\cdot, B_0)(f) \defeq F(f, \id_{B_0}^{\MB}), \quad f \in \Hom_{\MA}$
			\end{itemize} 
			\item \tbf{slice functor of $F$ at $A_0$}, denoted $F(A_0, \cdot): \MB \rightarrow \MD$ 
			\begin{itemize}
				\item $F(A_0, \cdot)(B) \defeq F(A, B), \quad B \in \MB$
				\item $F(A_0, \cdot)(g) \defeq F(\id_{A_0}^{\MA}, g), \quad g \in \Hom_{\MB}$
			\end{itemize} 			
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:products:0006}
		Let $\MA, \MB, \MD$ be categories, $F: \MA \times \MB \rightarrow \MD$. Then 
		\begin{enumerate}
			\item for each $B_0 \in \Obj(\MB)$, $F(\cdot, B_0): \MA \rightarrow \MD$ is a functor,
			\item for each $A_0 \in \Obj(\MA)$, $F(A_0, \cdot): \MB \rightarrow \MD$ is a functor.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $B_0 \in \Obj(\MB)$.
			\begin{enumerate}
				\item Let $A_1, A_2 \in \Obj(\MA)$ and $f_{12} \in \Hom_{\MA}(A_1, A_2)$. Then $(f_{12}, \id_{B_0}^{\MB}) \in \Hom_{\MA \times \MB}((A_1, B_0), (A_2, B_0))$. Since $F:\MA \times \MB \rightarrow \MD$, we have that
				\begin{align*}
					F(\cdot, B_0)(f_{12})
					& = F(f_{12}, \id_{B_0}^{\MB}) \\
					& \in \Hom_{\MD}(F(A_1, B_0), F(A_2, B_0)) \\
					& = \Hom_{\MD}(F(\cdot, B_0)(A_1), F(\cdot, B_0)(A_2)) \\
				\end{align*}
				\item Let $A_1, A_2, A_3 \in \Obj(\MA)$, $f_{12} \in \Hom_{\MA}(A_1, A_2)$ and $f_{23} \in \Hom_{\MA}(A_2, A_3)$. Since $F:\MA \times \MB \rightarrow \MD$, we have that
				\begin{align*}
					F(\cdot, B_0)(f_{23} \circ_{\MA} f_{12})
					& = F(f_{23} \circ_{\MA} f_{12}, \id_{B_0}^{\MB}) \\
					& = F(f_{23} \circ_{\MA} f_{12}, \id_{B_0}^{\MB} \circ_{\MB} \id_{B_0}^{\MB}) \\
					& = F[(f_{23}, \id_{B_0}^{\MB}) \circ_{\MA \times \MB} (f_{12}, \id_{B_0}^{\MB})] \\
					& = F(f_{23}, \id_{B_0}^{\MB}) \circ_{\MD} F(f_{12}, \id_{B_0}^{\MB}) \\
					& = F(\cdot, B_0)(f_{23}) \circ_{\MD} F(\cdot, B_0)(f_{12}).
				\end{align*} 
				\item Let $A \in \Obj(\MA)$. Then 
				\begin{align*}
					F(\cdot, B_0)(\id_A^{\MA}) 
					& = F(\id_A^{\MA}, \id_{B_0}^{\MB}) \\
					& = F(\id_{(A, B_0)}^{\MA \times \MB}) \\
					& = \id_{F(A, B_0)}^{\MD} \\
					& = \id_{F(\cdot, B_0)(A)}^{\MD}.  
				\end{align*}
			\end{enumerate}
			Thus $F(\cdot, B_0):\MA \rightarrow \MD$ is a functor.
			\item Similar to previous part \tcr{ref prev part}.
		\end{enumerate}
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:products:0007}
		Let $\MA, \MB$ be categories, $A_0 \in \Obj(\MA)$ and $B_0 \in \Obj(\MB)$. We define the
		\begin{itemize}
			\item \tbf{embedding functor of $\MA$ into $\MA \times \MB$ at $B_0$}, denoted $\iota_{\MA}^{B_0}: \MA \rightarrow \MA \times \MB$, by 
			$\iota_{\MA}^{B_0} \defeq \id_{\MA} \times \id_{\MB}(\cdot, B_0)$
			\item \tbf{embedding functor of $\MB$ into $\MA \times \MB$ at $A_0$}, denoted $\iota_{\MB}^{A_0}: \MB \rightarrow \MA \times \MB$, by $\iota_{\MB}^{A_0} \defeq \id_{\MA} \times \id_{\MB}(A_0, \cdot)$.
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:products:0008}
		Let $\MA, \MB$ be categories. Then 
		\begin{enumerate}
			\item for each $B_0 \in \Obj(\MA)$, $\iota_{\MA}^{B_0}:\MA \rightarrow \MA \times \MB$ is a functor and 
			\begin{itemize}
				\item $\iota_{\MA}^{B_0}(A) \defeq (A, B_0), \quad A \in \Obj(\MA)$,
				\item $\iota_{\MA}^{B_0}(f) \defeq (f, \id_{B_0}^{\MB}), \quad f \in \Hom_{\MA}$,
			\end{itemize}
			\item for each $A_0 \in \Obj(\MB)$, $\iota_{\MB}^{A_0}:\MB \rightarrow \MA \times \MB$ is a functor and 
			\begin{itemize}
				\item $\iota_{\MB}^{A_0}(B) \defeq (A_0, B), \quad B \in \Obj(\MB)$,
				\item $\iota_{\MB}^{A_0}(g) \defeq (\id_{A_0}^{\MA}, g), \quad g \in \Hom_{\MB}$.
			\end{itemize}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $B_0 \in \Obj(\MB)$. \tcr{By prev exercises}, $\iota_{\MA}^{B_0}$ is a functor. By definition, we have that
			\begin{itemize}
				\item for each $A \in \Obj(\MA)$, 
				\begin{align*}
					\iota_{\MA}^{B_0}(A)
					& = \id_{\MA} \times \id_{\MB}(A, B_0) \\
					& = (\id_{\MA}(A), \id_{\MB}(B_0)) \\ 
					& = (A, B_0),
				\end{align*}
				\item for each $f \in \Hom_{\MA}$, 
				\begin{align*}
					\iota_{\MA}^{B_0}(f)
					& = \id_{\MA} \times \id_{\MB}(f, \id_{B_0}^{\MB}) \\
					& = (\id_{\MA}(f), \id_{\MB}(\id_{B_0}^{\MB})) \\
					& = (f, \id_{B_0}^{\MB}).
				\end{align*}
			\end{itemize} 
			\item Similar \tcr{to prev part (ref prev part)}
		\end{enumerate}
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:products:0009}
		Let $\MA, \MB, \MC$ be categories, $F,G :\MA \times \MB \rightarrow \MC$, $\al: F \Rightarrow G$, $A_0 \in \Obj(\MA)$ and $B_0 \in \Obj(\MB)$. We define the
		\begin{itemize}
			\item \tbf{slice transformation of $\al$ at $A_0$}, denoted $\al_{(A_0, \cdot)}: F(A_0, \cdot) \Rightarrow G(A_0, \cdot)$, by 
			$(\al_{(A_0, \cdot)})_B \defeq \al_{(A_0, B)}$
			\item \tbf{slice transformation of $\al$ at $B_0$}, denoted $\al_{(\cdot, B_0)}: F(\cdot, B_0) \Rightarrow G(\cdot, B_0)$, by 
			$(\al_{(\cdot, B_0)})_A \defeq \al_{(A, B_0)}$. 
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:products:0010}
		Let $\MA, \MB, \MC$ be categories, $F,G :\MA \times \MB \rightarrow \MC$ and $\al: F \Rightarrow G$. Then
		\begin{enumerate}
			\item for each $A_0 \in \Obj(\MA)$, $\al_{(A_0, \cdot)}: F(A_0, \cdot) \Rightarrow G(A_0, \cdot)$ is a natural transformation,
			\item for each $B_0 \in \Obj(\MB)$, $\al_{(\cdot, B_0)}: F(\cdot, B_0) \Rightarrow G(\cdot, B_0)$ is a natural transformation.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A_0 \in \Obj(\MA)$.
			\begin{itemize}
				\item By construction, for each $B \in \Obj(\MB)$, 
				\begin{align*}
					(\al_{(A_0, \cdot)})_B
					& = \al_{(A_0, B)} \\
					& \in \Hom_{\MC}(F(A_0, B), G(A_0, B)) \\
					& = \Hom_{\MC}(F(A_0, \cdot)(B), G(A_0, \cdot)(B)).
				\end{align*}
				\item Let $B_1, B_2 \in \Obj(\MB)$ and $g \in \Hom_{\MB}(B_1, B_2)$. Since $\al:F \Rightarrow G$, we have that for each $g \in \Hom_{\MB}(B_1, B_2)$, $G(\id_{A_0}^{\MA}, g) \circ_{\MC} \al_{(A_0, B_1)} = \al_{(A_0, B_2)} \circ_{\MC} F(\id_{A_0}^{\MA}, g)$, i.e. the following diagram commutes: 
				\[
				\begin{tikzcd}
					F(A_0, B_1)  \arrow[r, "\al_{(A_0, B_1)}"] \arrow[d, "{F(\id_{A_0}^{\MA}, g)}"'] & G(A_0, B_1) \arrow[d, "{G(\id_{A_0}^{\MA}, g)}"] \\
					F(A_0, B_2) \arrow[r, "\al_{(A_0, B_2)}"] &  G(A_0, B_2).
				\end{tikzcd}
				\]
				Therefore
				\begin{align*}
					G(A_0, \cdot)(g) \circ_{\MC} (\al_{(A_0, \cdot)})_{B_1}
					& = G(\id_{A_0}^{\MA}, g) \circ_{\MC} \al_{(A_0, B_1)} \\
					& = \al_{(A_0, B_2)}  \circ_{\MC} F(\id_{A_0}^{\MA}, g) \\
					& = (\al_{(A_0, \cdot)})_{B_2} \circ_{\MC} F(A_0, \cdot)(g),
				\end{align*}
				i.e. the following diagram commutes: 
				\[
				\begin{tikzcd}
					F(A_0, \cdot)(B_1)  \arrow[r, "{(\al_{(A_0, \cdot)})_{B_1}}"] \arrow[d, "{F(A_0, \cdot)(g)}"'] & G(A_0, \cdot)(B_1) \arrow[d, "{G(A_0, \cdot)(g)}"] \\
					F(A_0, \cdot)(B_2) \arrow[r, "{(\al_{(A_0, \cdot)})_{B_2}}"] &  G(A_0, \cdot)(B_2).
				\end{tikzcd}
				\]
				Since $B_1, B_2 \in \Obj(\MB)$ and $g \in \Hom_{\MB}(B_1, B_2)$ are arbitrary, we have that for each $B_1, B_2 \in \Obj(\MB)$, $G(A_0, \cdot)(g) \circ_{\MC} (\al_{(A_0, \cdot)})_{B_1} = (\al_{(A_0, \cdot)})_{B_2} \circ_{\MC} F(A_0, \cdot)(g)$.  
			\end{itemize}
			Thus $\al_{(A_0, \cdot)}: F(A_0, \cdot) \Rightarrow G(A_0, \cdot)$ is a natural transformation. Since $A_0 \in \Obj(\MA)$ is arbitrary, we have that for each $A_0 \in \Obj(\MA)$, $\al_{(A_0, \cdot)}: F(A_0, \cdot) \Rightarrow G(A_0, \cdot)$ is a natural transformation.
			\item \tcr{Similar to previous part (ref prev part)}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:products:0010.1}
		Let $\MA, \MB, \MC$ be categories, $F_1,F_2, F_3 :\MA \times \MB \rightarrow \MC$, $\al_{1,2}: F_1 \Rightarrow F_2$ and $\al_{2,3}: F_2 \Rightarrow F_3$. Then 
		\begin{enumerate}
			\item for each $A_0 \in \Obj(\MA)$, $(\al_{2,3} \circ \al_{1,2})_{(A_0, \cdot)} = (\al_{2,3})_{(A_0, \cdot)} \circ (\al_{1,2})_{(A_0, \cdot)}$.
			\item for each $B_0 \in \Obj(\MB)$, $(\al_{2,3} \circ \al_{1,2})_{(\cdot, B_0)} = (\al_{2,3})_{(\cdot, B_0)} \circ (\al_{1,2})_{(\cdot, B_0)}$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A_0 \in \Obj(\MA)$ and $B \in \Obj(\MB)$. Then 
			\begin{align*}
				[(\al_{2,3} \circ \al_{1,2})_{(A_0, \cdot)}]_B
				& = (\al_{2,3} \circ \al_{1,2})_{(A_0, B)} \\
				& = (\al_{2,3})_{(A_0, B)} \circ (\al_{1,2})_{(A_0, B)} \\
				& = [(\al_{2,3})_{(A_0, \cdot)}]_B \circ [(\al_{1,2})_{(A_0, \cdot)}]_B \\
				& = [(\al_{2,3})_{(A_0, \cdot)} \circ (\al_{1,2})_{(A_0, \cdot)}]_B.
			\end{align*}
			Since $B \in \Obj(\MB)$ is arbitrary, we have that for each $B \in \Obj(\MB)$, $[(\al_{2,3} \circ \al_{1,2})_{(A_0, \cdot)}]_B = [(\al_{2,3})_{(A_0, \cdot)} \circ (\al_{1,2})_{(A_0, \cdot)}]_B$. Thus $(\al_{2,3} \circ \al_{1,2})_{(A_0, \cdot)} = (\al_{2,3})_{(A_0, \cdot)} \circ (\al_{1,2})_{(A_0, \cdot)}$. Since $A_0 \in \Obj$ is arbitrary, we have that for each $A_0 \in \Obj(\MA)$, $(\al_{2,3} \circ \al_{1,2})_{(A_0, \cdot)} = (\al_{2,3})_{(A_0, \cdot)} \circ (\al_{1,2})_{(A_0, \cdot)}$.
			\item \tcr{Similar to prev part (ref prev part)}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:products:0010.2}
		Let $\MA, \MB, \MC$ be categories and $F \in \MA \times \MB \rightarrow \MC$. Then
		\begin{enumerate}
			\item for each $A_0 \in \Obj(\MA)$, $(\id_F)_{(A_0, \cdot)} = \id_{F(A_0, \cdot)}$,
			\item for each $B_0 \in \Obj(\MA)$, $(\id_F)_{(\cdot, B_0)} = \id_{F(\cdot, B_0)}$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A_0 \in \Obj(\MA)$. Then for each $B \in \Obj(\MB)$, 
			\begin{align*}
				[(\id_F)_{(A_0, \cdot)}]_B
				& = (\id_F)_{(A_0, B)} \\
				& = \id_{F(A_0, B)} \\
				& = \id_{F(A_0, \cdot)(B)} \\
				& = (\id_{F(A_0, \cdot)})_B.
			\end{align*}
			Hence $(\id_F)_{(A_0, \cdot)} = \id_{F(A_0, \cdot)}$. Since $A_0 \in \Obj(\MA)$ is arbitrary, we have that for each $A_0 \in \Obj(\MA)$, $(\id_F)_{(A_0, \cdot)} = \id_{F(A_0, \cdot)}$.
			\item \tcr{Similart to (ref) prev part}
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage

	\section{Functor Categories}
	
	\begin{defn} \ld{def:basics:contructs:func_cats:0001}
		Let $\MC, \MD \in \Obj(\Cat)$. We define the \tbf{evaluation functor from $\MC \times \MD^{\MC}$ to $\MD$}, denoted $\eval_{(\MC, \MD)}:\MC \times \MD^{\MC} \rightarrow \MD$, by 
		\begin{itemize}
			\item $\eval_{(\MC, \MD)}(A, F) \defeq F(A), \quad (A,F) \in \Obj(\MC \times \MD^{\MC})$
			\item $\eval_{(\MC, \MD)}(f, \al) \defeq G(f) \circ_{\MD} \al_A, \quad (f, \al) \in \Hom_{\MC \times \MD^{\MC}}$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0002}
		Let $\MC, \MD \in \Obj(\Cat)$. Then $\eval_{(\MC, \MD)}: \eval:\MC \times \MD^{\MC} \rightarrow \MD$ is a functor. 
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $(A, F), (B,G) \in \Obj(\MC \times \MD^{\MC})$ and $(f, \al) \in \Hom_{\MC \times \MD^{\MC}}((A, F), (B,G))$. Then $G(f) \in \Hom_{\MD}(G(A), G(B))$ and $\al_A \in \Hom_{\MD}(F(A), G(A))$. Hence
			\begin{align*}
				\eval_{(\MC, \MD)}(f, \al)
				& = G(f) \circ_{\MD} \al_A \\
				& \in \Hom_{\MD}(F(A), G(B)) \\
				& = \Hom_{\MD}(\eval_{(\MC, \MD)}(A, F), \eval_{(\MC, \MD)}(B, G)). 
			\end{align*}
			\item Let $(A, F), (B,G), (C, H) \in \Obj(\MC \times \MD^{\MC})$, $(f, \al) \in \Hom_{\MC \times \MD^{\MC}}((A, F), (B,G))$ and $(g, \be) \in \Hom_{\MC \times \MD^{\MC}}((B, G), (C,H))$. 
			Since $\be \in \Hom_{\MD^{\MC}}(G,H)$, we have that $H(f) \circ_{\MD} \be_A = \be_B \circ_{\MD} G(f)$, i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				G(A)  \arrow[r, "\be_A"] \arrow[d, "{G(f)}"'] & H(A) \arrow[d, "{H(f)}"] \\
				G(B)  \arrow[r, "\be_B"] & H(B).
			\end{tikzcd}
			\]
			\begin{align*}
				\eval_{(\MC, \MD)}((g, \be) \circ_{\MC \times \MD^{\MC}} (f, \al))
				& = \eval_{(\MC, \MD)}(g \circ_{\MC} f, \be \circ_{\MD^{\MC}} \al) \\
				& = H(g \circ_{\MC} f) \circ_{\MD} (\be \circ_{\MD^{\MC}} \al)_A \\
				& = H(g) \circ_{\MD} (H(f) \circ_{\MD} \be_A) \circ_{\MD} \al_A \\
				& = H(g) \circ_{\MD} (\be_B \circ_{\MD} G(f)) \circ_{\MD} \al_A \\
				& = (H(g) \circ_{\MD} \be_B) \circ_{\MD} (G(f) \circ_{\MD} \al_A) \\
				& = \eval_{(\MC, \MD)}(g, \be) \circ_{D} \eval_{(\MC, \MD)}(f, \al)).
			\end{align*}
			\item For each $(A, F) \in \Obj(\MC \times \MD^{\MC})$, we have that 
			\begin{align*}
				\eval_{(\MC, \MD)} (\id_{(A,F)}^{\MC \times \MD^{\MC}}) 
				& = \eval_{(\MC, \MD)} (\id_A^{\MC}, \id_F^{\MD^{\MC}}) \\ 
				& = \eval_{(\MC, \MD)} (\id_A^{\MC}, \id_F^{\MD^{\MC}}) \\ 
				& = F(\id_A^{\MC}) \circ_{\MD} (\id_F^{\MD^{\MC}})_A \\
				& = \id_{F(A)}^{\MD} \circ_{\MD} \id_{F(A)}^{\MD} \\
				& = \id_{F(A)}^{\MD} \\
				& = \id_{\eval_{(\MC, \MD)}(A,F)}^{\MD}
			\end{align*}
		\end{enumerate}
		Hence $\eval_{(\MC, \MD)}:\MC \times \MD^{\MC} \rightarrow \MD$ is a functor. 
	\end{proof}
	
	\begin{ex}
		\tcr{Find two functors $F,G: \Cat \times \Cat \rightarrow \Cat$ such that $\eval \mapsto \eval_{(\MC, \MD)}$ is a natural isomorphism $F \Rightarrow G$.}
	\end{ex}
	
	\begin{defn} \ld{def:basics:contructs:func_cats:0003}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$, $(F,G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$, $H,J \in \Obj(\MB_1^{\MA_1})$ and $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$. 
		\begin{itemize}
			\item For each $H \in \Obj(\MB_1^{\MA_1})$, we define the \tbf{internal Hom functor object induced by $F$ and $G$ at $H$}, denoted $G^F(H) \in \Obj(\MB_2^{\MA_2})$, by $G^F(H) \defeq G \circ_{\Cat} H \circ_{\Cat} F$
			\item \tbf{internal Hom functor natural transformation induced by $F$ and $G$ at $\al$}, denoted $G^F(\al): G^F(H) \Rightarrow G^F(J)$, by $G^F(\al)_A \defeq G(\al_{F(A)})$.
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0004}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$, $(F,G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$, $H,J \in \Obj(\MB_1^{\MA_1})$ and $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$. Then $G^F(\al):G^F(H) \Rightarrow G^F(J)$ is a natural transformation.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item Let $A \in \Obj(\MA_2)$. Since $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$, we have that $\al_{F(A} \in \Hom_{\MB_1}(H(F(A)), J(F(A)))$. Then
			\begin{align*}
				G^F(\al)_A
				& = G(\al_{F(A)}) \\
				& \in \Hom_{\MB_2}(G(H(F(A))), G(J(F(A)))) \\
				& = \Hom_{\MB_2}(G^F(H)(A)), G^F(J)(A)).
			\end{align*}
			Since $A \in \Obj(\MA_2)$ is arbitrary, we have that for each $A \in \Obj(\MA_2)$, $G^F(\al)_A \in \Hom_{\MB_2}(G^F(H)(A)), G^F(J)(A))$.
			\item Let $A_1, A_2 \in \Obj(\MA_2)$ and $f \in \Hom_{\MA_2}(A_1, A_2)$. Define $A'_1, A'_2 \in \Obj(\MA_1)$ and $f' \in \Hom_{\MA_1}(A'_1, A'_2)$ by $A'_k \defeq F(A_k)$ and $f' \defeq F(f)$. Since $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$, we have that
			\begin{align*}
				J(f') \circ_{\MB_1} \al_{A'_1}
				& = \al_{A'_2} \circ_{\MB_1} H(f'),
			\end{align*}
			i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				H(A'_1)  \arrow[r, "\al_{A'_1}"] \arrow[d, "{H(f')}"'] & J(A'_1) \arrow[d, "{J(f')}"] \\
				H(A'_2) \arrow[r, "\al_{A'_2}"] &  J(A'_2).
			\end{tikzcd}
			\]
			Therefore,
			\begin{align*}
				G^F(J)(f) \circ_{\MB_2} G^F(\al)_{A_1}
				& = [G \circ_{\Cat} J \circ_{\Cat} F](f) \circ_{\MB_2} G(\al_{F(A_1)}) \\
				& = G(J(F(f))) \circ_{\MB_2} G(\al_{F(A_1)}) \\
				& = G(J(f')) \circ_{\MB_1} G(\al_{A'_2}) \\
				& = G(J(f') \circ_{\MB_1} \al_{A'_1}) \\
				& = G(\al_{A'_2} \circ_{\MB_1} H(f')) \\
				& = G(\al_{A'_2}) \circ_{\MB_2} G(H(f')) \\
				& = G(\al_{F(A_2)}) \circ_{\MB_2} G(H(F(f))) \\
				& = G(\al_{F(A_2)}) \circ_{\MB_2} [G \circ_{\Cat} H \circ_{\Cat} F](f) \\
				& = G^F(\al)_{A_2} \circ_{\MB_2} G^F(H)(f),
			\end{align*}
			i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				G^F(H)(A_1)  \arrow[r, "(G^F_\al)_{A_1}"] \arrow[d, "{G^F(H)(f)}"'] & G^F(J)(A_1) \arrow[d, "{G^F(J)(f)}"] \\
				G^F(H)(A_2) \arrow[r, "(G^F_\al)_{A_2}"] &  G^F(J)(A_2).
			\end{tikzcd}
			\]
			Since $A_1, A_2 \in \Obj(\MA_2)$ and $f \in \Hom_{\MA_2}(A_1, A_2)$ are arbitrary, we have that for each $A_1, A_2 \in \Obj(\MA_2)$ and $f \in \Hom_{\MA_2}(A_1, A_2)$, $G^F(J)(f) \circ_{\MB_2} G^F(\al)_{A_1} = G^F(\al)_{A_2} \circ_{\MB_2} G^F(H)(f)$. 
		\end{itemize}
		Thus $G^F(\al):G^F(H) \Rightarrow G^F(J)$ is a natural transformation.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0005}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$, $(F,G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$, $H,J, K \in \Obj(\MB_1^{\MA_1})$, $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$ and $\be \in \Hom_{\MB_1^{\MA_1}}(J,K)$. Then $G^F(\be \circ_{\MB_1^{\MA_1}} \al) = G^F(\be) \circ_{\MB_2^{\MA_2}} G^F(\al)$.
	\end{ex}
	
	\begin{proof}
		For each $A \in \Obj(\MA_2)$,
		\begin{align*}
			G^F(\be \circ_{\MB_1^{\MA_1}} \al)_A
			& = G([\be \circ_{\MB_1^{\MA_1}} \al]_{F(A)}) \\
			& = G(\be_{F(A)} \circ_{\MB_1} \al_{F(A)}) \\
			& = G(\be_{F(A)}) \circ_{\MB_2} G(\al_{F(A)}) \\
			& = G^F(\be)_A \circ_{\MB_2} G^F(\al)_A \\
			& = (G^F(\be) \circ_{\MB_2^{\MA_2}} G^F(\al))_A.
		\end{align*}
		Hence $G^F(\be \circ_{\MB_1^{\MA_1}} \al) = G^F(\be) \circ_{\MB_2^{\MA_2}} G^F(\al)$.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0006}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$, $(F,G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$, $H \in \Obj(\MB_1^{\MA_1})$, Then $G^F(\id_H^{\MB_1^{\MA_1}}) = \id_{G^F(H)}^{\MB_2^{\MA_2}}$.
	\end{ex}
	
	\begin{proof}
		For each $A \in \MA_2$,
		\begin{align*}
			G^F(\id_H^{\MB_1^{\MA_1}})_A
			& = G((\id_H^{\MB_1^{\MA_1}})_{F(A)}) \\
			& = G(\id_{H(F(A))}^{\MB_1}) \\
			& = \id_{G(H(F(A)))}^{\MB_1} \\
			& = \id_{G \circ_{\Cat} H \circ_{\Cat} F(A)}^{\MB_1} \\
			& = \id_{G^F(H)(A)}^{\MB_1} \\
			& = (\id_{G^F(H)}^{\MB_2^{\MA_2}})_A.
		\end{align*}
		Hence $G^F(\id_H^{\MB_1^{\MA_1}}) = \id_{G^F(H)}^{\MB_2^{\MA_2}}$.
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:func_cats:0007}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$ and $(F,G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$. We define the \tbf{internal Hom functor of $\Cat$ at $(F,G)$}, denoted $[F,G]_{\Cat}:\MB_1^{\MA_1} \rightarrow \MB_2^{\MA_2}$ or $G^F:\MB_1^{\MA_1} \rightarrow \MB_2^{\MA_2}$, by 
		\begin{itemize}
			\item $[F,G]_{\Cat}(H) \defeq G^F(H), \quad H \in \Obj(\MB_1^{\MA_1})$ 
			\item $[F,G]_{\Cat}(\al) \defeq G^F(\al), \quad \al \in \Hom_{\MB_1^{\MA_1}}$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0008}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$ and $(F,G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$. Then $G^F:\MB_1^{\MA_1} \rightarrow \MB_2^{\MA_2}$ is a functor. 
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item \rex{ex:basics:contructs:func_cats:0004} implies that for each $H, J \in \Obj(\MB_1^{\MA_1})$ and $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$, $G^F(\al) \in \Hom_{\MB_2^{\MA_2}}(G^F(H), G^F(J))$. 
			\item \rex{ex:basics:contructs:func_cats:0005} implies that for each $H,J, K \in \Obj(\MB_1^{\MA_1})$, $\al \in \Hom_{\MB_1^{\MA_1}}(H,J)$ and $\be \in \Hom_{\MB_1^{\MA_1}}(J,K)$, $G^F(\be \circ_{\MB_1^{\MA_1}} \al) = G^F(\be) \circ_{\MB_2^{\MA_2}} G^F(\al)$.
			\item \rex{ex:basics:contructs:func_cats:0006} implies that for each $A \in \Obj(\MA_2)$, $G^F(\id_H^{\MB_1^{\MA_1}}) = \id_{G^F(H)}^{\MB_2^{\MA_2}}$.
		\end{enumerate}
		Hence $G^F:\MB_1^{\MA_1} \rightarrow \MB_2^{\MA_2}$ is a functor.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0009}
		Let $(\MA_1, \MB_1), (\MA_2, \MB_2), (\MA_3, \MB_3) \in \Obj(\op{\Cat} \times \Cat)$, $(F_{1,2}, G_{1,2}) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$ and  $(F_{2,3}, G_{2,3}) \in \Hom_{\op{\Cat} \times \Cat}((\MA_2, \MB_2), (\MA_3, \MB_3))$. Then 
		$$(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}} = G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}}.$$
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item For each $H \in \Obj(\MB_1^{\MA_1})$, 
			\begin{align*}
				(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}}(H)
				& = G_{2,3} \circ_{\Cat} G_{1,2} \circ_{\Cat} H \circ_{\Cat} (F_{2,3} \circ_{\op{\Cat}} F_{1,2}) \\
				& = G_{2,3} \circ_{\Cat} G_{1,2} \circ_{\Cat} H \circ_{\Cat} (F_{1,2} \circ_{\Cat} F_{2,3}) \\
				& = G_{2,3} \circ_{\Cat} (G_{1,2} \circ_{\Cat} H \circ_{\Cat} F_{1,2}) \circ_{\Cat} F_{2,3} \\
				& = G_{2,3} \circ_{\Cat} (G_{1,2}^{F_{1,2}}(H)) \circ_{\Cat} F_{2,3} \\
				& = G_{2,3}^{F_{2,3}} (G_{1,2}^{F_{1,2}}(H)) \\
				& = G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}}(H).
			\end{align*}
			\item Let $H,K \in \Obj(\MB_1^{\MA_1})$ and $\al \in \Hom_{\MB_1^{\MA_1}}(H, K)$. Then for each $A \in \Obj(\MA_3)$,
			\begin{align*}
				[(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}}(\al)]_A
				& = [(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{1,2} \circ_{\Cat} F_{2,3}}(\al)]_A \\
				& = G_{2,3} \circ_{\Cat} G_{1,2}(\al_{F_{1,2} \circ_{\Cat} F_{2,3}(A)}) \\
				& = G_{2,3}(G_{1,2}(\al_{F_{1,2}(F_{2,3}(A))})) \\
				& = G_{2,3}(G_{1,2}^{F_{1,2}}(\al)_{F_{2,3}(A)}) \\
				& = [G_{2,3}^{F_{2,3}}(G_{1,2}^{F_{1,2}}(\al))]_A \\
				& = [G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}} (\al)]_A
			\end{align*}
			Thus $(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}}(\al) = G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}} (\al)$. Since $H,K \in \Obj(\MB_1^{\MA_1})$ and $\al \in \Hom_{\MB_1^{\MA_1}}(H, K)$ are arbitrary, we have that for each $H,K \in \Obj(\MB_1^{\MA_1})$ and $\al \in \Hom_{\MB_1^{\MA_1}}(H, K)$, $(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}}(\al) = G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}} (\al)$.
		\end{itemize}
		Therefore $(G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}} = G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}}$.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0010}
		Let $\MA, \MB \in \Obj(\Cat)$. Then
		$$(\id_{\MB}^{\Cat})^{\id_{\MA}^{\Cat}} = \id_{\MB^{\MA}}^{\Cat}.$$
	\end{ex}
	
	\begin{proof}
		Let $\MA, \MB \in \Obj(\Cat)$. 
		\begin{itemize}
			\item For each $H \in \Obj(\MB^{\MA})$, 
			\begin{align*}
				(\id_{\MB}^{\Cat})^{\id_{\MA}^{\Cat}}(H) 
				& = \id_{\MB}^{\Cat} \circ_{\Cat} H \circ_{\Cat} \id_{\MA}^{\Cat} \\
				& = H \\
				& = \id_{\MB^{\MA}}^{\Cat}(H).
			\end{align*}
			\item Let $H,K \in \Obj(\MB^{\MA})$ and $\al \in \Hom_{\MB^{\MA}}(H, K)$. Then for each $A \in \Obj(\MA)$,
			\begin{align*}
				[(\id_{\MB}^{\Cat})^{\id_{\MA}^{\Cat}}(\al)]_A
				& = \id_{\MB}^{\Cat}(\al_{\id_{\MA}^{\Cat}(A)}) \\
				& = \id_{\MB}^{\Cat}(\al_A) \\
				& = \al_A \\
				& = [\id_{\MB^{\MA}}^{\Cat}(\al)]_A
			\end{align*}
			Hence $(\id_{\MB}^{\Cat})^{\id_{\MA}^{\Cat}}(\al) = \id_{\MB^{\MA}}^{\Cat}(\al)$.
		\end{itemize}
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:func_cats:0011}
		We define the \tbf{internal Hom functor of $\Cat$}, denoted $[\cdot, \cdot]_{\Cat}: \op{\Cat} \times \Cat \rightarrow \Cat$, by 
		\begin{itemize}
			\item $[\MC, \MD]_{\Cat} \defeq \MD^{\MC}, \quad (\MC, \MD) \in \Obj(\op{\Cat} \times \Cat)$,
			\item $[F, G]_{\Cat} \defeq G^F, \quad (F, G) \in \Hom_{\op{\Cat} \times \Cat}$.
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:func_cats:0012}
		We have that $[\cdot, \cdot]_{\Cat}: \op{\Cat} \times \Cat \rightarrow \Cat$ is a functor.
	\end{ex}
	
	\begin{note}
		When the context is clear, we may write $[\cdot, \cdot]$ in place of $[\cdot, \cdot]_{\Cat}$.
	\end{note}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $(\MA_1, \MB_1), (\MA_2, \MB_2) \in \Obj(\op{\Cat} \times \Cat)$ $(F, G) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$. \rex{ex:basics:contructs:func_cats:0008} implies that 
			\begin{align*}
				[\cdot, \cdot](F,G)
				& = G^F \\
				& \in \Hom_{\Cat}(\MB_1^{\MA_1}, \MB_2^{\MA_2}) \\
				& = \Hom_{\Cat}([\MA_1, \MB_1], [\MA_2, \MB_2]) \\
				& = \Hom_{\Cat}([\cdot, \cdot](\MA_1, \MB_1), [\cdot, \cdot](\MA_2, \MB_2)).
			\end{align*}
			\item $(\MA_1, \MB_1), (\MA_2, \MB_2), (\MA_2, \MB_3) \in \Obj(\op{\Cat} \times \Cat)$ $(F_{1,2}, G_{1,2}) \in \Hom_{\op{\Cat} \times \Cat}((\MA_1, \MB_1), (\MA_2, \MB_2))$ and  $(F_{2,3}, G_{2,3}) \in \Hom_{\op{\Cat} \times \Cat}((\MA_2, \MB_2), (\MA_3, \MB_3))$. \rex{ex:basics:contructs:func_cats:0009} then implies that
			\begin{align*}
				[\cdot, \cdot]((F_{2,3}, G_{2,3}) \circ_{\op{\Cat} \times \Cat} (F_{1,2}, G_{1,2})) 
				& = [\cdot, \cdot](F_{2,3} \circ_{\op{\Cat}} F_{1,2}, G_{2,3} \circ_{\Cat} G_{1,2}) \\
				& = (G_{2,3} \circ_{\Cat} G_{1,2})^{F_{2,3} \circ_{\op{\Cat}} F_{1,2}} \\
				& = G_{2,3}^{F_{2,3}} \circ_{\Cat} G_{1,2}^{F_{1,2}} \\
				& = [\cdot, \cdot](F_{2,3}, G_{2,3}) \circ_{\Cat} [\cdot, \cdot](F_{1,2}, G_{1,2}).
			\end{align*}
			\item \rex{ex:basics:contructs:func_cats:0010} implies that for each $\MA, \MB \in \Obj(\Cat)$,
			\begin{align*}
				[\cdot, \cdot](\id_{(\MA, \MB)}^{\op{\Cat} \times \Cat})
				& = [\cdot, \cdot](\id_{\MA}^{\Cat}, \id_{\MB}^{\Cat}) \\
				& = (\id_{\MB}^{\Cat})^{\id_{\MA}^{\Cat}} \\
				& = \id_{\MB^{\MA}}^{\Cat} \\
				& = \id_{[\cdot, \cdot](\MA, \MB)}^{\Cat}.
			\end{align*}
		\end{enumerate}
		Hence $[\cdot, \cdot]: \op{\Cat} \times \Cat \rightarrow \Cat$ is a functor.
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Opposition}
	
	\tcr{relabel and organize}
	
	\begin{defn} \ld{def:basics:functors:intro:0006}
		Let $\MC, \MD$ be a categories and $F:\MC \rightarrow \MD$. We define the \tbf{opposite of $F$}, denoted $\op{F}: \op{\MC} \rightarrow \op{\MD}$, by
		\begin{itemize}
			\item $\op{F}(A) \defeq F(A), \quad A \in \Obj(\op{\MC})$
			\item $\op{F}(f) \defeq F(f), \quad f \in \Hom_{\op{\MC}}$
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:functors:intro:0007}
		Let $\MC, \MD$ be a categories and $F:\MC \rightarrow \MD$. Then $\op{F}: \op{\MC} \rightarrow \op{\MD}$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item For each $A,B \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(A,B)$,
			\begin{align*}
				\op{F}(f)
				& = f \\
				& \in \Hom_{\op{\MC}}(A,B) \\
				& = \Hom_{\op{\MC}}(\op{F}(A), \op{F}(B)).
			\end{align*}
			\item For each $A,B,C \in \Obj(\op{\MC})$, $f \in \Hom_{\op{\MC}}(A,B)$ and $g \in \Hom_{\op{\MC}}(B,C)$,
			\begin{align*}
				\op{F}(g \circ_{\op{\MC}} f) 
				& = g \circ_{\op{\MC}} f \\
				& = \op{F}(g) \circ_{\op{\MC}} \op{F}(f). 
			\end{align*}
			\item For each $A \in \Obj(\op{\MC})$, 
			\begin{align*}
				\op{F}(\id_A^{\op{\MC}})
				& = \id_A^{\op{\MC}} \\
				& = \id_{\op{F}(A)}^{\op{\MC}}.
			\end{align*}
		\end{enumerate}
		Hence $\op{F}: \op{\MC} \rightarrow \op{\MD}$ is a functor.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:functors:small_cat:0011}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$, $F \in \Hom_{\Cat}(\MA, \MB)$ and $G \in \Hom_{\Cat}(\MB, \MC)$. Then $\op{G \circ_{\Cat} F} = \op{G} \circ_{\Cat} \op{F}$.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item For each $A \in \Obj(\op{A})$, 
			\begin{align*}
				\op{G \circ_{\Cat} F}(A)
				& = G \circ_{\Cat} F(A) \\
				& = G(F(A)) \\
				& = \op{G}(\op{F}(A)) \\
				& = \op{G} \circ_{\Cat} \op{F}(A).
			\end{align*}
			\item For each $A,B,C \in \Obj(\op{\MA})$ and $f \in \Hom_{\op{\MA}}(A,B)$,
			\begin{align*}
				\op{G \circ_{\Cat} F}(f) 
				& = G \circ_{\Cat} F(f) \\
				& = G(F(f)) \\
				& = \op{G}(\op{F}(f)) \\
				& = \op{G} \circ_{\Cat} \op{F}(f).
			\end{align*}
		\end{itemize}
		Thus $\op{G \circ_{\Cat} F} = \op{G} \circ_{\Cat} \op{F}$.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:functors:small_cat:0012}
		Let $\MC \in \Obj(\Cat)$. Then $\op{\id_{\MC}^{\Cat}} = \id_{\op{\MC}}^{\Cat}$.
	\end{ex}
	
	\begin{proof}
		\begin{itemize}
			\item For each $A \in \Obj(\op{\MC})$,
			\begin{align*}
				\op{\id_{\MC}^{\Cat}}(A)
				& = \id_{\MC}^{\Cat}(A) \\
				& = A \\
				& = \id_{\op{\MC}}^{\Cat}(A).
			\end{align*}
			\item For each $A,B \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(A,B)$,
			\begin{align*}
				\op{\id_{\MC}^{\Cat}}(f)
				& = \id_{\MC}^{\Cat}(f) \\
				& = f \\
				& = \id_{\op{\MC}}^{\Cat}(f).
			\end{align*}
		\end{itemize}
		Thus $\op{\id_{\MC}^{\Cat}} = \id_{\op{\MC}}^{\Cat}$.
	\end{proof}
	
	\begin{defn} \ld{def:basics:functors:small_cat:0013}
		We define the \tbf{opposite functor on $\Cat$}, denoted $\opp^{\Cat}: \Cat \rightarrow \Cat$, by 
		\begin{itemize}
			\item $\opp^{\Cat}(\MC) \defeq \op{\MC}$
			\item $\opp^{\Cat}(F) \defeq \op{F}$
		\end{itemize}
	\end{defn}
	
	\begin{note}
		When the context is clear, we may write $\opp$ in place of $\opp^{\Cat}$.
	\end{note}
	
	\begin{ex} \lex{ex:basics:functors:small_cat:0014}
		We have that $\opp^{\Cat}: \Cat \rightarrow \Cat$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item \rex{ex:basics:functors:intro:0007} implies that for each $\MC, \MD \in \Obj(\Cat)$ and $F \in \Hom_{\Cat}(\MC, \MD)$,
			\begin{align*}
				\opp(F)
				& = \op{F} \\
				& \in \Hom_{\Cat}(\op{\MC}, \op{\MD}) \\
				& = \Hom_{\Cat}(\opp(\MC), \opp(\MD)).
			\end{align*}
			\item \rex{ex:basics:functors:small_cat:0011} implies that for each $\MA, \MB, \MC \in \Obj(\Cat)$, $F \in \Hom_{\Cat}(\MA, \MB)$ and $G \in \Hom_{\Cat}(\MB, \MC)$, 
			\begin{align*}
				\opp(G \circ_{\Cat} F)
				& = \op{G \circ_{\Cat} F} \\
				& = \op{G} \circ_{\Cat} \op{F} \\
				& = \opp((G) \circ_{\Cat} \opp(F).
			\end{align*}
			\item \rex{ex:basics:functors:small_cat:0012} implies that for each $\MC \in \Obj(\Cat)$, 
			\begin{align*}
				\opp(\id_{\MC}^{\Cat})
				& = \op{\id_{\MC}^{\Cat}} 
				& = \id_{\op{\MC}}^{\Cat} \\
				& = \id_{\opp(\MC)}^{\Cat}.
			\end{align*}
		\end{enumerate}
		Thus $\opp: \Cat \rightarrow \Cat$ is a functor.
	\end{proof}
	
	\begin{defn} \ld{def:basics:nat_trans:cat_funct:0012}
		Let $\MC, \MD$ be categories, $F,G:\MC \rightarrow \MD$ functors and $\al:F \Rightarrow G$ a natural transformation. We define the \tbf{opposite of $\al$}, denoted $\op{\al}: \op{G} \Rightarrow \op{F}$, by 
		$$\op{\al}_A \defeq \al_A, \quad A \in \Obj(\op{\MC})$$
	\end{defn}
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0013}
		Let $\MC, \MD$ be categories, $F,G:\MC \rightarrow \MD$ functors and $\al:F \Rightarrow G$ a natural transformation. Then $\op{\al}: \op{G} \Rightarrow \op{F}$ is a natural transformation.
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item Let $A \in \Obj(\op{\MC})$. Then $A \in \Obj(\MC)$ and
			\begin{align*}
				\op{\al}_A
				& = \al_A \\
				& \in \Hom_{\MD}(F(A), G(A)) \\
				& = \Hom_{\op{\MD}}(G(A), F(A)) \\
				& = \Hom_{\op{\MD}}(\op{G}(A), \op{F}(A)).
			\end{align*}
			Since $A \in \Obj(\op{\MC})$ is arbitrary, we have that for each $A \in \Obj(\op{\MC})$, $\op{\al}_A \in \Hom_{\op{\MD}}(\op{G}(A), \op{F}(A))$.
			\item Let $A, B \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(A, B)$. Then $A, B \in \Obj(\MC)$ and $f \in \Hom_{\MC}(B, A)$. Since $\al:F \Rightarrow G$ is a natural transformation, $G(f) \circ_{\MD} \al_B = \al_A \circ_{\MD} F(f)$, i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				F(B)  \arrow[r, "\al_B"]  \arrow[d, "F(f)"']  & G(B)   \arrow[d, "G(f)"]\\
				F(A) \arrow[r, "\al_A"'] &  G(A).
			\end{tikzcd}
			\]
			Therefore
			\begin{align*}
				\op{F}(f) \circ_{\op{\MD}} \op{\al}_A
				& = F(f) \circ_{\op{\MD}} \al_A \\
				& = \al_A \circ_{\MD} F(f) \\
				& = G(f) \circ_{\MD} \al_B \\
				& = \al_B \circ_{\op{\MD}} G(f) \\
				& = \op{\al}_B \circ_{\op{\MD}} \op{G}(f),
			\end{align*}
			i.e. the following diagram commutes:
			\[ 
			\begin{tikzcd}
				\op{G}(A)  \arrow[r, " \op{\al}_A "]  \arrow[d, "\op{G}(f)"']  & \op{F}(A)   \arrow[d, "\op{F}(f)"] \\
				\op{G}(B) \arrow[r, "\op{\al}_B"'] &  \op{F}(B).
			\end{tikzcd}
			\]
			Since $A, B \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(A, B)$ are arbitrary, we have that for each $A, B \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(A, B)$, $\op{F}(f) \circ_{\op{\MD}} \op{\al}_A = \op{\al}_B \circ_{\op{\MD}} \op{G}(f)$. 
		\end{itemize}
		Thus $\op{\al}: \op{G} \Rightarrow \op{F}$ is a natural transformation.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0014}
		Let $\MC, \MD \in \Obj(\Cat)$, $F,G,H \in \Obj(\MD^{\MC})$, $\al \in \Hom_{\MD^{\MC}}(F,G)$ and $\be \in \Hom_{\MD^{\MC}}(G,H)$. Then $\op{(\be \circ_{\MD^{\MC}} \al)} = \op{\al} \circ_{(\op{\MD})^{\op{\MC}}} \op{\be}$.
	\end{ex}
	
	\begin{proof}
		For each $A \in \Obj(\op{\MC})$,
		\begin{align*}
			\op{(\be \circ_{\MD^{\MC}} \al)}_A
			& = (\be \circ_{\MD^{\MC}} \al)_A \\
			& = \be_A \circ_{\MD} \al_A \\
			& = \al_A \circ_{\op{\MD}} \be_A \\
			& = \op{\al}_A \circ_{\op{\MD}} \op{\be}_A \\
			& = (\op{\al} \circ_{(\op{\MD})^{\op{\MC}}} \op{\be})_A.
		\end{align*}
		Thus $\op{(\be \circ_{\MD^{\MC}} \al)} = \op{\al} \circ_{(\op{\MD})^{\op{\MC}}} \op{\be}$.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:nat_trans:cat_funct:0015}
		Let $\MC, \MD \in \Obj(\Cat)$ and $F \in \Obj(\MD^{\MC})$. Then $\op{(\id_F^{\MD^{\MC}})} = \id_{\op{F}}^{(\op{\MD})^{\op{\MC}}}$. 
	\end{ex}
	
	\begin{proof}
		For each $A \in \Obj(\op{\MC})$, 
		\begin{align*}
			(\op{\id_F^{\MD^{\MC}}})_A
			& = (\id_F^{\MD^{\MC}})_A \\
			& = \id_{F(A)}^{\MD} \\
			& = \id_{F(A)}^{\op{\MD}} \\
			& = \id_{\op{F}(A)}^{\op{\MD}} \\
			& = (\id_{\op{F}}^{(\op{\MD})^{\op{\MC}}})_A.
		\end{align*}
		Thus $\op{(\id_F^{\MD^{\MC}})} = \id_{\op{F}}^{(\op{\MD})^{\op{\MC}}}$.
	\end{proof}
	
	\begin{defn}
		Let $\MC, \MD \in \Obj(\Cat)$. We define the \tbf{opposite functor on $\MD^{\MC}$}, denoted $\opp_{(\MC, \MD)}: \MD^{\MC} \rightarrow \op{[(\op{\MD})^{{\op{\MC}}}]}$, by 
		\begin{itemize}
			\item $\opp_{(\MC, \MD)}(F) \defeq \op{F}$
			\item $\opp_{(\MC, \MD)}(\al) \defeq \op{\al}$
		\end{itemize}
	\end{defn}
	
	\begin{ex}
		Let $\MC, \MD \in \Obj(\Cat)$. Then $\opp_{(\MC, \MD)}: \MD^{\MC} \rightarrow \op{[(\op{\MD})^{{\op{\MC}}}]}$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $F,G \in \Obj(\MD^{\MC})$ and $\al \in \Hom_{\MD^{\MC}}(F,G)$. \rex{ex:basics:functors:intro:0007} implies that 
			\begin{align*}
				\opp_{(\MC, \MD)}(F), \opp_{(\MC, \MD)}(G) 
				& \in \Obj((\op{\MD})^{\op{\MC}}) \\
				& = \Obj(\op{[(\op{\MD})^{\op{\MC}}]})
			\end{align*}
			and \rex{ex:basics:nat_trans:cat_funct:0013} implies that 
			\begin{align*}
				\opp_{(\MC, \MD)}(\al)
				& \in \Hom_{(\op{\MD})^{\op{\MC}}}(\op{G}, \op{F}) \\
				& = \Hom_{\op{[(\op{\MD})^{\op{\MC}}]}}(\op{F}, \op{G}) \\
				& = \Hom_{\op{[(\op{\MD})^{\op{\MC}}]}}(\opp_{(\MC, \MD)}(F), \opp_{(\MC, \MD)}(G)).
			\end{align*}
			Since $F,G \in \Obj(\MD^{\MC})$ and $\al \in \Hom_{\MD^{\MC}}(F,G)$ are arbitrary, we have that for each $F,G \in \Obj(\MD^{\MC})$ and $\al \in \Hom_{\MD^{\MC}}(F,G)$, $\opp_{(\MC, \MD)}(\al) \in \Hom_{\op{[(\op{\MD})^{\op{\MC}}]}}(\opp_{(\MC, \MD)}(F), \opp_{(\MC, \MD)}(G))$.
			\item Let $F,G,H \in \Obj(\MD^{\MC})$, $\al \in \Hom_{\MD^{\MC}}(F,G)$ and $\be \in \Hom_{\MD^{\MC}}(G,H)$. \rex{ex:basics:nat_trans:cat_funct:0014} implies that 
			\begin{align*}
				\opp_{(\MC, \MD)}(\be \circ_{\MD^{\MC}} \al)
				& = \op{\be \circ_{\MD^{\MC}} \al} \\
				& = \op{\al} \circ_{(\op{\MD})^{\op{\MC}}} \op{\be} \\
				& = \op{\be} \circ_{\op{[(\op{\MD})^{\op{\MC}}]}} \op{\al} \\
				& = \opp_{(\MC, \MD)}(\be) \circ_{\op{[(\op{\MD})^{\op{\MC}}]}} \opp_{(\MC, \MD)}(\al).
			\end{align*}
			\item \rex{ex:basics:nat_trans:cat_funct:0015} implies that for each $F \in \Obj(\MD^{\MC})$, 
			\begin{align*}
				\opp_{(\MC, \MD)}(\id_F^{\MD^{\MC}}) 
				& = \op{(\id_F^{\MD^{\MC}})} \\
				& = \id_{\op{F}}^{(\op{\MD})^{\op{\MC}}} \\
				& = \id_{\opp_{(\MC, \MD)}(F)}^{(\op{\MD})^{\op{\MC}}}. 
			\end{align*}
		\end{enumerate}
		Thus $\opp_{(\MC, \MD)}: \MD^{\MC} \rightarrow \op{[(\op{\MD})^{{\op{\MC}}}]}$ is a functor.
	\end{proof}
	
	\begin{defn}
		We define $\opp: [\cdot, \cdot]_{\Cat} \Rightarrow \opp^{\Cat} \circ_{\Cat} [\cdot, \cdot] \circ (\opp^{\Cat} , \opp^{\Cat})$ by 
		$\opp_{(\MC, \MD)} \defeq \opp_{(\MC, \MD)}$
		\tcr{rename stuff and reorganize the opposite stuff}
	\end{defn}
	
	\begin{ex}
		\o
	\end{ex}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\section{Currying}
	
	\begin{defn}  \ld{def:basics:contructs:currying:0001}
		Let $\MA, \MB, \MC$ be categories, $F :\MA \times \MB \rightarrow \MC$, $A_1, A_2 \in \Obj(\MA)$, $B_1, B_2 \in \Obj(\MB)$, $f \in \Hom_{\MA}(A_1, A_2)$ and $g \in \Hom_{\MB}(B_1, B_2)$. We define the 
		\begin{itemize}
			\item \tbf{natural transformation from $F(A_1, \cdot)$ to $F(A_2, \cdot)$ induced by $f$}, denoted $\al(F)^f:F(A_1, \cdot) \Rightarrow F(A_2, \cdot)$, by $\al(F)^f_B \defeq F(f, \id_B^{\MB})$,
			\item \tbf{natural transformation from $F(\cdot, B_1)$ to $F(\cdot, B_2)$ induced by $g$}, denoted $\be(F)^g:F(\cdot, B_1) \Rightarrow F(\cdot, B_2)$, by $\be(F)^g_A \defeq F(\id_A^{\MA}, g)$,
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0002}
		Let $\MA, \MB, \MC$ be categories and $F :\MA \times \MB \rightarrow \MC$. Then
		\begin{enumerate}
			\item for each $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$, $\al(F)^f:F(A_1, \cdot) \Rightarrow F(A_2, \cdot)$ is a natural transformation,
			\item for each $B_1, B_2 \in \Obj(\MB)$ and $g_0 \in \Hom_{\MB}(B_1, B_2)$, $\be(F)^g:F(\cdot, B_1) \Rightarrow F(\cdot, B_2)$ is a natural transformation.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A_1, A_2 \in \Obj(\MA)$.
			\begin{itemize}
				\item Let $B \in \Obj(\MB)$. Then $(f, \id_B^{\MB}) \in \Hom_{\MA \times \MB}((A_1, B), (A_2, B))$. Therefore
				\begin{align*}
					\al(F)^f_B
					& = F(f, \id_B^{\MB}) \\
					& \in \Hom_{\MA \times \MB}(F(A_1, B), F(A_2, B)) \\
					& = \Hom_{\MA \times \MB}(F(A_1, \cdot)(B), F(A_2, \cdot)(B)).
				\end{align*}
				Since $B \in \Obj(\MB)$ is arbitrary, we have that for each $B \in \Obj(\MB)$, $\al(F)^f_B \in \Hom_{\MA \times \MB}(F(A_1, \cdot)(B), F(A_2, \cdot)(B))$.
				\item Let $B_1, B_2 \in \Obj(\MB)$, $f \in \Hom_{\MA}(A_1, A_2)$ and $g \in \Hom_{\MB}(B_1, B_2)$. Then 
				\begin{align*}
					F(A_2, \cdot)(g) \circ_{\MC} \al(F)^f_{B_1} 
					& = F(\id_{A_2}^{\MA}, g) \circ_{\MC} F(f, \id_{B_1}^{\MB}) \\
					& = F((\id_{A_2}^{\MA}, g) \circ_{\MA \times \MB} (f, \id_{B_1}^{\MB})) \\
					& = F(\id_{A_2}^{\MA} \circ_{\MA} f, g \circ_{\MB} \id_{B_1}^{\MB}) \\
					& = F(f, g) \\
					& = F(f \circ_{\MA} \circ_{\MA} \id_{A_1}^{\MA}, \id_{B_2}^{\MB} \circ_{\MB} g) \\
					& = F((f, \id_{B_2}^{\MB}) \circ_{\MA \times \MB} (\id_{A_1}^{\MA}, g)) \\
					& = F(f, \id_{B_2}^{\MB}) \circ_{\MC} F(\id_{A_1}^{\MA}, g) \\
					& = \al(F)^f_{B_2} \circ_{\MC} F(A_1, \cdot)(g),
				\end{align*} 
				i.e. the following diagram commutes:
				\[
				\begin{tikzcd}
					F(A_1, \cdot)(B_1)  \arrow[r, "{\al(F)^f_{B_1}}"] \arrow[d, "{F(A_1, \cdot)(g)}"'] & F(A_2, \cdot)(B_1) \arrow[d, "{F(A_2, \cdot)(g)}"] \\
					F(A_1, \cdot)(B_2) \arrow[r, "{\al(F)^f_{B_2}}"] &  F(A_2, \cdot)(B_2).
				\end{tikzcd}
				\]
				Since $B_1, B_2 \in \Obj(\MB)$ and $g \in \Hom_{\MB}(B_1, B_2)$ are arbitrary, we have that for each $B_1, B_2 \in \Obj(\MB)$ and $g \in \Hom_{\MB}(B_1, B_2)$, $F(A_2, \cdot)(g) \circ_{\MC} \al(F)^f_{B_1} = \al(F)^f_{B_2} \circ_{\MC} F(A_1, \cdot)(g)$.
			\end{itemize}
			Thus $\al(F)^f:F(A_1, \cdot) \Rightarrow F(A_2, \cdot)$ is a natural transformation. Since $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$ are arbitrary, we have that for each $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$, $\al(F)^f:F(A_1, \cdot) \Rightarrow F(A_2, \cdot)$ is a natural transformation.
			\item Similar to \tcr{prev part (ref part)}.
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0003}
		Let $\MA, \MB, \MC$ be categories and $F :\MA \times \MB \rightarrow \MC$. Then
		\begin{enumerate}
			\item for each $A_1, A_2, A_3 \in \Obj(\MA)$, $f_{1,2} \in \Hom_{\MA}(A_1, A_2)$ and $f_{2,3} \in \Hom_{\MA}(A_2, A_3)$, $\al(F)^{f_{2,3} \circ_{\MA} f_{1,2}} = \al(F)^{f_{2,3}} \circ_{\MC^{\MB}} \al(F)^{f_{1,2}} $
			\item for each $B_1, B_2, B_3 \in \Obj(\MB)$, $g_{1,2} \in \Hom_{\MB}(B_1, B_2)$ and $g_{2,3} \in \Hom_{\MB}(B_2, B_3)$, $\be(F)^{g_{2,3} \circ_{\MB} g_{1,2}} = \be(F)^{g_{2,3}} \circ_{\MC^{\MA}} \be(F)^{g_{1,2}}$
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A_1, A_2, A_3 \in \Obj(\MA)$, $f_{1,2} \in \Hom_{\MA}(A_1, A_2)$ and $f_{2,3} \in \Hom_{\MA}(A_2, A_3)$. Then for each $B \in \Obj(\MB)$,
			\begin{align*}
				(\al(F)^{f_{2,3} \circ_{\MA} f_{1,2}})_B
				& = F(f_{2,3} \circ_{\MA} f_{1,2}, \id_B^{\MB}) \quad \text{(by \rd{def:basics:contructs:currying:0001})} \\
				& = F(f_{2,3} \circ_{\MA} f_{1,2}, \id_B^{\MB} \circ_{\MB} \id_B^{\MB}) \\
				& = F((f_{2,3}, \id_B^{\MB}) \circ_{\MA \times \MB} (f_{1,2}, \id_B^{\MB})) \\
				& = F(f_{2,3}, \id_B^{\MB}) \circ_{\MC} F(f_{1,2}, \id_B^{\MB}) \\
				& = \al(F)^{f_{2,3}}_B \circ_{\MC} \al(F)^{f_{1,2}}_B \\
				& = (\al(F)^{f_{2,3}} \circ_{\MC^{\MB}} \al(F)^{f_{1,2}})_B.
			\end{align*}
			Thus $\al(F)^{f_{2,3} \circ_{\MA} f_{1,2}} = \al(F)^{f_{2,3}} \circ_{\MC^{\MB}} \al(F)^{f_{1,2}}$.
			\item \tcr{similar to prev part (ref prev part)}
		\end{enumerate}
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0004}
		Let $\MA, \MB, \MC$ be categories and $F :\MA \times \MB \rightarrow \MC$. Then
		\begin{enumerate}
			\item For each $A \in \Obj(\MA)$, $\al(F)^{\id_A^{\MA}} = \id_{F(A, \cdot)}^{\MC^{\MB}}$.
			\item For each $B \in \Obj(\MB)$, $\be(F)^{\id_B^{\MB}} = \id_{F(\cdot, B)}^{\MC^{\MA}}$.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item For each $B \in \Obj(\MB)$, 
			\begin{align*}
				\al(F)^{\id_A^{\MA}}_B 
				& = F(\id_A^{\MA}, \id_B^{\MB}) \\
				& = F(\id_{(A,B)}^{\MA \times \MB}) \\
				& = \id_{F(A, B)}^{\MC} \\
				& = \id_{F(A, \cdot)(B)}^{\MC} \\
				& = (\id_{F(A, \cdot)})_B \quad \text{(by \rd{def:basics:nat_trans:cat_funct:0004})}.
			\end{align*}
			Since $B \in \Obj(\MB)$ is arbitrary, we have that for each $B \in \Obj(\MB)$, $\al(F)^{\id_A^{\MA}}_B = (\id_{F(A, \cdot)})_B$. Thus $\al(F)^{\id_A^{\MA}} = \id_{F(A, \cdot)}$.
			\item \tcr{Similar to prev part (ref prev part)}.
		\end{enumerate}
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:currying:0005}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$ and $F \in \Obj(\MC^{\MA \times \MB})$. We define the \tbf{Curry functor induced by $F$}, denoted $\cur(F): \MA \rightarrow \MC^{\MB}$ by 
		\begin{itemize}
			\item $\cur(F)(A) \defeq F(A, \cdot), \quad (A \in \Obj(\MA))$,
			\item $\cur(F)(f) \defeq \al(F)^f, \quad (f \in \Hom_{\MA})$,
		\end{itemize} 
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0006}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$ and $F \in \Obj(\MC^{\MA \times \MB})$. Then $\cur(F): \MA \rightarrow \MC^{\MB}$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$. \rex{ex:basics:contructs:currying:0002} implies that 
			\begin{align*}
				\cur(F)(f)
				& = \al(F)^f \\
				& \in \Hom_{\MC^{\MB}}(F(A_1, \cdot), F(A_2, \cdot)) \\
				& = \Hom_{\MC^{\MB}}(\cur(F)(A_1), \cur(F)(A_1)).
			\end{align*}
			\item Let $A_1, A_2, A_3 \in \Obj(\MA)$, $f_{1,2} \in \Hom_{\MA}(A_1, A_2)$ and $f_{2,3} \in \Hom_{\MA}(A_2, A_3)$. \rex{ex:basics:contructs:currying:0003} implies that 
			\begin{align*}
				\cur(F)(f_{2,3} \circ_{\MA} f_{1,2})
				& = \al(F)^{f_{2,3} \circ_{\MA} f_{1,2}} \\
				& = \al(F)^{f_{2,3}} \circ_{\MC^{\MB}} \al(F)^{f_{1,2}} \\
				& = \cur(F)(f_{2,3}) \circ_{\MC^{\MB}} \cur(F)(f_{1,2}).
			\end{align*} 
			\item Let $A \in \Obj(\MA)$. \rex{ex:basics:contructs:currying:0004} implies that,
			\begin{align*}
				\cur(F)(\id_A^{\MA})
				& = \al(F)^{\id_A^{\MA}} \\
				& = \id_{F(A, \cdot)}^{\MC^{\MB}} \\
				& = \id_{\cur(F)(A)}^{\MC^{\MB}}.
			\end{align*}
		\end{enumerate}
		Hence $\cur(F):\MA \rightarrow \MC^{\MB}$ is a functor. 
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:currying:0007}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$ and $F,G \in \Obj(\MC^{\MA \times \MB})$ and $\al \in \Hom_{\MC^{\MA \times \MB}}(F,G)$. We define the \tbf{Curry transformation induced by $\al$}, denoted $\cur(\al): \cur(F) \Rightarrow \cur(G)$ by 
		$$\cur(\al)_A \defeq \al_{(A, \cdot)}, \quad A \in \Obj(\MA).$$
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0008}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$, $F,G \in \Obj(\MC^{\MA \times \MB})$ and $\al \in \Hom_{\MC^{\MA \times \MB}}(F,G)$. Then $\cur(\al): \cur(F) \Rightarrow \cur(G)$ is a natural transformation. 
	\end{ex}
	
	\begin{proof}\
		\begin{itemize}
			\item \rex{ex:basics:contructs:products:0010} implies that for each $A \in \Obj(\MA)$,
			\begin{align*}
				\cur(\al)_A
				& = \al_{(A, \cdot)} \\
				& \in \Hom_{\MC^{\MB}}(F(A, \cdot), G(A, \cdot)) \\
				& = \Hom_{\MC^{\MB}}(\cur(F)(A), \cur(G)(A)).
			\end{align*}
			\item Let $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$. Since $\al \in \Hom_{\MC^{\MA \times \MB}}(F,G)$, we have that
			\begin{align*}
				G(f, \id_B^{\MB}) \circ_{\MC} \al_{(A_1,B)}
				& = \al_{(A_2,B)} \circ_{\MC}  F(f, \id_{B}^{\MB}),
			\end{align*}
			i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				F(A_1, B)  \arrow[r, "{\al_{(A_1,B)} }"] \arrow[d, "{F(f, \id_B^{\MB})}"'] & G(A_1, B) \arrow[d, "{G(f, \id_B^{\MB})}"] \\
				F(A_2, B) \arrow[r, "{\al_{(A_2, B)}}"] &  G(A_2, B).
			\end{tikzcd}
			\]
			Therefore for each $B \in \Obj(\MB)$,
			\begin{align*}
				(\cur(G)(f) \circ_{\MC^{\MB}} \cur(\al)_{A_1})_B
				& = \cur(G)(f)_B \circ_{\MC} (\cur(\al)_{A_1})_B \\
				& = G(f, \id_B^{\MB}) \circ_{\MC} \al_{(A_1,B)} \\
				& = \al_{(A_2,B)} \circ_{\MC}  F(f, \id_{B}^{\MB}) \\
				& = \cur(\al)_{A_1})_B \circ_{\MC} \cur(F)(f)_B \\
				& = (\cur(\al)_{A_1} \circ_{\MC} \cur(F)(f))_B.
			\end{align*}
			Hence $\cur(G)(f) \circ_{\MC^{\MB}} \cur(\al)_{A_1} = \cur(\al)_{A_2} \circ_{\MC} \cur(F)(f)$, i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				\cur(F)(A_1)  \arrow[r, "{\cur(\al)_{A_1}}", Rightarrow] \arrow[d, "{\cur(F)(f)}"', Rightarrow] & \cur(G)(A_1) \arrow[d, Rightarrow, "{\cur(G)(f)}"] \\
				\cur(F)(A_2) \arrow[r, "{\cur(\al)_{A_2}}", Rightarrow] &  \cur(G)(A_2).
			\end{tikzcd}
			\]
			Since $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$ are arbitrary, we have that for each $A_1, A_2 \in \Obj(\MA)$ and $f \in \Hom_{\MA}(A_1, A_2)$, $\cur(G)(f) \circ_{\MC^{\MB}} \cur(\al)_{A_1} = \cur(\al)_{A_2} \circ_{\MC} \cur(F)(f)$. 
		\end{itemize}
		Thus $\cur(\al):\cur(F) \Rightarrow \cur(G)$ is a natural transformation. 
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0009}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$, $F_1, F_2, F_3 \in \Obj(\MC^{\MA \times \MB})$, $\al_{1,2} \in \Hom_{\MC^{\MA \times \MB}}(F_1, F_2)$ and $\al_{2,3} \in \Hom_{\MC^{\MA \times \MB}}(F_2, F_3)$. Then $\cur(\al_{2,3} \circ_{\MC^{\MA \times \MB}} \al_{1,2}) = \cur(\al_{2,3}) \circ_{(\MC^{\MB})^{\MA}} \cur(\al_{1,2})$.
	\end{ex}
	
	\begin{proof}
		\rex{ex:basics:contructs:products:0010.1} implies that for each $A \in \Obj(\MA)$,
		\begin{align*}
			\cur(\al_{2,3} \circ_{\MC^{\MA \times \MB}} \al_{1,2})_A
			& = (\al_{2,3} \circ_{\MC^{\MA \times \MB}} \al_{1,2})_{(A, \cdot)} \\
			& = (\al_{2,3})_{(A, \cdot)} \circ_{\MC^{\MB}} (\al_{1,2})_{(A, \cdot)} \\
			& = \cur(\al_{2,3})_A \circ_{\MC^{\MB}} \cur(\al_{1,2})_A \\
			& = [\cur(\al_{2,3}) \circ_{(\MC^{\MB})^{\MA}} \cur(\al_{1,2})]_A.
		\end{align*}
		Therefore $\cur(\al_{2,3} \circ_{\MC^{\MA \times \MB}} \al_{1,2}) = \cur(\al_{2,3}) \circ_{(\MC^{\MB})^{\MA}} \cur(\al_{1,2})$.
	\end{proof}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0010}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$ and $F \in \Obj(\MC^{\MA \times \MB})$. Then $\cur(\id_F^{\MC^{\MA \times \MB}}) = \id_{\cur(F)^{(\MC^{\MB})^{\MA}}}$. 
	\end{ex}
	
	\begin{proof}
		\rex{ex:basics:contructs:products:0010.2} implies that for each $A \in \Obj(\MA)$,
		\begin{align*}
			\cur(\id_F^{\MC^{\MA \times \MB}})_A
			& = (\id_F^{\MC^{\MA \times \MB}})_{(A, \cdot)} \\
			& = \id_{F(A, \cdot)}^{\MC^{\MB})} \\
			& = \id_{\cur(F)(A)}^{\MC^{\MB}} \\
			& = (\id_{\cur(F)}^{(\MC^{\MB})^{\MA}})_A.
		\end{align*}
		Hence $\cur(\id_F^{\MC^{\MA \times \MB}}) = \id_{\cur(F)}^{(\MC^{\MB})^{\MA}}$.
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:currying:0011}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$. We define the \tbf{Curry functor from $\MC^{\MA \times \MB}$ to $(\MC^{\MB})^{\MA}$}, denoted $\cur^{\Cat}_{(\MA, \MB, \MC)}: \MC^{\MA \times \MB} \rightarrow (\MC^{\MB})^{\MA}$ by 
		\begin{itemize}
			\item $\cur^{\Cat}_{(\MA, \MB, \MC)}(F) \defeq \cur(F)$
			\item $\cur^{\Cat}_{(\MA, \MB, \MC)}(\al) \defeq \cur(\al)$.
		\end{itemize}   
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0012}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$. Then $\cur^{\Cat}_{(\MA, \MB, \MC)}: \MC^{\MA \times \MB} \rightarrow (\MC^{\MB})^{\MA}$ is a functor.
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $F,G \in \Obj(\MC^{\MA \times \MB})$ and $\al \in \Hom_{\MC^{\MA \times \MB}}(F, G)$. \rex{ex:basics:contructs:currying:0008} implies that
			\begin{align*}
				\cur^{\Cat}_{(\MA, \MB, \MC)}(\al)
				& = \cur(\al) \\
				& \in \Hom_{\MC^{\MB}}(\cur(F), \cur(G)) \\
				& = \Hom_{\MC^{\MB}}(\cur^{\Cat}_{(\MA, \MB, \MC)}(F), \cur^{\Cat}_{(\MA, \MB, \MC)}(G)).
			\end{align*}
			\item Let $F_1, F_2, F_3 \in \Obj(\MC^{\MA \times \MB})$, $\al_{1,2} \in \Hom_{\MC^{\MA \times \MB}}(F_1, F_2)$ and $\al_{2,3} \in \Hom_{\MC^{\MA \times \MB}}(F_2, F_3)$. \rex{ex:basics:contructs:currying:0009} implies that
			\begin{align*}
				\cur^{\Cat}_{(\MA, \MB, \MC)}(\al_{2,3} \circ_{\MC^{\MA \times \MB}} \al_{1,2})
				 & = \cur((\al_{2,3} \circ_{\MC^{\MA \times \MB}} \al_{1,2})) \\
				 & = \cur(\al_{2,3}) \circ_{(\MC^{\MB})^{\MA}} \cur(\al_{1,2}) \\
				 & = \cur^{\Cat}_{(\MA, \MB, \MC)}(\al_{2,3}) \circ_{(\MC^{\MB})^{\MA}} \cur^{\Cat}_{(\MA, \MB, \MC)}(\al_{1,2}).
			\end{align*}
			\item \rex{ex:basics:contructs:currying:0010} implies that 
			\begin{align*}
				\cur^{\Cat}_{(\MA, \MB, \MC)}(\id_F^{\MC^{\MA \times \MB}}) 
				& = \cur(\id_F^{\MC^{\MA \times \MB}}) \\
				& = \id_{\cur(F)}^{(\MC^{\MB})^{\MA}} \\
				& = \id_{\cur^{\Cat}_{(\MA, \MB, \MC)}(F)}^{(\MC^{\MB})^{\MA}}.
			\end{align*}
		\end{enumerate}
		Thus $\cur^{\Cat}_{(\MA, \MB, \MC)}: \MC^{\MA \times \MB} \rightarrow (\MC^{\MB})^{\MA}$ is a functor.
	\end{proof}
	
	\begin{defn} \ld{def:basics:contructs:currying:0013}
		We define the \tbf{Currying natural transformation on $\Cat$}, denoted $\cur^{\Cat}: [(- \times -)_{\Cat}, -]_{\Cat} \Rightarrow [-, [-, -]_{\Cat}]_{\Cat}$, by  $(\cur^{\Cat})_{(\MA, \MB, \MC)} \defeq \cur^{\Cat}_{(\MA, \MB, \MC)}$
	\end{defn}
	
	\begin{ex} \lex{ex:basics:contructs:currying:0014}
		We have that $\cur^{\Cat}:[(- \times -)_{\Cat}, -]_{\Cat} \Rightarrow [-, [-, -]_{\Cat}]_{\Cat}$ is a natural transformation.
	\end{ex}
	
	\begin{proof}
		\item \tcr{show it is in correct Hom set}
		\item \tcr{Show diagram commutes}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\tcr{To Do:  
	\begin{itemize}
		\item make a note that $[-, [-, -]]: \op{\Cat} \times (\op{\Cat} \times \Cat) \rightarrow \Cat$ means $[-, -] \circ \id_{\Cat} \times [-, -]$
		\item define opposite functor $OP: \MC \rightarrow \op{\MC}$
		\item show that $\cur^{\Cat}:F \Rightarrow G$ is a natural transformation (and natural isomorphism) 
	\end{itemize}
	}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\begin{defn}
		
	\end{defn}
	
	\begin{ex}
		content...
	\end{ex}
	
	\begin{proof}
		content...
	\end{proof}
	
	\begin{defn}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$. We define the \tbf{Currying functor from $(\MC)^{\MA \times \MB}$ to $(\MC^{\MB})^{\MA}$}, denoted $\cur^{\Cat}_{(\MA,\MB, \MC)}: (\MC)^{\MA \times \MB} \rightarrow (\MC^{\MB})^{\MA}$, by 
		\begin{itemize}
			\item $\cur^{\Cat}_{(\MA,\MB, \MC)}(F) \defeq \cur(F), \quad (A \in \Obj(\MA))$
			\item $\cur^{\Cat}_{(\MA,\MB, \MC)}(\al)(A) \defeq \al_{(A, \cdot)}$.
		\end{itemize}
		\tcr{(need exercise showing that if $\MA, \MB$ are small, then $\MA \times \MB$ is small)}
	\end{defn}
	
	\begin{ex}
		Let $\MA, \MB, \MC \in \Obj(\Cat)$. Then $\cur^{\Cat}_{(\MA, \MB, \MC)}: \MC^{\MA \times \MB} \rightarrow (\MC^{\MB})^{\MA}$ is a functor. 
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Let $F,G \in \Obj(\MC^{\MA \times \MB})$ and $\al \in \Hom_{\MC^{\MA \times \MB}}(F, G)$. Then for each $A \in \Obj(\MA)$,
			\begin{align*}
				\cur^{\Cat}_{\MA, \MB, \MC}(\al)(A)
				& = \al_{(A, \cdot)} \\
				& \in \Hom_{\MC^{\MB}}(F(A, \cdot), G(A, \cdot))  \quad \text{(by \tcr{ref prev ex})}\\
				& = \Hom_{\MC^{\MB}}(\cur^{\Cat}_{(\MA,\MB, \MC)}(F)(A), \cur^{\Cat}_{(\MA,\MB, \MC)}(G)(A)) 
			\end{align*}
			\item 
			\item 
		\end{enumerate}
	\end{proof}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\section{Equalizer and Coequalizer Categories}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	























































































































































	
	























	















































	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\newpage
	\chapter{Limits}
	
	\section{Cones and Cocones}
	
	\begin{defn} \ld{def:limits:cones_cocones:0001}
		Let $\MJ$, $\MC$ be categories and $D: \MJ \rightarrow \MC$. Then $D$ is said to be a \textbf{diagram of type $\MJ$ in $\MC$}.
	\end{defn}
	
	\begin{note}
		We are usually interested in the case that $\MJ$ is small. We will identify a diagram $D$ with its image \tcr{and we visualize a diagram by the generating morphisms in $\MJ$}. 
	\end{note}
	
	\begin{exmp} \tcr{create example reference}
		Define $\MJ$ by
		\begin{itemize}
			\item  $\Obj(\MJ) = \{1, 2, 3, 4\}$,
			\item for $i,j \in \Obj(\MJ)$, $\Hom_{\MJ}(i,j) = \{a_{ij}\}$.
		\end{itemize}
		Let $\MC$ be a category and $D: \MJ \rightarrow \MC$. Without including the identity morphisms or compositions, we can visualize $D$ \tcr{by its set of generating morphisms (i.e. not including the identity morphisms)} as follows:
		\[
		\begin{tikzcd}
			&     1  \arrow[dl, "a_{1,3}"'] \arrow[r, "a_{1,2}"]        &  2 \arrow[dl, "a_{2,4}"] \\
			3 \arrow[r, "a_{3,4}"'] &        4   & \\
		\end{tikzcd}
		\overset{D}{\longrightarrow}
		\begin{tikzcd}
			&     D_1  \arrow[dl, "D_{1,3}"'] \arrow[r, "D_{1,2}"]        &  D_2 \arrow[dl, "D_{2,4}"] \\
			D_3 \arrow[r, "D_{3, 4}"'] &        D_4   & \\
		\end{tikzcd}
		\]
	\end{exmp}
	
	\begin{defn} \ld{def:limits:cones_cocones:0003}
		Let $\MJ$, $\MC$ be categories. Suppose that $\MJ$ is small. Let $D \in \Obj(\MC^{\MJ})$. 
		\begin{itemize}
			\item We define the \textbf{category of cones over $D$}, denoted $\Cone(D)$, by $\Cone(D) = (\Del^{\MJ} \doar D)$.
			\item We define the \textbf{category of cocones under $D$}, denoted $\Cocone(D)$, by $\Cocone(D) = (D \doar \Del^{\MJ})$.
		\end{itemize}
	\end{defn}
	
	\begin{note}\
		\begin{itemize}
			\item By defintion,
			\begin{align*}
				\Obj(\Cone(D)) 
				& = \{(X, \phi): X \in \Obj(\MC) \text{ and } \phi \in \Hom_{\MC^{\MJ}}(\Del^{\MJ}(X), D) \} \\
				& = \{(X, \phi): X \in \Obj(\MC) \text{ and } \phi: \Del^{\MJ}_X \Rightarrow D\}
			\end{align*}
			and for $(X, \phi), (Y, \psi) \in \Obj(\Cone(D))$,
			\begin{align*}
				\Hom_{\Cone(D)}((X, \phi),(Y, \psi)) 
				& = \{\al \in \Hom_{\MC}(X, Y): \psi \circ_{\MC^{\MJ}} \Del^{\MJ}(\al) = \phi \} \\
				& = \{\al \in \Hom_{\MC}(X, Y): \psi \circ_{\MC^{\MJ}} \del^{\MJ}_{\al} = \phi \} \\
				& = \{\al \in \Hom_{\MC}(X, Y): \text{for each $j \in \MJ$, $\psi_j \circ_{\MC} \al  = \phi_j$} \}.
			\end{align*}
			\tcr{make ex in subcategory section and rephrase this in terms of the commutative diagram on only the generating morphisms. This will enable us to more precisely cover limits like products and projective systems where the identity maorphisms are not typically included in the definition of a diagram, but rather only the set of generating morphisms}. Therefore, $(X, \phi) \in \Obj(\Cone(D))$ iff for each $i,j \in \Obj(\MJ)$ and $f_{i,j} \in \Hom_{\MJ}(i, j)$, the following diagram commutes:
			\[ 
			\begin{tikzcd}
				&  X \arrow[dl, "\phi_i"']  \arrow[dr, "\phi_j"] & \\
				D_i  \arrow[rr, "D_{f_{i,j}}"'] &&  D_j \\ 
			\end{tikzcd}
			\]  
			and $\al \in \Hom_{\Cone(D)}((X, \phi), (Y, \psi))$ iff  for each $i,j \in \Obj(\MJ)$ and $(i,j) \in \Hom_{\MJ}(i, j)$ the following diagram commutes: 
			\[ 
			\begin{tikzcd}
				& X \arrow[d, "\al"'] \arrow[bend right=30, swap]{ddl}{\phi_i} \arrow[bend left=30]{ddr}{\phi_j} \\
				&  Y \arrow[dl, "\psi_i"']  \arrow[dr, "\psi_j"] & \\
				D_i  \arrow[rr, "D_{i,j}"'] &&  D_j \\ 
			\end{tikzcd}
			\]
			\item By defintion,
			\begin{align*}
				\Obj(\Cocone(D)) 
				& = \{(X, \phi): X \in \Obj(\MC) \text{ and } \phi \in \Hom_{\MC^{\MJ}}( D, \Del^{\MJ}(X)) \} \\
				& = \{(X, \phi): X \in \Obj(\MC) \text{ and } \phi: D \Rightarrow \Del^{\MJ}_X\}
			\end{align*}
			and for $(X, \phi), (Y, \psi) \in \Obj(\Cocone(D))$,
			\begin{align*}
				\Hom_{\Cocone(D)}((X, \phi),(Y, \psi)) 
				& = \{\al \in \Hom_{\MC}(X, Y): \Del^{\MJ}(\al) \circ_{\MC^{\MJ}} \phi = \psi \} \\
				& = \{\al \in \Hom_{\MC}(X, Y): \del^{\MJ}_{\al} \circ_{\MC^{\MJ}} \phi = \psi \} \\
				& = \{\al \in \Hom_{\MC}(X, Y): \text{for each $j \in \MJ$, $\al \circ_{\MC} \phi_j = \psi_j$} \}.
			\end{align*}
			\tcr{make ex in subcategory section and rephrase this in terms of the commutative diagram on only the generating morphisms. This will enable us to more precisely cover limits like products and projective systems where the identity maorphisms are not typically included in the definition of a diagram, but rather only the set of generating morphisms}. Therefore, $(X, \phi) \in \Obj(\Cone(D))$ iff for each $i,j \in \Obj(\MJ)$ and $f_{i,j} \in \Hom_{\MJ}(i, j)$, the following diagram commutes:
			\[ 
			\begin{tikzcd}
				D_i \arrow[dr, "\phi_i"'] \arrow[rr, "D_{f_{i,j}}"] &&  D_j \arrow[dl, "\phi_j"]  \\ 
				&  X  & 
			\end{tikzcd}
			\]  
			and $\al \in \Hom_{\Cone(D)}((X, \phi), (Y, \psi))$ iff  for each $i,j \in \Obj(\MJ)$ and $(i,j) \in \Hom_{\MJ}(i, j)$ the following diagram commutes: 
			\[ 
			\begin{tikzcd}
				D_i \arrow[dr, "\phi_i"'] \arrow[rr, "D_{f_{i,j}}"] \arrow[bend right=30, swap]{ddr}{\psi_i}  & &  D_j \arrow[dl, "\phi_j"] \arrow[bend left=30]{ddl}{\psi_j} \\ 
				&  X  \arrow[d, "\al"'] & \\
				&  Y & 
			\end{tikzcd}
			\]
			
		\end{itemize}
	\end{note}
	
	
	
	\tcr{note that in the case of say a product of projective system, the category $\MJ$ does not include the identity morphisms in the Hom sets, to avoid having to specify the category with all morphisms, rephrase this definition in terms of the subcategory generated by a set of morphisms. This will need some exercises made in section on subcategories about natural transformations on a generated subcategory needing only to satisfy the composition rules in the def natl transf's on the generating morphisms of that category. maybe other similar exercises needed as well. For example in a product, when we write the diagram, we include the objects $X,Y$ but we never include the morphisms $\id_X, \id_Y$ in the diagram.}
	
	\begin{exmp} \tcr{ref example}
		Define $\MJ$ and $\MD$ \tcr{as in previous example}. 
		\begin{itemize}
			\item Let $(X, \phi) \in \Obj(\Cone(D))$. We can visualize $(X, \phi)$ as follows:
			\[
			\begin{tikzcd}
				&  &  X \arrow[ddd, "\phi_1"'] \arrow[ddddll, "\phi_3"']  \arrow[dddrrr, "\phi_2"], \arrow[ddddr, "\phi_4"] &       &    \\
				&       &     &       &    \\
				&       &     &       &    \\
				&       &  D_1  \arrow[dll, "D_{1,3}"'] \arrow[rrr, "D_{1,2}"]    &       & &  D2 \arrow[dll, "D_{2,4}"] \\
				D_3 \arrow[rrr, "D_{3,4}"'] &       &     &  D_4  &    \\
			\end{tikzcd}
			\]
			\item Let $(X, \phi) \in \Obj(\Cocone(D))$. We can visualize $(X, \phi)$ as follows:
			\[
			\begin{tikzcd}
				&  &  X \arrow[ddd, "\phi_1"'] \arrow[ddddll, "\phi_3"']  \arrow[dddrrr, "\phi_2"], \arrow[ddddr, "\phi_4"] &       &    \\
				&       &     &       &    \\
				&       &     &       &    \\
				&       &  D_1  \arrow[dll, "D_{1,3}"'] \arrow[rrr, "D_{1,2}"]    &       & &  D2 \arrow[dll, "D_{2,4}"] \\
				D_3 \arrow[rrr, "D_{3,4}"'] &       &     &  D_4  &    \\
			\end{tikzcd}
			\]
			\tcr{FIX!!!!}
		\end{itemize}
	\end{exmp}
	
	\begin{ex} \lex{ex:limits:cones_cocones:0005}
		\tcr{show $\Cocone(D) \cong \op{\Cone(D)}$ (ref ex about comma categories and opposite categories)}
	\end{ex}
	
	\begin{proof}
		
	\end{proof}
	
	
	\begin{ex} \lex{ex:limits:cones_cocones:0006}
		Let $\MC$ be a category, $\MJ \in \Obj(\Cat)$ and $D_1, D_2 \in \Obj(\MC^{\MJ})$.
		\begin{enumerate}
			\item Let $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$.
			\begin{enumerate}
				\item For each $(X, \phi) \in \Obj(\Cone(D_1))$, 
				$$(X, \al \circ_{\MC^{\MJ}} \phi) \in \Obj(\Cone(D_2)).$$
				\item For each $(X, \phi), (X', \phi') \in \Obj(\Cone(D_1))$ and $\eta \in \Hom_{\Cone(D_1)}((X, \phi), (X', \phi'))$, 
				$$\eta \in \Hom_{\Cone(D_2)}((X, \al \circ_{\MC^{\MJ}} \phi), (X', \al \circ_{\MC^{\MJ}} \phi')).$$
			\end{enumerate} 
			\item Let $\be \in \Hom_{\MC^{\MJ}}(D_2, D_1)$.
			\begin{enumerate}
				\item \tcr{FIX for cocones}
				\item 
			\end{enumerate} 
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\begin{enumerate}
				\item Let $(X, \phi) \in \Obj(\Cone(D_1))$. Then $X \in \Obj(\MC)$ and $\phi \in \Hom_{\MC^{\MJ}}(\Del^{\MJ}_X, D_1)$. Therefore $\al \circ_{\MC^{\MJ}} \phi \in \Hom_{\MC^{\MJ}}(\Del^{\MJ}_X, D_2)$. Hence $(X, \al \circ_{\MC^{\MJ}} \phi) \in \Obj(\Cone(D_2))$. 
				\item Let $(X, \phi), (X', \phi') \in \Obj(\Cone(D_1))$ and $\eta \in \Hom_{\Cone(D_1)}((X, \phi), (X', \phi'))$. Then $\eta \in \Hom_{\MC}(X, X')$ and $\phi' \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta) = \phi$. Therefore $\al \circ_{\MC^{\MJ}} \phi' \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta) = \al \circ_{\MC^{\MJ}} \phi$. Hence $\eta \in \Hom_{\Cone(D_2)}((X, \al \circ_{\MC^{\MJ}} \phi), (X', \al \circ_{\MC^{\MJ}} \phi'))$.
			\end{enumerate}
			\item \tcr{use duality}
		\end{enumerate}
	\end{proof}
	
	\begin{defn} \ld{def:limits:cones_cocones:0007}
		Let $\MC$ be a category, $\MJ \in \Obj(\Cat)$ and $D_1, D_2 \in \Obj(\MC^{\MJ})$.
		\begin{enumerate}
			\item Let $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$. We define the \tbf{cone functor induced by $\al$}, denoted $\Cn_{\al}: \Cone(D_1) \rightarrow \Cone(D_2)$, by 
			\begin{itemize}
				\item $\Cn_{\al}(X, \phi) \defeq (X, \al \circ_{\MC^{\MJ}} \phi), \quad (X, \phi) \in \Obj(\Cone(D_1))$,
				\item $\Cn_{\al}(\eta) \defeq \eta, \quad \eta \in \Hom_{\Cone(D_1)}$.
			\end{itemize}
			\item \tcr{similar for cocone functor}
		\end{enumerate}
	\end{defn}
	
	\begin{ex} \lex{ex:limits:cones_cocones:0008}
		Let $\MC$ be a category, $\MJ \in \Obj(\Cat)$ and $D_1, D_2 \in \Obj(\MC^{\MJ})$.
		\begin{enumerate}
			\item Let $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$. Then $\Cn_{\al}: \Cone(D_1) \rightarrow \Cone(D_2)$ is a functor.
			\item \tcr{similar for cocone functor}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item We note that \tcr{ref prev ex} implies that $\Cn_{\al}$ is well-defined. 
			\begin{enumerate}
				\item \tcr{ref prev ex} implies that for each $(X, \phi), (X', \phi') \in \Obj(\Cone(D_1))$, and $\eta \in \Hom_{\Cone(D_1)}((X, \phi), (X', \phi'))$,
				\begin{align*}
					\Cn_{\al}(\eta)
					& = \eta \\
					& \in \Hom_{\Cone(D_2)}((X, \al \circ{\MC^{\MJ}} \phi), (X', \al \circ{\MC^{\MJ}} \phi')) \\
					& = \Hom_{\Cone(D_2)}(\Cn_{\al}(X, \phi), \Cn_{\al}(X', \phi')).
				\end{align*}
				\item Let $(X, \phi), (Y, \psi), (Z, \chi) \in \Obj(\Cone(D_1))$ and $\mu \in \Hom_{\Cone(D_1)}((X, \phi), (Y, \psi))$ and $\nu \in \Hom_{\Cone(D_1)}((Y, \psi), (Z, \chi))$. Since $\Cone(D_1) = (\Del^{\MJ} \doar D_1)$ and $\Cone(D_2) = (\Del^{\MJ} \doar D_2)$,  \rd{def:basics:functors:comma_cat:0004} implies that 
				\begin{align*}
					\Cn_{\al}(\nu \circ_{\Cone(D_1)} \mu)
					& = \nu \circ_{\Cone(D_1)} \mu \\
					& = \nu \circ_{(\Del^{\MJ} \doar D_1)} \mu \\
					& = \nu \circ_{\MC} \mu \\
					& = \nu \circ_{(\Del^{\MJ} \doar D_2)} \mu \\
					& = \nu \circ_{\Cone(D_2)} \mu \\
					& = \Cn_{\al}(\nu) \circ_{\Cone(D_2)} \Cn_{\al}(\mu).
				\end{align*} 
				\item 
				By \rd{def:limits:cones_cocones:0003},  
				\begin{align*}
					\id_{(X, \phi)}^{\Cone(D_1)} 
					& = \id_{(X, \phi)}^{(\Del^{\MJ} \doar D_1)} \\
					& = \id_X^{\MC} \\
					& = \id_{(X, \al \circ_{\MC^{\MJ}} \phi)}^{(\Del^{\MJ} \doar D_2)} \\
					& = \id_{(X, \al \circ_{\MC^{\MJ}} \phi)}^{\Cone(D_2)}.
				\end{align*}
				Hence for each $(X, \phi) \in \Obj(\Cone(D_1))$,
				\begin{align*}
					\Cn_{\al}(\id_{(X, \phi)}^{\Cone(D_1)})
					& = \id_{(X, \phi)}^{\Cone(D_1)} \\
					& = \id_{(X, \al \circ_{\MC^{\MJ}} \phi)}^{\Cone(D_2)} \\
					& = \id_{\Cn_{\al}(X, \phi)}^{\Cone(D_2)}.
				\end{align*}
			\end{enumerate}
			Hence $\Cn_{\al}: \Cone(D_1) \rightarrow \Cone(D_2)$ is a functor.
			\item \tcr{use duality}
		\end{enumerate}
	\end{proof}

	\begin{defn}
		Let $\MC$ be a category, $\MJ \in \Obj(\Cat)$. 
		\begin{enumerate}
			\item We define the \tbf{Cone functor}, denoted $\Cone(\cdot):\MC^{\MJ} \rightarrow \Cat$, by
			\begin{itemize}
				\item $\Cone(\cdot)(D) \defeq \Cone(D), \quad D \in \Obj(\MC^{\MJ})$ 
				\item $\Cone(\cdot)(\al) \defeq \Cn_{\al}, \quad \al \in \Hom_{\MC^{\MJ}}$.
			\end{itemize}
			\item \tcr{define cocone functor}
		\end{enumerate}
	\end{defn}
	
	\begin{ex}
		Let $\MC$ be a category, $\MJ \in \Obj(\Cat)$. 
		\begin{enumerate}
			\item We have that $\Cone(\cdot):\MC^{\MJ} \rightarrow \Cat$ is a functor.
			\item \tcr{show cocone functor is functor}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item Set $C \defeq \Cone(\cdot)$.
			\begin{enumerate}
				\item Let $D_1, D_2 \in \Obj(\MC^{\MJ})$ and $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$. Then 
				\begin{align*}
					C(\al)
					& = \Cn_{\al} \\
					& \in \Hom_{\Cat}(\Cone(D_1), \Cone(D_2)) \\
					& = \Hom_{\Cat}(C(D_1), C(D_2)).
				\end{align*}
				\item Let $D_1, D_2, D_3 \in \Obj(\MC^{\MJ})$, $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$ and $\be \in \Hom_{\MC^{\MJ}}(D_2, D_3)$. Then for each $(X, \phi) \in \Obj(\Cone(D))$,
				\begin{align*}
					[C(\be \circ_{\MC^{\MJ}} \al)](X, \phi)
					& = \Cn_{\be \circ_{\MC^{\MJ}} \al} (X, \phi) \\
					& = (X, [\be \circ_{\MC^{\MJ}} \al] \circ_{\MC^{\MJ}} \phi) \\
					& = (X, \be \circ_{\MC^{\MJ}} [\al \circ_{\MC^{\MJ}} \phi]) \\
					& = \Cn_{\be}(X, \al \circ_{\MC^{\MJ}} \phi) \\
					& = \Cn_{\be}(\Cn_{\al}(X, \phi)) \\
					& = C(\be)[C(\al)(X, \phi)] \\
					& = [C(\be) \circ_{\Cat} C(\al)](X, \phi)
				\end{align*} 
				Therefore $C(\be \circ_{\MC^{\MJ}} \al) = C(\be) \circ_{\Cat} C(\al)$.
				\item Let $D \in \Obj(\MC^{\MJ})$. Then for each $(X, \phi), (X', \phi') \in \Obj(\Cone(D))$ and $\eta \in \Hom_{\Cone(D)}((X, \phi), (X', \phi'))$,
				\begin{align*}
					C(\id_D^{\MC^{\MJ}})(X, \phi)
					& = \Cn_{\id_D^{\MC^{\MJ}}}(X, \phi) \\
					& = (X, \id_D^{\MC^{\MJ}} \circ_{\MC^{\MJ}} \phi) \\
					& = (X, \phi) \\
					& = \id_{\Cone(D)}^{\Cat}(X, \phi) \\
					& = \id_{C(D)}^{\Cat}(X, \phi)
				\end{align*}
				and 
				\begin{align*}
					C(\id_D^{\MC^{\MJ}})(\eta)
					& = \Cn_{\id_D^{\MC^{\MJ}}}(\eta) \\
					& = \eta \\
					& = \id_{\Cone(D)}^{\Cat}(\eta) \\
					& = \id_{C(D)}^{\Cat}(\eta).
				\end{align*}
				Thus $C(\id_D^{\MC^{\MJ}}) = \id_{C(D)}^{\Cat}$.
			\end{enumerate}
			Hence $\Cone(\cdot):\MC^{\MJ} \rightarrow \Cat$ is a functor.
			\item \tcr{FINISH for cocones!!!!}
		\end{enumerate}
	\end{proof}



































	\newpage
	\section{Limits and Colimits}
	
	\subsection{Universal Morphisms}
	\tcr{make subsection instead of section and put it in section on limits after section on cones and cocones}
	
	\begin{defn} \ld{def:limits:limits_colimits:0001}
		Let $\MC, \MD$ be a categories, $X \in \Obj(\MD)$, $F: \MC \rightarrow \MD$ and $A \in \Obj(\MC)$.
		\begin{itemize}
			\item Let $f \in \Hom_{\MD}(X, F(A))$. Then $(A, f)$ is said to be a \textbf{universal morphism from $X$ to $F$} if for each $A' \in \Obj(\MC)$ and $f' \in \Hom_{\MD}(X, F(A'))$, there exists a unique $\al \in \Hom_{\MC}(A, A')$ such that $F(\al) \circ_{\MC} f = f'$, i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				X \arrow[r, "f"]  \arrow[dr, "f'"'] & F(A) \arrow[d, "F(\al)", dashed] \\
				& F(A')  
			\end{tikzcd}
			\hspace{.3cm}
			\begin{tikzcd}
				A  \arrow[d, "\al", dashed] \\
				A'  
			\end{tikzcd}
			\]
			\item Let $f \in \Hom_{\MD}(F(A), X)$. Then $(A, f)$ is said to be a \textbf{universal morphism from $F$ to $X$} if for each $A' \in \Obj(\MC)$ and $f' \in \Hom_{\MD}(F(A'), X)$, there exists a unique $\al \in \Hom_{\MC}(A', A)$ such that $f \circ_{\MD} F(\al) = f'$, i.e. the following diagram commutes:
			\[
			\begin{tikzcd}
				X   & F(A) \arrow[l, "f"'] \\
				& F(A')  \arrow[ul, "f'"] \arrow[u, "F(\al)"', dashed]  
			\end{tikzcd}
			\hspace{.3cm}
			\begin{tikzcd}
				A \\
				A'  \arrow[u, "\al"', dashed]   
			\end{tikzcd}
			\]
		\end{itemize}
	\end{defn}
	
	\begin{ex} \lex{ex:limits:limits_colimits:0002}
		Let $\MC, \MD$ be a categories, $X \in \Obj(\MD)$, $F: \MC \rightarrow \MD$ and $A \in \Obj(\MC)$.
		\begin{enumerate}
			\item Let $f \in \Hom_{\MD}(X, F(A))$. Then $(A, f)$ is a universal morphism from $X$ to $F$ iff $(A, f)$ is $(X \doar F)$-initial. 
			\item Let $f \in \Hom_{\MD}(F(A), X)$. Then $(A, f)$ is a universal morphism from $F$ to $X$ iff $(A, f)$ is $(F \doar X)$-terminal.
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\item 
		\end{enumerate}
		\tcr{FINISH!!!}
	\end{proof}
	
	\begin{note}
		\tcr{make a comment on how if $(A, f)$ is universal from $X$ to $F$, then for each $(A', f')$, $f'$ is a post-processing of $f$ and $(A, f)$ is universal from $F$ to $X$, then for each $(A', f')$, $f'$ is a pre-processing of $f$}
	\end{note}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Limits and Colimits}
	
	\begin{defn} \ld{def:limits:limits_colimits:0003}
		Let $\MJ$, $\MC$ be categories. Suppose that $\MJ$ is small. Let $D \in \Obj(\MC^{\MJ})$. 
		\begin{itemize}
			\item 
			\begin{itemize}
				\item Let $(X, \phi) \in \Obj(\Cone(D))$. Then $(X, \phi)$ is said to be a \textbf{$D$-limit}, denoted $(X, \phi) = \lim D$, if $(X, \phi)$ is a universal morphism from $\Del^{\MJ}$ to $D$.  
				\item We define the \tbf{limit set of $D$}, denoted $\limSet(D)$, by 
				$$\limSet D \defeq \{(X, \phi) \in \Obj(\Cone(D)): \text{$\Obj(\Cone(D))$ is a $D$-limit}\}.$$
			\end{itemize}
			\item 
			\begin{itemize}
				\item Let $(X, \phi) \in \Obj(\Cocone(D))$. Then $(X, \phi)$ is said to be a \textbf{$D$-colimit}, denoted $(X, \phi) = \colim D$, if $(X, \phi)$ is a universal morphism from $D$ to $\Del^{\MJ}$.  
				\item We define the \tbf{colimit set of $D$}, denoted $\colimSet(D)$, by 
				$$\colimSet D \defeq \{(X, \phi) \in \Obj(\Cocone(D)): \text{$\Obj(\Cocone(D))$ is a $D$-colimit}\}.$$
			\end{itemize}
		\end{itemize}
		\tcr{maybe define $\lim$ set, but maybe not, we want to be able to write $(X, \phi) = \lim D$, but we need some guarantee that anything we would possibly want to say is invariant under isomorphism, other wise different limits of $D$ may always be interchangeable, ask someone if we need to be careful here and define limit sets. For instance \href{https://ncatlab.org/nlab/show/commutativity+of+limits+and+colimits}{commutativity}}
	\end{defn}

	\begin{note}
		Let $\MJ$, $\MC$ be categories. Suppose that $\MJ$ is small. Let $D \in \Obj(\MC^{\MJ})$. 
		\begin{itemize}
			\item Let $(X, \phi) \in \Obj(\Cone(D))$. Then 
			\begin{align*}
				\text{$(X, \phi)$  is a limit of $D$} 
				& \iff \text{$(X, \phi)$ is $\Cone(D)$-terminal} \\
				& \iff \text{for each $(X', \phi') \in \Obj(\Cone(D))$, there exists a unique} \\
				& \hspace{1.3cm }\text{$\al \in \Hom_{\MC}(X', X)$ such that for each $j \in \MJ$, $\phi_j \circ_{\MC} \al = \phi'_j$}
			\end{align*} 
			\item Let $(X, \phi) \in \Obj(\Cocone(D))$. Then 
			\begin{align*}
				\text{$(X, \phi)$  is a colimit of $D$} 
				& \iff \text{$(X, \phi)$ is $\Cocone(D)$-initial} \\
				& \iff \text{for each $(X', \phi') \in \Obj(\Cocone(D))$, there exists a unique} \\
				& \hspace{1.3cm }\text{$\al \in \Hom_{\MC}(X, X')$ such that for each $j \in \MJ$, $\al \circ_{\MC} \phi_j = \phi'_j $}
			\end{align*} 
		\end{itemize}
	\end{note} 

	\begin{ex} \lex{lex:limits:limits_colimits:0004}
		\tcr{limits and colimits are unique up to isomorphism} 
		\begin{enumerate}
			\item ?Let $(X, \phi) \in \limSet D$ and $Y \in \Obj(\MC)$, then $(Y, \psi) \in \limSet D$ iff there exists $\al \in \Iso_{\MC}(X,Y)$ such that $\psi \circ_{\MC^{\MJ}} \del^{\MJ}_{\al} = \phi$? 
			\item \tcr{colimits}
		\end{enumerate}
	\end{ex}
	
	\begin{proof}\
		\begin{enumerate}
			\item 
			\item 
		\end{enumerate}
	\end{proof}
	
	\begin{defn} \ld{def:limits:limits_colimits:0005}
		Let $\MJ$, $\MC$ be categories. Suppose that $\MJ$ is small. Let $L \in \prod\limits_{\Obj(\MC^{\MJ})} \limSet(D)$. 
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\section{Fundamental Examples}
	
	\subsection{Products and Coproducts}
	
	\begin{defn}
		Let $\MJ$ be a discrete category, $\MC$ a category, $D \in \MC^{\MJ}$ and $(X, \pi) \in \Cone(D)$. Then $(X, \pi)$ is said to be a \tbf{product of $D$}.
	\end{defn}
	
	\begin{note}
		We may think of a product of $D$ as a tuple $(X, )$
	\end{note}
	
	\begin{ex}
		\tcr{show that if $\b1$ is terminal, then $X \times \b1 \cong X$.   }
	\end{ex}
	
	\begin{ex}
		\tcr{show that if $\MC$ has products, then $\MC$ has a copy morphism (define a copy morphism) see page 32 in `elementary categories, elementary toposes` by McLarty}. 
	\end{ex}
	
	
	
	
	
	
	
	
	
	
	\subsection{Equalizers and Coequalizers}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\subsection{Projective and Inductive Limits}
	
	\begin{defn}
		Let $\MJ$ be a \tcr{directed} poset, $\MC$ a category and $D \in \MC^{\MJ}$. Then $D$ is said to be a \tbf{$\MC$-projective system}.  
	\end{defn}

	\begin{note}
		We may think of 
		\begin{itemize}
			\item a $\MC$-projective system as a tuple $((X_j)_{j \in J}, (\pi_{j,k})_{(j,k) \in \leq})$ where $(J, \leq)$ is a \tcr{directed} poset, $(X_j)_{j \in J} \subset \Obj(\MC)$ and $(\pi_{j,k})_{(j,k) \in \leq} \subset \Hom_{\MC}$ satisfy that for each $j,k,l \in J$, 
			\begin{enumerate}
				\item $j \leq k$ implies that $\pi_{j,k} \in \Hom_{\MC}(X_k, X_j)$,
				\item $\pi_{j,j} = \id_{X_j}$,
				\item $j \leq k$ and $k \leq l$ implies that $\pi_{j,k} \circ_{\MC} \pi_{k,l} = \pi_{j,l}$.
			\end{enumerate}
			\item a cone over $D$ as a tuple $(X, (\pi_j)_{j \in J})$ where $X \in \Obj(\MC)$ and $(\pi_j)_{j \in J} \subset \Hom_{\MC}$ satisfy that for each $j,k \in J$, $j \leq k$ implies that $\pi_{j,k} \circ_{\MC} \pi_k = \pi_j$. 
		\end{itemize}
	\end{note}
	
	\tcr{make some diagrams}
	
	\begin{ex}
		Let $\MC$ be a category and $(X_j)_{j \in \N} \subset \Obj(\MC)$. Define $(Y_n)_{n \in \N} \subset \Obj(\MC)$ and $(\pi_{n, k})_{n \leq k} \in \prod\limits_{n \leq k} \Hom_{\MC}(Y_k, Y_n)$ by $Y_n \defeq \prod\limits_{j=1}^n X_j$ and $\pi_{n,k}$.  Suppose that for each  $(\prod_{n \in \N}, (\pi_n)_{n \in \N})$ \tcr{arg1}. 
	\end{ex}

	\begin{defn}
		Let $(\MJ, \MC, D)$ be a $\MC$-projective system and $(X, \phi) \in \Obj(\Cone(D))$. Then $(X, \phi)$ is said to be a $\MC$-projective limit of $(\MJ, \MC, D)$ if $(X, \phi)$ is a limit of $D$. 
	\end{defn}

	
\begin{note}
	We may think of a projective limit if $(\MJ, \MC, D)$ as a cone $(X, (\pi_j)_{j \in J})$ over $D$ satisfying that for each cone $(Y, (\tau_j)_{j \in J})$ over $D$, there exists a unique $\al \in \Hom_{\MC}(Y, X)$ such that $\tau_j = \pi_j \circ_{\MC} \al$. 
\end{note}

\tcr{make some diagrams}
















































\newpage
\section{Completeness}

\begin{defn} \ld{def:limits:completeness:0001}
	Let $\MC$ be a category and $\MJ \in \Obj(\Cat)$. Then $\MC$ is said to 
	\begin{itemize}
		\item \tbf{have all $\MJ$-limits} if for each $D \in \Obj(\MC^{\MJ})$, $\limSet D \neq \varnothing$. 
		\item \tbf{have all $\MJ$-colimits} if for each $D \in \Obj(\MC^{\MJ})$, $\colimSet D \neq \varnothing$. 
	\end{itemize}
\end{defn}

\begin{defn} \ld{def:limits:completeness:0002}
	Let $\MC$ be a category and $\MJ \in \Obj(\Cat)$.  
	\begin{itemize}
		\item 
		\begin{itemize}
			\item Suppose that $\MC$ has all $\MJ$-limits. Let $L \in \prod\limits_{D \in \Obj(\MC^{\MJ})} \limSet D$. Then $L$ is said to be a \tbf{$\MC^{\MJ}$-limit choice function}.
			\item We define $\limChoice(\MC^{\MJ}) \defeq \prod\limits_{D \in \Obj(\MC^{\MJ})} \limSet D$.
		\end{itemize}
		\item 
		\begin{itemize}
			\item Suppose that $\MC$ has all $\MJ$-colimits. Let $C \in \prod\limits_{D \in \Obj(\MC^{\MJ})} \colimSet D$. Then $C$ is said to be a \tbf{$\MC^{\MJ}$-colimit choice function}.
			\item We define $\colimChoice(\MC^{\MJ}) \defeq \prod\limits_{D \in \Obj(\MC^{\MJ})} \colimSet D$.
		\end{itemize}
	\end{itemize}
\end{defn}


\begin{ex} \lex{ex:limits:completeness:0003}
	Let $\MC$ be a category and $\MJ \in \Obj(\Cat)$.
	\begin{enumerate}
		\item Suppose that $\MC$ has all $\MJ$-limits. Let $L \in \limChoice(\MC^{\MJ})$. Then for each $D_1, D_2 \in \Obj(\MC^{\MJ})$ and $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$, there exists $\eta^L_{\al} \in \Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2})$ such that $\Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2}) = \{\eta^L_{\al}\}$. 
		\item \tcr{do somethign similar for colimtis}
	\end{enumerate}
\end{ex}

\begin{proof}\
	\begin{enumerate}
		\item Let $D_1, D_2 \in \Obj(\MC^{\MJ})$ and $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$. Since $L_{D_2}$ is a $D_2$-limit, $L_{D_2}$ is $\Cone(D_2)$-terminal. Thus there exists $\eta^L_{\al} \in \Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2})$ such that $\Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2}) = \{\eta^L_{\al}\}$. 
		\item \tcr{FINISH!!!!}
	\end{enumerate}
\end{proof}

\begin{defn} \ld{def:limits:completeness:0004}
	Let $\MC$ be a category and $\MJ \in \Obj(\Cat)$. 
	\begin{itemize}
		\item Suppose that $\MC$ has all $\MJ$-limits. Let $L \in \limChoice(\MC^{\MJ})$.
		\begin{itemize}
			\item For $D_1, D_2 \in \Obj(\MC^{\MJ})$ and $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$, we define $\eta^L_{\al} \in \Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2})$ as in \rex{ex:limits:completeness:0003}. 
			\item We define the \tbf{$L$-limit functor}, denoted $\lim\limits_L: \MC^{\MJ} \rightarrow \MC$, by
			\begin{itemize}
				\item $\lim\limits_L(D) \defeq \prj_{\Obj(\MC)}(L_D), \quad D \in \Obj(\MC^{\MJ})$ 
				\item $\lim\limits_L(\al) \defeq \eta^L_{\al}, \quad \al \in \Hom_{\MC^{\MJ}}$.
			\end{itemize}
		\end{itemize}
		\item \tcr{define something similar for colimits, might need to change notation from $\eta^L_{\al}$ to something else}
	\end{itemize}
\end{defn}

\begin{ex} \lex{ex:limits:completeness:0005}
	Let $\MC$ be a category and $\MJ \in \Obj(\Cat)$. 
	\begin{enumerate}
		\item Suppose that $\MC$ has all $\MJ$-limits. Let $L \in \limChoice(\MC^{\MJ})$. Then $\lim\limits_L: \MC^{\MJ} \rightarrow \MC$ is a functor.
		\item \tcr{do something similar for colimits}
	\end{enumerate}
\end{ex}

\begin{proof}\
	\begin{enumerate}
		\item 
		\begin{enumerate}
			\item Let $D_1, D_2 \in \Obj(\MC^{\MJ})$ and $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$. Write $L_{D_1} = (X_1, \phi_1)$ and $L_{D_2} = (X_2, \phi_2)$. Then $\lim\limits_L(D_1) = X_1$ and $\lim\limits_L(D_2) = X_2$. By \rd{def:limits:cones_cocones:0003},  
			\begin{align*}
				\Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2}) 
				& = \Hom_{\Cone(D_2)}((X_1, \al \circ_{\MC^{\MJ}} \phi_1), (X_2, \phi_2)) \\
				& \subset \Hom_{\MC}(X_1, X_2).
			\end{align*}
			Therefore 
			\begin{align*}
				\lim\limits_L(\al)
				& = \eta^L_{\al} \\
				& \in \Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2}) \\
				& \subset \Hom_{\MC}(X_1, X_2) \\
				& = \Hom_{\MC}(\lim\limits_L(D_1), \lim\limits_L(D_2)).
			\end{align*}
			\item Let $D_1, D_2, D_3 \in \Obj(\MC^{\MJ})$, $\al \in \Hom_{\MC^{\MJ}}(D_1, D_2)$ and $\be \in \Hom_{\MC^{\MJ}}(D_2, D_3)$. By \rex{ex:limits:completeness:0003},
			\begin{itemize}
				\item $\Hom_{\Cone(D_2)}(\Cn_{\al}(L_{D_1}), L_{D_2}) = \{\eta^L_{\al}\}$, \item $\Hom_{\Cone(D_3)}(\Cn_{\be}(L_{D_2}), L_{D_3}) = \{\eta^L_{\be}\}$,
				\item $\Hom_{\Cone(D_3)}(\Cn_{\be \circ_{\MC^{\MJ}} \al}(L_{D_1}), L_{D_3}) = \{\eta^L_{\be \circ_{\MC^{\MJ}} \al}\}$. 
			\end{itemize}
			By definition \rd{def:limits:cones_cocones:0003},
			\begin{itemize}
				\item $\eta^L_{\al} \in \Hom_{\MC}(X_1, X_2)$ and $\phi_2 \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\al}) = \al \circ_{\MC^{\MJ}} \phi_1$
				\item $\eta^L_{\be} \in \Hom_{\MC}(X_2, X_3)$ and $\phi_3 \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\be}) = \be \circ_{\MC^{\MJ}} \phi_2$.
				\item 
			\end{itemize}
			Therefore $\eta^L_{\be} \circ_{\MC} \eta^L_{\al} \in \Hom_{\MC}(X_1, X_3)$ and
			\begin{align*}
				\phi_3 \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\be} \circ_{\MC} \eta^L_{\al}) 
				& = \phi_3 \circ_{\MC^{\MJ}} [\Del^{\MJ}(\eta^L_{\be}) \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\al})] \\
				& = [\phi_3 \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\be})] \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\al}) \\
				& = [\be \circ_{\MC^{\MJ}} \phi_2] \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\al}) \\
				& = \be \circ_{\MC^{\MJ}} [\phi_2 \circ_{\MC^{\MJ}} \Del^{\MJ}(\eta^L_{\al}) ] \\
				& = \be \circ_{\MC^{\MJ}} [\al \circ_{\MC^{\MJ}} \phi_1] \\
				& = [\be \circ_{\MC^{\MJ}} \al] \circ_{\MC^{\MJ}} \phi_1.
			\end{align*}
			Hence 
			\begin{align*}
				\eta^L_{\be} \circ_{\MC} \eta^L_{\al} 
				& \in \Hom_{\Cone(D_3)}(X_1, (\be \circ_{\MC^{\MJ}} \al) \circ_{\MC^{\MJ}} \phi_1, (X_3, \phi_3)) \\
				& = \Hom_{\Cone(D_3)}(\Cn_{\be \circ_{\MC^{\MJ}} \al}(L_{D_1}), L_{D_3}) \\
				& = \{\eta^L_{\be \circ_{\MC^{\MJ}} \al}\}.
			\end{align*} 
			Thus 
			\begin{align*}
				\lim\limits_L(\be \circ_{\MC^{\MJ}} \al)
				& = \eta^L_{\be \circ_{\MC^{\MJ}} \al} \\
				& = \eta^L_{\be} \circ_{\MC} \eta^L_{\al} \\
				& = \lim\limits_L(\be) \circ_{\MC} \lim\limits_L(\al).
			\end{align*}
			\item Let $D \in \Obj(\MC^{\MJ})$. Write $L_D = (X, \phi)$. \rex{} \tcr{ref prev ex} implies that $\Cone(\cdot): \MC^{\MJ} \rightarrow \Cat$ and 
			\begin{align*}
				\Cn_{\id_D^{\MC^{\MJ}}} 
				& = \Cone(\cdot)(\id_D^{\MC^{\MJ}}) \\
				& = \id_{\Cone(D)}^{\Cat}.
			\end{align*} 
			Then  
			\begin{align*}
				\Cn_{\id_D^{\MC^{\MJ}}}(L_D) 
				& = \id_{\Cone(D)}^{\Cat}(L_D) \\
				& = L_D.
			\end{align*}
			Since $L_D$ is $\Cone(D)$-terminal,
			\begin{align*}
				\lim\limits_L(\id_D^{\MC^{\MJ}})
				& = \eta^L_{\id_D^{\MC^{\MJ}}} \\
				& \in \Hom_{\Cone(D)}(\Cn_{\id_D^{\MC^{\MJ}}}(L_D), L_D) \\
				& = \Hom_{\Cone(D)}(L_D, L_D) \\
				& = \{\id_{L_D}^{\Cone(D)}\}. 
			\end{align*}
			By \rd{} \tcr{ref cone def}, 
			\begin{align*}
				\id_{L_D}^{\Cone(D)} 
				& = \id_{L_D}^{(\Del^{\MJ} \doar D)} \\
				& = \id_{(X, \phi)}^{(\Del^{\MJ} \doar D)} \\
				& = \id_X^{\MC}.
			\end{align*}
			Therefore
			\begin{align*}
				\lim\limits_L(\id_D^{\MC^{\MJ}})
				& = \id_{L_D}^{\Cone(D)} \\
				& = \id_X^{\MC} \\
				& = \id_{\lim\limits_L(D)}^{\MC}.
			\end{align*}
		\end{enumerate}
		Hence $\lim\limits_L: \MC^{\MJ} \rightarrow \MC$ is a functor. 
		\item \tcr{colimit functor}
	\end{enumerate}
\end{proof}

\begin{ex}
	For a choice of $L$, we get a functor $\lim\limits_L$. Rephrasing this, for each object (a set $L \in \limChoice(\MC^{\MJ})$)  we get a an object (a functor $\lim\limits_L: \MC^{\MJ} \rightarrow \MC$). Maybe we can consider $\limChoice(\MC^{\MJ})$ as a category and consider an arrow $f: L \rightarrow M$ as a function $f: \bigcup\limits_{D \in \Obj(\MC^{\MJ})} \Cone(D) \rightarrow \bigcup\limits_{D \in \Obj(\MC^{\MJ})} \Cone(D)$ such that $f \circ_{\bSet} L = M$, i.e. for each $D \in \Obj(\MC^{\MJ})$ $f(L_D) = M_D$, \tcr{idk, think about}
\end{ex}









\begin{defn} \ld{def:limits:completeness:0007}
	Let $\MC$ be a category. Then $\MC$ is said to be 
	\begin{itemize}
		\item \tbf{complete} if for each $J \in \Obj(\Cat)$, $\MC$ has all $\MJ$-limits.
		\item \tbf{cocomplete} if for each $J \in \Obj(\Cat)$, $\MC$ has all $\MJ$-colimits.
	\end{itemize}
\end{defn}



















































\newpage
\chapter{Yoneda Lemma}

\section{Representable Functors}

\begin{ex} \lex{ex:yoneda:rep_funct:0001}
	Let $\MC$ be a category, $(A_1, A_2), (B_1, B_2) \in \Obj(\op{\MC} \times \MC)$ and $(f_1, f_2) \in \Hom_{\op{\MC} \times \MC}((A_1, A_2), (B_1, B_2))$. Then for each $h \in \Hom_{\MC}(A_1, A_2)$, $f_2 \circ_{\MC} h \circ_{\MC} f_1 \in \Hom_{\MC}(B_1, B_2)$. 
\end{ex}

\begin{proof}
	By definition of $\op{\MC} \times \MC$, we have that
	\begin{itemize}
		\item 
		\begin{align*}
			A_1, B_1
			& \in \Obj(\op{\MC}) \\
			& = \Obj(\MC),
		\end{align*}
		\begin{align*}
			f_1 
			& \in \Hom_{\op{\MC}}(A_1, B_1) \\
			& = \Hom_{\MC}(B_1, A_1),
		\end{align*}
		\item $A_2, B_2 \in \Obj(\MC)$ and $f_2 \in \Hom_{\MC}(A_2, B_2)$.
	\end{itemize}
	Therefore, for each $h \in \Hom_{\MC}(A_1, A_2)$, $f_2 \circ_{\MC} h \circ_{\MC} f_1 \in \Hom_{\MC}(B_1, B_2)$.
\end{proof}

\begin{note}
	If $\MC$ is locally small, then for each $(A_1, A_2) \in \Obj(\op{\MC} \times \MC)$, $\Hom_{\MC}(A_1, A_2) \in \Obj(\bSet)$.
\end{note}

\begin{defn} \ld{def:yoneda:rep_funct:0002}
	Let $\MC$ be a locally small category. We define the \tbf{Hom-functor of $\MC$}, denoted $\Hom_{\MC}(\cdot, \cdot):\op{\MC} \times \MC \rightarrow \bSet$, by 
	\begin{itemize}
		\item $\Hom_{\MC}(\cdot, \cdot)(A_1, A_2) \defeq \Hom_{\MC}(A_1, A_2), \quad (A_1, A_2) \in \Obj(\op{\MC} \times \MC)$
		\item $\Hom_{\MC}(\cdot, \cdot)(f_1,f_2)(h) \defeq f_2 \circ_{\MC} h \circ_{\MC} f_1, \quad (f_1, f_2) \in \Hom_{\op{\MC} \times \MC}((A_1, A_2), (B_1, B_2)), h \in \Hom_{\MC}(A_1, A_2)$
	\end{itemize}
\end{defn}

\begin{ex} \lex{ex:yoneda:rep_funct:0003}
	Let $\MC$ be a locally small category. Then $\Hom_{\MC}:\op{\MC} \times \MC \rightarrow \bSet$ is a functor. 
\end{ex}

\begin{proof}
	Set $H \defeq \Hom_{\MC}(\cdot, \cdot)$.
	\begin{enumerate}
	\item \tcr{The previous ex} implies that for each $(A_1, A_2), (B_1, B_2) \in \Obj(\op{\MC} \times \MC)$ and $(f_1, f_2) \in \Hom_{\op{\MC} \times \MC}((A_1, A_2), (B_1, B_2))$, 
	\begin{align*}
		H(f_1, f_2) 
		& \in \Hom_{\bSet}(\Hom_{\MC}(A_1, A_2), \Hom_{\MC}(B_1, B_2)) \\
		& = \Hom_{\bSet}(H(A_1, A_2), H(B_1, B_2))
	\end{align*}
	\item Let $(A_1, A_2), (B_1, B_2), (C_1, C_2) \in \Obj(\op{\MC} \times \MC)$, $(f_1, f_2) \in \Hom_{\op{\MC} \times \MC}((A_1, A_2), (B_1, B_2))$ and $(g_1, g_2) \in \Hom_{\op{\MC} \times \MC}((B_1, B_2), (C_1, C_2))$. Then for each $h \in \Hom_{\MC}(A_1, A_2)$, we have that 
	\begin{align*}
		H((g_1, g_2) \circ_{\op{\MC} \times \MC}(f_1, f_2))(h)
		& = H(g_1 \circ_{\op{\MC}} f_1, g_2 \circ_{\MC} f_2)(h) \\
		& = H(f_1 \circ_{\MC} g_1, g_2 \circ_{\MC} f_2)(h) \\
		& = (g_2 \circ_{\MC} f_2) \circ_{\MC} h \circ_{\MC} (f_1 \circ_{\MC} g_1) \\
		& = g_2 \circ_{\MC} (f_2 \circ_{\MC} h \circ_{\MC} f_1) \circ_{\MC} g_1 \\
		& = g_2 \circ_{\MC} [H(f_1, f_2)(h)] \circ_{\MC} g_1 \\
		& = H(g_1, g_2)(H(f_1, f_2)(h)) \\
		& = H(g_1, g_2) \circ_{\bSet} H(f_1, f_2)(h).
	\end{align*}
	Thus $H((g_1, g_2) \circ_{\op{\MC} \times \MC}(f_1, f_2)) = H(g_1, g_2) \circ_{\bSet}  H(f_1, f_2)$. Since $(A_1, A_2), (B_1, B_2), (C_1, C_2) \in \Obj(\op{\MC} \times \MC)$, $(f_1, f_2) \in \Hom_{\op{\MC} \times \MC}((A_1, A_2), (B_1, B_2))$ and $(g_1, g_2) \in \Hom_{\op{\MC} \times \MC}((B_1, B_2), (C_1, C_2))$ are arbitrary, we have that for each $(A_1, A_2), (B_1, B_2), (C_1, C_2) \in \Obj(\op{\MC} \times \MC)$, $(f_1, f_2) \in \Hom_{\op{\MC} \times \MC}((A_1, A_2), (B_1, B_2))$ and $(g_1, g_2) \in \Hom_{\op{\MC} \times \MC}((B_1, B_2), (C_1, C_2))$, $H((g_1, g_2) \circ_{\op{\MC} \times \MC}(f_1, f_2)) = H(g_1, g_2) \circ_{\bSet} H(f_1, f_2)$. 
	\item Let $(A_1, A_2) \in \Obj(\op{\MC} \times \MC)$. Then for each $h \in \Hom_{\MC}(A_1, A_2)$,
	\begin{align*}
		H(\id_{(A_1, A_2)}^{\op{\MC} \times \MC})(h)
		& = H(\id_{A_1}^{\op{\MC}}, \id_{A_2}^{\MC})(h) \\
		& = H(\id_{A_1}^{\MC}, \id_{A_2}^{\MC})(h) \\
		& = \id_{A_2}^{\MC} \circ_{\MC} h \circ_{\MC} \id_{A_1}^{\MC} \\
		& = h \\
		& = \id_{\Hom_{\MC}(A_1, A_2)}^{\bSet}(h) \\
		& = \id_{H(A_1, A_2)}^{\bSet}(h).
	\end{align*}
	Thus $H(\id_{(A_1, A_2)}^{\op{\MC} \times \MC}) = \id_{H(A_1, A_2)}^{\bSet}$. Since $(A_1, A_2) \in \Obj(\op{\MC} \times \MC)$ is arbitrary, we have that for each $(A_1, A_2) \in \Obj(\op{\MC} \times \MC)$, $\Hom_{\MC}(\id_{(A_1, A_2)}^{\op{\MC} \times \MC}) = \id_{H(A_1, A_2)}^{\bSet}$.
	\end{enumerate}
	Hence $\Hom_{\MC}: \op{\MC} \times \MC \rightarrow \bSet$ is a functor. 
\end{proof}

\begin{note}
	If $\MC$ is locally small, \rex{ex:basics:contructs:products:0006} implies that for each $X \in \Obj(\MC)$, $\Hom_{\MC}(X, \cdot): \MC \rightarrow \bSet$ and $\Hom_{\MC}(\cdot, X): \op{\MC} \rightarrow \bSet$ are functors.
\end{note}

\begin{ex} \lex{ex:yoneda:rep_funct:0004}
	Let $\MC$ be a category. Suppose that $\MC$ is locally small. Then 
	\begin{enumerate}
		\item for each $X \in \Obj(\op{\MC})$, $\Hom_{\op{\MC}}(X, \cdot) = \Hom_{\MC}(\cdot, X)$
		\item for each $X \in \Obj(\MC)$, $\Hom_{\MC}(X, \cdot) = \Hom_{\op{\MC}}(\cdot, X)$
	\end{enumerate}
\end{ex}

\begin{proof}
	We note that \rex{} \tcr{(ref ex)} implies that $\op{(\op{\MC})} = \MC$. So $\op{(\op{\MC})} \times \op{\MC} = \MC\times \op{\MC}$.
	\begin{enumerate}
		\item Let $X \in \Obj(\op{\MC})$. Then $X \in \Obj(\MC)$.
		\begin{itemize}
			\item Let $A \in \Obj(\op{\MC})$. Then $A \in \Obj(\MC)$ and
			\begin{align*}
				\Hom_{\op{\MC}}(X, \cdot)(A)
				& = \Hom_{\op{\MC}}(\cdot, \cdot)(X, A) \\
				& = \Hom_{\op{\MC}}(X, A) \\
				& = \Hom_{\MC}(A, X) \\
				& = \Hom_{\MC}(\cdot, \cdot)(A, X) \\
				& = \Hom_{\MC}(\cdot, X)(A). 
			\end{align*}
			\item Let $A,B \in \Obj(\op{\MC})$ and $f \in \Hom_{\op{\MC}}(A, B)$ and $h \in \Hom_{\op{\MC}}(X, A)$. Then $A,B \in \Obj(\MC)$, $f \in \Hom_{\MC}(B,A)$ and $h \in \Hom_{\MC}(A, X)$. Thus $(\id_X^{\MC}, f) \in \Hom_{\MC \times \op{\MC}}((X, A), (X, B))$ and
			\begin{align*}
				\Hom_{\op{\MC}}(X, \cdot)(f)(h)
				& = \Hom_{\op{\MC}}(\cdot, \cdot)(\id_X^{\MC}, f)(h) \\
				& = f \circ_{\op{\MC}} h \circ_{\op{\MC}} \id_X^{\MC} \\
				& = \id_X^{\MC} \circ_{\MC} h \circ_{\MC} f \\
				& = \Hom_{\MC}(\cdot, \cdot)(f, \id_X^{\MC})(h) \\
				& = \Hom_{\MC}(\cdot, X)(f)(h)
			\end{align*}
			Since $h \in \Hom_{\op{\MC}}(X, A)$ is arbitrary, we have that for each $h \in \Hom_{\op{\MC}}(X, A)$, $\Hom_{\op{\MC}}(X, \cdot)(f)(h) = \Hom_{\MC}(\cdot, X)(f)(h)$. Thus $\Hom_{\op{\MC}}(X, \cdot)(f) = \Hom_{\MC}(\cdot, X)(f)$.
		\end{itemize}
		Hence $\Hom_{\op{\MC}}(X, \cdot) = \Hom_{\MC}(\cdot, X)$.
		\item \tcr{FINISH!!!} (similar)
	\end{enumerate}
\end{proof}

\begin{defn} \ld{def:yoneda:rep_funct:0005}
	Let $\MC$ be a category. Suppose that $\MC$ is locally small. Let $F: \MC \rightarrow \bSet$. 
	\begin{itemize}
		\item Let $X \in \Obj(\MC)$ and $\phi : F \Rightarrow \Hom_{\MC}(X, \cdot)$. Then $(X, \phi)$ is said to be a \tbf{representation of $F$} if $\phi$ is a natural isomorphism.
		\item Then $F$ is said to be \tbf{representable} if there exists $X \in \Obj(\MC)$ and $\phi:F \Rightarrow \Hom_{\MC}(X, \cdot)$ such that $(X, \phi)$ is a representation of $F$. 
	\end{itemize}
\end{defn}

\begin{ex} \lex{ex:yoneda:rep_funct:0006}
	Let $\MC$ be a category. Suppose that $\MC$ is small. Let $X \in \Obj(\MC)$. Let $1 \in \Obj(\bSet)$. Suppose that $1$ is $\bSet$-terminal. Then
	\begin{enumerate}
		\item $X$ is $\MC$-initial iff $\Hom_{\MC}(X, \cdot) \cong_{\bSet^{\MC}} \Del^{\MC}_1$.
		\item $X$ is $\MC$-terminal iff $\Hom_{\op{\MC}}(\cdot, X) \cong_{\bSet^{\op{\MC}}} \Del^{\op{\MC}}_1$.
	\end{enumerate}
\end{ex}

\begin{proof}
	Define $F \in \bSet^{\MC}$ by $F \defeq \Hom_{\MC}(X, \cdot)$.
	\begin{enumerate}
		\item \rex{15020} implies that $\phi^{(F,1)} \in \Hom_{\bSet^{\MC}}(F, \Del^{\MC}_1)$. \rex{15015} implies that there exists $x \in 1$ such that $1 = \{x\}$.
		\begin{itemize}
			\item $(\implies)$: \\
			Suppose that $X$ is $\MC$-initial. Let $A \in \Obj(\MC)$. Since $F(A) = \Hom_{\MC}(X, A)$, \rex{15015.1} implies that $F(A)$ is $\bSet$-terminal. Since $1$ is $\bSet$-terminal, \rex{15014} implies that $F(A) \cong_{\bSet} 1$ and $\Hom_{\bSet}(F(A), 1) = \Iso_{\bSet}(F(A), 1)$. Therefore 
			\begin{align*}
				\phi^{(F,1)}_A 
				& \in \Hom_{\bSet}(F(A), 1) \\
				& = \Iso_{\bSet}(F(A), 1) \\
				& = \Iso_{\bSet}(F(A), \Del^{\MC}_1(A)).
			\end{align*}
			Since $A \in \Obj(\MC)$ is arbitrary, we have that for each $A \in \Obj(\MC)$, $\phi^{(F,1)}_A \in \Iso_{\bSet}(F(A), \Del^{\MC}_1(A))$. Thus $\phi^{(F,1)}:F \Rightarrow \Del^{\MC}_1$ is a natural isomorphism. \rex{15011.5} then implies that $\phi^{(F,1)} \in \Iso_{\bSet^{\MC}}(F, \Del^{\MC}_1)$. Since $\Iso_{\bSet^{\MC}}(F, \Del^{\MC}_1) \neq \varnothing$, we have that $F \cong_{\bSet^{\MC}} \Del^{\MC}_1$.
			\item $(\impliedby)$: \\
			Suppose that $F \cong_{\bSet^{\MC}} \Del^{\MC}_1$. Then there exists $\phi \in \Iso_{\bSet^{\MC}}(F, \Del^{\MC}_1)$. \rex{15011.5} then implies that $\phi: F \Rightarrow \Del^{\MC}_1$ is a natural isomorphism. Let $A \in \Obj(\MC)$. Then 
			\begin{align*}
				\phi_A 
				& \in \Iso_{\bSet}(F(A), \Del^{\MC}_1(A)) \\
				& = \Iso_{\bSet}(F(A), 1).
			\end{align*}
			Since $\Iso_{\bSet}(F(A), 1) \neq \varnothing$ and $1$ is $\bSet$-terminal, we have that  
			\begin{align*}
				\Hom_{\MC}(X, A) 
				& = F(A) \\
				& \cong_{\bSet} 1 \\
				& \cong_{\bSet} \{\varnothing\}, \quad \text{(by \rex{15015})}.
			\end{align*}
			Thus there exists $f \in \Hom_{\MC}(X, A)$ such that $\Hom_{\MC}(X, A) = \{f\}$. Since $A \in \Obj(\MX)$ is arbitrary, we have that for each $A \in \Obj(\MC)$, there exists $f \in \Hom_{\MC}(X, A)$ such that $\Hom_{\MC}(X, A) = \{f\}$. Hence $X$ is $\MC$-initial.
		\end{itemize}
		\item We have that 
		\begin{align*}
			\text{$X$ is $\MC$-terminal}
			& \iff \text{$X$ is $\op{\MC}$-initial}, \quad \text{(by \rex{15012.1})} \\
			& \iff \Hom_{\op{\MC}}(X, \cdot) \cong_{\bSet^{\op{\MC}}} \Del^{\op{\MC}}_1, \quad \text{(by \tcr{(ref) prev part})} \\
			& \iff \Hom_{\MC}(\cdot, X) \cong_{\bSet^{\op{\MC}}} \Del^{\op{\MC}}_1, \quad \text{(by \tcr{(ref) prev ex about $\Hom_{\MC}(\cdot, X) = \Hom_{\op{\MC}}(X, \cdot)$})}
		\end{align*}
	\end{enumerate}
\end{proof}

\begin{ex}
	Let $\MC$ be a category, $F:\MC \rightarrow \bSet$, $X \in \Obj(\bSet)$ and $(A, f) \in (X \doar F)$. Suppose that $\MC$ is locally small, $X$ is $\bSet$-terminal and $(A,f)$ is a universal morphism from $X$ to $F$. Then 
\end{ex}











\tcr{relevant exercises}

\rex{ex:basics:contructs:func_cats:0002}

\rex{ex:basics:contructs:currying:0012}


\begin{ex} \lex{} \tbf{Yoneda Lemma:}
	Let $\MC$ be a category. Suppose that $\MC$ is locally small. Then 
	$$ \Rightarrow \eval_{(\MC, \bSet)}$$
\end{ex}































\newpage
\section{Fundamental Examples}

\tcr{look up applications of yoneda lemma to analysis. For example, see Tom LaGatta's answer on \href{https://mathoverflow.net/questions/243429/corollaries-of-the-yoneda-lemma-in-analysis}{stackexchange}} and look up yoneda lemma construction of dedikind cuts for posets.











































































	\newpage
	\chapter{Adjunctions}
	
	\begin{ex}
		Let 
	\end{ex}
	
	\begin{defn}
		Let $\MC$, $\MD$ be categories, $F: \MC \rightarrow \MD$ and $G: \MD \rightarrow \MC$. Then $(F,G)$ is said to be an \tbf{adjunction} if 
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	

	\section{TO DO}
	\begin{itemize}
		\item Define subcategories and full subcategories and show that if $\Obj(D) \subset \Obj(C)$ and for each $X, Y \in \Obj(D)$, $\Hom_{D}(X, Y) = \Hom_{C}(X,Y)$, then $D$ is a full subcategory of $C$. I used this in differential 
		\item discuss projective/inductive systems and the projective/inductive limits and applications to topology and measure theory
	\end{itemize}
	
	
	
	
	
	
	
	
	
	
	
	
	

	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\chapter{Monoidal Categories}
	
	\begin{defn}
		Let $\MC$ be a category, $\otimes : \MC \times \MC \rightarrow \MC$, $\rho: (- \otimes -) \otimes \cdot \Rightarrow - \otimes (- \otimes -)$.
	\end{defn}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	\chapter{To Do}
	
	
	\begin{itemize}
		\item look into the schroder bernstein property \href{https://en.wikipedia.org/wiki/Schr%C3%B6der%E2%80%93Bernstein_property}{wikipedia}
	\end{itemize}
	
	
	
	
	
	
	
	
	
	
	
	
	\appendix
	\chapter{App}
	
	\section{Reading Diagrams and associated digraphs of diagrams}
	
	\begin{defn}
		Let 
		\[ 
		\begin{tikzcd}[baseline= 7]
			C \arrow[r, "g"] \arrow[d, "h"'] & A \arrow[d, "f"] \\
			A \arrow[r, "f"'] & B\\
		\end{tikzcd}
		\implies
		\begin{tikzcd}[baseline= 7]
			C \arrow[bend right=60, swap]{r}{h} \arrow[bend right=-60]{r}{g} & A  \\
		\end{tikzcd}
		\]
		
		see an intro to the language of category theory by roman for description
	\end{defn}
	
	
	\begin{defn}
		A diagram is said to be \tbf{commutative} if for each path of length $\geq 2$, in the associated digraph gives the same morphism.  
	\end{defn}
	
	
	
	\backmatter
	
	
	
	
	
	
	
	
	
	
	
	
	
	
\end{document}